---
title: "Manuscript Summary"
subtitle: "A Systematic Review of Methods Used for Studying Heartbeat Evoked Responses"
output: 
  html_document:
    self_contained: false
    theme: null
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
library(cowplot)
library(dplyr)
library(eegUtils)
library(grid)
library(gridExtra)
library(gridGraphics)
library(ggimage)
library(ggplot2)
library(ggtext)
library(magick)
library(PRISMA2020)
library(purrr)
library(scales)
library(stringr)
library(testit)
library(tidyr)
library(viridis)
library(zeallot)

# Use absolute paths to avoid path resolution issues
project_root <- "/data/hu_steinfath/Desktop/Code/systematic-hep-review"
data_path <- file.path(project_root, 'data')
func_path <- file.path(project_root, 'functions')
derivatives_path <- file.path(data_path, 'derivatives')
df_included <- read.csv(file.path(derivatives_path, 'included.csv'))
df_screening <- read.csv(file.path(derivatives_path, 'screening.csv'))

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      results = "asis")

# Create study-level and pipeline-level datasets for efficiency
df_studies <- df_included %>% distinct(PMID, .keep_all = TRUE)
df_pipelines <- df_included

# EEG-only datasets
eeg_studies <- df_studies %>% filter(modality == "EEG")
eeg_pipelines <- df_pipelines %>% filter(modality == "EEG")

meg_studies <- df_studies %>% filter(modality == "MEG")
meg_pipelines <- df_pipelines %>% filter(modality == "MEG")
```

# Overview

This document provides all values mentioned in the manuscript "Heartbeat-evoked responses in MEG/EEG: A systematic review of methods and suggestions for analysis and reporting". All sections of this document apart from this overview match the corresponding section of the manuscript. Numbers highlighted in **bold** are also present in the manuscript.

## Important Distinction: Studies vs Pipelines

- **Studies**: Unique publications (identified by PMID). Each study represents one research paper.
- **Pipelines**: Individual analysis approaches within studies. Some studies report multiple analysis pipelines (e.g. different time windows, or statistical approaches).

# Methods

## Literature search

```{r data-export}
# Load the search data files
exports_path <- file.path(data_path, 'exports')

df_query1 <- read.csv(file.path(exports_path, '20240115_pubmed_query1.csv'))
df_query2 <- read.csv(file.path(exports_path, '20240724_pubmed_query2.csv'))
df_query2_rerun <- read.csv(file.path(exports_path, '20240805_pubmed_query2.csv'))
df_query3 <- read.csv(file.path(exports_path, '20240805_pubmed_query3.csv'))

df_merged <- df_query1 %>%
  bind_rows(df_query2) %>%
  bind_rows(df_query2_rerun) %>%
  bind_rows(df_query3) %>%
  distinct(PMID)
```

Table 1 - number of retrieved papers:

* 15.01.2024: **`r nrow(df_query1)`**
* 24.07.2024: **`r nrow(df_query2)`** (rerun: **`r nrow(df_query2_rerun)`**)
* 05.08.2024: **`r nrow(df_query3)`**
* After removing duplicates: **`r nrow(df_merged)`**

```{r literature-search, results='asis'}
screening_pubmed <- df_screening[df_screening$source == "pubmed",]
screening_manual <- df_screening[df_screening$source == "manual",]

total_retrieved_pubmed <- nrow(screening_pubmed)
total_included_pubmed <- nrow(screening_pubmed[screening_pubmed$Include == 1,])
total_retrieved_manual <- nrow(screening_manual)
total_included_manual <- nrow(screening_manual[screening_manual$Include == 1,])
```

Exported from Pubmed:

* Retrieved: **`r total_retrieved_pubmed`** studies
* Included: **`r total_included_pubmed`** studies

Manually added:

* Retrieved: **`r total_retrieved_manual`** studies
* Included: **`r total_included_manual`** studies

Final sample: **`r total_included_pubmed + total_included_manual`** studies

# Results

## Overview of the included studies

```{r literature-overview}
# Basic counts
total_pipelines <- nrow(df_pipelines)
total_studies <- nrow(df_studies)

# Year range (based on unique studies)
year_range <- df_studies %>% 
  summarise(min_year = min(Year, na.rm = TRUE), max_year = max(Year, na.rm = TRUE))

# Modality breakdown (unique studies)
modality_counts <- df_studies %>%
  count(modality) %>%
  mutate(percentage = round(n / sum(n) * 100, 1))
modality_eeg <- as.list(modality_counts[modality_counts$modality == "EEG",])
modality_meg <- as.list(modality_counts[modality_counts$modality == "MEG",])

# Task vs resting state - studies that have both vs only one type
study_types <- df_pipelines %>%
  filter(!is.na(rsHEP)) %>%
  group_by(PMID) %>%
  summarise(
    has_resting = any(rsHEP == 1),
    has_task = any(rsHEP == 0),
    .groups = "drop"
  ) %>%
  mutate(
    category = case_when(
      has_resting & has_task ~ "Both",
      has_resting & !has_task ~ "Rest", 
      !has_resting & has_task ~ "Task",
      TRUE ~ "Other"
    )
  ) %>%
  count(category) %>%
  mutate(percentage = round(n / sum(n) * 100, 1))
assert("All studies perform either task-based or resting-state analysis",
       nrow(study_types[study_types$category == "Other",]) == 0)

study_type_task <- as.list(study_types[study_types$category == "Task",])
study_type_rest <- as.list(study_types[study_types$category == "Rest",])
study_type_both <- as.list(study_types[study_types$category == "Both",])
```

```{r overview-stats}
# Calculate final sample stats
final_sample_stats <- df_studies %>%
  summarise(
    total_studies = n(),
    year_min = min(Year, na.rm = TRUE),
    year_max = max(Year, na.rm = TRUE)
  )

# Modality breakdown
modality_breakdown <- df_studies %>%
  count(modality) %>%
  mutate(percentage = round(n / sum(n) * 100, 1))

eeg_stats <- modality_breakdown %>% filter(modality == "EEG")
meg_stats <- modality_breakdown %>% filter(modality == "MEG")
```

In total, **`r final_sample_stats$total_studies`** studies published between **`r final_sample_stats$year_min`** and **`r final_sample_stats$year_max`** were included in the review. The vast majority of studies used EEG recordings (**`r eeg_stats$n`** studies, **`r eeg_stats$percentage`%**), while only **`r meg_stats$n`** studies (**`r meg_stats$percentage`%**) employed MEG to measure HERs.

Study type distribution:

* Task-based: **`r study_type_task$n`** studies (**`r study_type_task$percentage`%**)
* Resting-state: **`r study_type_rest$n`** studies (**`r study_type_rest$percentage`%**)
* Both: **`r study_type_both$n`** studies (**`r study_type_both$percentage`%**)

## Overview of methodological choices

```{r variations}
```

## M/EEG Acquisition & Preprocessing

### Channel Information

```{r channels}
# EEG channel statistics
channel_data <- eeg_studies %>%
  filter(!is.na(meeg_num_electrodes) & meeg_num_electrodes != "unknown") %>%
  distinct(PMID, meeg_num_electrodes) %>%
  mutate(channels_numeric = as.numeric(meeg_num_electrodes)) %>%
  filter(!is.na(channels_numeric))

channel_stats <- channel_data %>%
  summarise(
    min_channels = min(channels_numeric, na.rm = TRUE),
    max_channels = max(channels_numeric, na.rm = TRUE),
    median_channels = median(channels_numeric, na.rm = TRUE),
    n_studies = n()
  )
```

### Reference Schemes

```{r references}
# Reference processing
major_categories <- tolower(c(
  "Cz", "Nose", "Linked earlobes", "Linked mastoids",
  "FCz", "Common average", "Fpz", "CMS", "CMS and DRL",
  "unknown", "Laplacian reference", "REST"
))

# Process reference categories
eeg_studies_ref <- eeg_studies %>%
  mutate(across(
    .cols = c(reference_online, reference_offline),
    .fns = ~ case_when(
      tolower(.) %in% major_categories ~ tolower(.),
      TRUE ~ "Other"
    )
  ))

# Common reference category mapping 
ref_categories <- c(
  "common average" = "CAR",
  "linked mastoids" = "LM", 
  "linked earlobes" = "LE",
  "cz" = "Cz",
  "fcz" = "FCz",
  "fpz" = "Fpz",
  "cms" = "CMS",
  "cms and drl" = "CMS",
  "nose" = "Nose",
  "laplacian reference" = "LAP",
  "rest" = "REST",
  "other" = "Other",
  "unknown" = "N/M"
)

# Online reference distribution (studies) 
online_ref_counts <- eeg_studies_ref %>%
  count(reference_online) %>%
  filter(reference_online %in% names(ref_categories)) %>%
  mutate(
    display_name = ref_categories[reference_online],
    percentage = round(n / sum(n) * 100, 1)
  ) %>%
  arrange(desc(n))

# Offline reference distribution (studies)
offline_ref_counts <- eeg_studies_ref %>%
  count(reference_offline) %>%
  filter(reference_offline %in% names(ref_categories)) %>%
  mutate(
    display_name = ref_categories[reference_offline],
    percentage = round(n / sum(n) * 100, 1)
  ) %>%
  arrange(desc(n))
```

For the data acquisition, we can observe some variability with respect to the used online reference. This variability is reduced during data processing, where the dominant choice is Common Average Reference (CAR, used in **`r offline_ref_counts$percentage[offline_ref_counts$display_name == "CAR"]`%** of the studies).

### Artifact Removal

```{r artifacts}
# Artifact removal statistics (studies)
artifact_stats <- df_studies %>%
  summarise(
    # Noisy epochs removal 
    noisy_epochs_pct = round(mean(grepl("noisy epoch", other_cleaning_strategy, ignore.case = TRUE) %in% TRUE, na.rm = TRUE) * 100, 0),
    
    # Bad channels removal 
    bad_channels_pct = round(mean(grepl("bad channels", other_cleaning_strategy, ignore.case = TRUE) %in% TRUE, na.rm = TRUE) * 100, 0),
    
    # Blink/EOG correction
    blink_correction_pct = round(mean(grepl("blink|eye|gratton", other_cleaning_strategy, ignore.case = TRUE) %in% TRUE, na.rm = TRUE) * 100, 0),

    # ICA usage
    ica_pct = round(mean(ICA == 1, na.rm = TRUE) * 100, 1),
    
    # Studies with ICA
    n_ica_studies= sum(ICA == 1, na.rm = TRUE),
    total_studies = n() 
  )

# Studies using ICA (unique studies)
ica_studies <- df_pipelines %>%
  group_by(PMID) %>%
  summarise(uses_ica = any(ICA == 1, na.rm = TRUE)) %>%
  summarise(
    n_ica_studies = sum(uses_ica),
    total_studies = n(),
    ica_study_pct = round(mean(uses_ica) * 100, 1)
  )

# Studies using ICA specifically for cardiac field artifacts (CFA) removal
ica_for_cfa_studies <- df_pipelines %>%
  group_by(PMID) %>%
  summarise(
    uses_ica_for_cfa = any(ICA == 1 & 
                           !is.na(rejected_components) & 
                           rejected_components != "" &
                           grepl("cfa", rejected_components, ignore.case = TRUE)),
    .groups = "drop"
  ) %>%
  summarise(
    n_ica_cfa_studies = sum(uses_ica_for_cfa),
    total_studies = n(),
    ica_cfa_study_pct = round(mean(uses_ica_for_cfa) * 100, 1)
  )

# Component rejection types (studies with ICA)
component_types_df <- df_pipelines %>%
  filter(ICA == 1) %>%
  distinct(PMID, rejected_components) %>%
  filter(rejected_components != "", rejected_components != "unknown") %>%
  mutate(pipeline_id = row_number())

# Clean rejected_components
component_types_df$rejected_components <- sapply(component_types_df$rejected_components, function(x) {
  x <- gsub("[\r\n]+", ",", x)    
  x <- gsub(",+", ",", x)         
  x <- gsub("^,|,$", "", x)       
  comps <- unlist(strsplit(x, ","))
  comps <- unique(trimws(comps))
  comps <- comps[comps != ""]
  paste(comps, collapse = ",")
})

# Count total studies before splitting
total_ica_studies <- nrow(component_types_df)

component_types <- component_types_df %>%
  separate_rows(rejected_components, sep = ",") %>%
  mutate(
    rejected_components = trimws(rejected_components),
    rejected_components = tolower(rejected_components)
  ) %>%
  # Apply component mapping
  mutate(rejected_components = case_when(
    rejected_components == "eye movements" ~ "Ocular",
    rejected_components == "blinks" ~ "Ocular", 
    rejected_components == "muscle" ~ "Muscle",
    rejected_components == "cfa" ~ "CFA",
    rejected_components == "channel noise" ~ "Channel noise",
    rejected_components == "line noise" ~ "Line noise",
    rejected_components == "other" ~ "Other",
    TRUE ~ rejected_components
  )) %>%
  filter(rejected_components != "") %>%
  group_by(rejected_components) %>%
  summarise(count = n_distinct(pipeline_id), .groups = "drop") %>%
  arrange(desc(count)) %>%
  mutate(percentage = round(count / total_ica_studies * 100, 1))
```

## Artifact Removal Statistics

In terms of artifact reduction, many studies reported the removal of noisy epochs (**`r artifact_stats$noisy_epochs_pct`%**) and bad channels (**`r artifact_stats$bad_channels_pct`%**). Independent Component Analysis (ICA) is by far the most commonly used technique used by **`r ica_studies$ica_study_pct`%** of all studies to remove artifacts related to cardiac, eye movement, muscle or other nuisance sources.

### ICA Usage Statistics

* Studies using ICA: **`r ica_studies$ica_study_pct`%** (**`r ica_studies$n_ica_studies`**/**`r ica_studies$total_studies`**)
* Studies using ICA for cardiac field artifacts: **`r ica_for_cfa_studies$ica_cfa_study_pct`%** (**`r ica_for_cfa_studies$n_ica_cfa_studies`**/**`r ica_for_cfa_studies$total_studies`**)

### ICA Component Types Removed

* `r component_types$rejected_components[1]`: **`r component_types$percentage[1]`%**
* `r component_types$rejected_components[2]`: **`r component_types$percentage[2]`%**
* `r component_types$rejected_components[3]`: **`r component_types$percentage[3]`%**
* remaining noise components: **`r component_types$percentage[4] + component_types$percentage[5] + component_types$percentage[6]`%**
## Filter Settings

```{r filters}
# Filter statistics
filter_data <- df_pipelines %>%
  filter(!is.na(high_pass) & !is.na(low_pass)) %>%
  distinct(PMID, high_pass, low_pass, .keep_all = TRUE)

filter_stats <- filter_data %>%
  summarise(
    n_valid = n(),
    high_pass_range_min = min(high_pass, na.rm = TRUE),
    high_pass_range_max = max(high_pass, na.rm = TRUE),
    low_pass_range_min = min(low_pass, na.rm = TRUE), 
    low_pass_range_max = max(low_pass, na.rm = TRUE)
  )

# Most common high-pass filter values (studies)
common_highpass <- filter_data %>%
  count(high_pass, sort = TRUE) %>%
  head(3)

# Most common low-pass filter values (studies)
common_lowpass <- filter_data %>%
  count(low_pass, sort = TRUE) %>%
  head(3)

```

## Filter Settings

When analysing relatively slow evoked responses, like the HER, optimal filter settings are an important consideration to not remove or induce effects. We observe that across studies, filtering is most frequently done between **`r common_highpass$high_pass[1]` Hz** and **`r common_lowpass$low_pass[1]` Hz**, with the most dominant high-pass filter cutoffs at **`r paste(common_highpass$high_pass, collapse = ", ")` Hz** (Fig. 3E).

# ECG Acquisition

```{r ecg}
```

# Dealing with cardiac field artifacts

```{r cfa}
# ICA timing (studies using ICA)
ica_timing <- df_studies %>%
  filter(ICA == 1 & !is.na(ica_on_epochs)) %>%
  count(ica_on_epochs) %>%
  mutate(
    timing = case_when(
      ica_on_epochs == 0 ~ "Continuous",
      ica_on_epochs == 1 ~ "Epoched",
      TRUE ~ "Unknown"
    ),
    percentage = round(n / sum(n) * 100, 1)
  )

# CFA identification approaches (studies)
cfa_approach_counts <- df_studies %>%
  filter(!is.na(cfa_rej_approach) & 
         cfa_rej_approach != "" & 
         tolower(str_trim(cfa_rej_approach)) != "unknown") %>%
  mutate(cfa_rej_approach_clean = str_to_title(tolower(str_trim(cfa_rej_approach)))) %>%
  count(cfa_rej_approach_clean, sort = TRUE) %>%
  mutate(percentage = round(n / sum(n) * 100, 1)) %>%
  rename(cfa_rej_approach = cfa_rej_approach_clean)

# CFA identification criteria (studies)
cfa_criteria_counts <- df_studies %>%
  mutate(cfa_rej_criteria = tolower(cfa_rej_criteria)) %>%
  filter(!is.na(cfa_rej_criteria), cfa_rej_criteria != "", cfa_rej_criteria != "unknown") %>%
  distinct(PMID, cfa_rej_criteria) %>%
  mutate(pipeline_id = row_number()) %>%
  separate_rows(cfa_rej_criteria, sep = ",") %>%
  mutate(
    cfa_rej_criteria = str_replace_all(cfa_rej_criteria, "[\r\n]", " "),
    cfa_rej_criteria = str_trim(cfa_rej_criteria, side = "both"),
    cfa_rej_criteria = case_when(
      cfa_rej_criteria == "time course" ~ "Time Course",
      cfa_rej_criteria == "topography" ~ "Topography", 
      cfa_rej_criteria == "power spectrum" ~ "Power Spectrum",
      cfa_rej_criteria == "phase consistency" ~ "Phase Consistency",
      cfa_rej_criteria == "iclabel" ~ "Algorithm",
      cfa_rej_criteria == "corrmap" ~ "Algorithm",
      cfa_rej_criteria == "correlation" ~ "Correlation",
      cfa_rej_criteria == "sasica" ~ "Algorithm",
      TRUE ~ str_to_title(cfa_rej_criteria)
    )
  ) %>%
  filter(cfa_rej_criteria != "", cfa_rej_criteria != "unknown") %>%
  distinct(pipeline_id, cfa_rej_criteria, .keep_all = TRUE) %>%
  group_by(cfa_rej_criteria) %>%
  summarise(count = n_distinct(pipeline_id), .groups = "drop") %>%
  arrange(desc(count)) %>%
  mutate(
    total_pipelines = length(unique(df_studies$PMID[!is.na(df_studies$cfa_rej_criteria) & 
                                                    df_studies$cfa_rej_criteria != "" & 
                                                    tolower(df_studies$cfa_rej_criteria) != "unknown"])),
    percentage = round(count / total_pipelines * 100, 1)
  )

# Number of rejected cardiac ICs (studies)
cardiac_ic_stats <- df_studies %>%
  filter(!is.na(rejected_cardiac_ics)) %>%
  summarise(
    n_studies = n(),
    min_ics = min(rejected_cardiac_ics, na.rm = TRUE),
    max_ics = max(rejected_cardiac_ics, na.rm = TRUE),
    median_ics = median(rejected_cardiac_ics, na.rm = TRUE)
  )

# Other CFA removal strategies (studies)
# Use exact same logic as the rr_intervals_plot: start from df_pipelines and use distinct(PMID, other_cfa_removal_strategy)
other_cfa_strategies <- df_pipelines %>%
  filter(!is.na(other_cfa_removal_strategy) & 
         other_cfa_removal_strategy != "" & 
         tolower(str_trim(other_cfa_removal_strategy)) != "unknown") %>%
  distinct(PMID, other_cfa_removal_strategy) %>%  
  mutate(
    # Clean and standardize strategy names
    strategy_clean = case_when(
      other_cfa_removal_strategy == "limit analysis to time of minimal artifact" ~ 
        "Minimal artifact window",
      # Use same logic as figure: match "rr at least" followed by number and "ms"
      !is.na(str_match(tolower(other_cfa_removal_strategy), "rr at least\\s*(\\d+)\\s*ms")[,1]) ~ 
        "RR interval\nconstraints",
      tolower(other_cfa_removal_strategy) %in% c(
        "subtract/regress ecg from eeg"
      ) ~ "Subtract/regress ECG from EEG",
      tolower(other_cfa_removal_strategy) == "subtract rshep from taskhep" ~ 
        "subtract rsHEP\nfrom task HEP",
      tolower(other_cfa_removal_strategy) == "pca on heps" ~ "PCA on\nHEP",
            tolower(other_cfa_removal_strategy) == "csd" ~ "CSD",
      TRUE ~ str_to_title(str_trim(other_cfa_removal_strategy))
    )
  ) %>%
  count(strategy_clean, sort = TRUE) %>%
  mutate(percentage = round(n / sum(n) * 100, 1)) %>%
  rename(strategy = strategy_clean)


# Papers with no CFA approach (studies level)
no_cfa_analysis <- df_studies %>%
  mutate(
    # Check if study uses ICA AND mentions CFA in rejected components
    uses_ica_for_cfa = (ICA == 1 & 
                        rejected_components != "" &
                        rejected_components != "unknown" &
                        grepl("CFA", rejected_components, ignore.case = TRUE)),
    # Check if study has other CFA removal strategies
    has_other_cfa = (!is.na(other_cfa_removal_strategy) & 
                     other_cfa_removal_strategy != "" & 
                     tolower(str_trim(other_cfa_removal_strategy)) != "unknown"),
    # Study has some CFA approach if it uses ICA for CFA OR has other CFA strategies
    has_any_cfa_approach = (uses_ica_for_cfa | has_other_cfa),
    # Study has no CFA approach if it doesn't use ICA for CFA AND has no other CFA strategies
    no_cfa_approach = !has_any_cfa_approach
  )

# Calculate summary statistics
no_cfa_stats <- no_cfa_analysis %>%
  summarise(
    total_studies = n(),
    studies_with_ica_for_cfa = sum(uses_ica_for_cfa, na.rm = TRUE),
    studies_with_other_cfa = sum(has_other_cfa, na.rm = TRUE),
    studies_with_any_cfa = sum(has_any_cfa_approach, na.rm = TRUE),
    studies_with_no_cfa = sum(no_cfa_approach, na.rm = TRUE),
    pct_with_ica_for_cfa = round(studies_with_ica_for_cfa / total_studies * 100, 1),
    pct_with_other_cfa = round(studies_with_other_cfa / total_studies * 100, 1),
    pct_with_any_cfa = round(studies_with_any_cfa / total_studies * 100, 1),
    pct_with_no_cfa = round(studies_with_no_cfa / total_studies * 100, 1)
  )

# Breakdown by modality
no_cfa_by_modality <- df_studies %>%
  mutate(
    uses_ica_for_cfa = (ICA == 1 & 
                        !is.na(rejected_components) & 
                        rejected_components != "" &
                        rejected_components != "unknown" &
                        grepl("cfa|cardiac", rejected_components, ignore.case = TRUE)),
    has_other_cfa = (!is.na(other_cfa_removal_strategy) & 
                     other_cfa_removal_strategy != "" & 
                     tolower(str_trim(other_cfa_removal_strategy)) != "unknown"),
    has_any_cfa_approach = (uses_ica_for_cfa | has_other_cfa),
    no_cfa_approach = !has_any_cfa_approach
  ) %>%
  group_by(modality) %>%
  summarise(
    total_studies = n(),
    studies_with_no_cfa = sum(no_cfa_approach, na.rm = TRUE),
    pct_with_no_cfa = round(studies_with_no_cfa / total_studies * 100, 1),
    .groups = "drop"
  )
```

## ICA Application Timing

In terms of artifact removal, ICA is used by (**`r no_cfa_stats$studies_with_ica_for_cfa`**/**`r no_cfa_stats$total_studies`**) of all studies to remove cardiac artefacts  

* Continuous: **`r ica_timing$percentage[ica_timing$timing == "Continuous"]`%**
* Epoched: **`r ica_timing$percentage[ica_timing$timing == "Epoched"]`%**

## CFA Identification Approaches

* Not reported: **`r round((1 - sum(cfa_approach_counts$n) / ica_studies$n_ica_studies) * 100, 1)`%** of studies using ICA
* `r cfa_approach_counts$cfa_rej_approach[1]`: **`r cfa_approach_counts$percentage[1]`%**
* `r cfa_approach_counts$cfa_rej_approach[2]`: **`r cfa_approach_counts$percentage[2]`%**
* `r cfa_approach_counts$cfa_rej_approach[3]`: **`r cfa_approach_counts$percentage[3]`%**

## CFA Identification Criteria

* `r cfa_criteria_counts$cfa_rej_criteria[1]`: **`r cfa_criteria_counts$percentage[1]`%**
* `r cfa_criteria_counts$cfa_rej_criteria[2]`: **`r cfa_criteria_counts$percentage[2]`%**
* `r cfa_criteria_counts$cfa_rej_criteria[3]`: **`r cfa_criteria_counts$percentage[3]`%**
* `r cfa_criteria_counts$cfa_rej_criteria[6]`: **`r cfa_criteria_counts$percentage[6]`%**
* `r cfa_criteria_counts$cfa_rej_criteria[4]`: **`r cfa_criteria_counts$percentage[4]`%**
* `r cfa_criteria_counts$cfa_rej_criteria[5]`: **`r cfa_criteria_counts$percentage[5]`%**


## Rejected Cardiac ICs

* Studies reporting number: **`r cardiac_ic_stats$n_studies`**
* Range: **`r cardiac_ic_stats$min_ics`** - **`r cardiac_ic_stats$max_ics`**
* Median: **`r cardiac_ic_stats$median_ics`**


## Other CFA Removal Strategies

* `r other_cfa_strategies$strategy[3]`: **`r other_cfa_strategies$n[3]`** studies (**`r other_cfa_strategies$percentage[3]`%**)
* `r other_cfa_strategies$strategy[4]`: **`r other_cfa_strategies$n[4]`** studies (**`r other_cfa_strategies$percentage[4]`%**)
* `r other_cfa_strategies$strategy[5]`: **`r other_cfa_strategies$n[5]`** studies (**`r other_cfa_strategies$percentage[5]`%**)
* `r other_cfa_strategies$strategy[6]`: **`r other_cfa_strategies$n[6]`** studies (**`r other_cfa_strategies$percentage[6]`%**)

## Limit time range / analysis window

* `r other_cfa_strategies$strategy[1]`: `r other_cfa_strategies$n[1]` studies (`r other_cfa_strategies$percentage[1]`%)
* `r other_cfa_strategies$strategy[2]`: **`r other_cfa_strategies$n[2]`** studies (`r other_cfa_strategies$percentage[2]`%)

## Studies Without Any CFA Approach

* Studies with no CFA approach: **`r no_cfa_stats$pct_with_no_cfa`%** (**`r no_cfa_stats$studies_with_no_cfa`**/**`r no_cfa_stats$total_studies`**)
* Studies with other CFA strategies: **`r no_cfa_stats$pct_with_other_cfa`%** (**`r no_cfa_stats$studies_with_other_cfa`**/**`r no_cfa_stats$total_studies`**)
* Studies with any CFA approach: **`r no_cfa_stats$pct_with_any_cfa`%** (**`r no_cfa_stats$studies_with_any_cfa`**/**`r no_cfa_stats$total_studies`**)

### By Modality:

* EEG: **`r no_cfa_by_modality$pct_with_no_cfa[no_cfa_by_modality$modality == "EEG"]`%** (**`r no_cfa_by_modality$studies_with_no_cfa[no_cfa_by_modality$modality == "EEG"]`**/**`r no_cfa_by_modality$total_studies[no_cfa_by_modality$modality == "EEG"]`** studies) with no CFA approach
* MEG: **`r no_cfa_by_modality$pct_with_no_cfa[no_cfa_by_modality$modality == "MEG"]`%** (**`r no_cfa_by_modality$studies_with_no_cfa[no_cfa_by_modality$modality == "MEG"]`**/**`r no_cfa_by_modality$total_studies[no_cfa_by_modality$modality == "MEG"]`** studies) with no CFA approach

## HEP Time Windows

```{r timewindows}
# HEP reference scheme distribution (ALL pipelines, regardless of time window data)
hep_reference_all_pipelines <- df_pipelines %>%
  filter(!is.na(hep_relative_to) & hep_relative_to != "unknown") %>%
  count(hep_relative_to, sort = TRUE) %>%
  mutate(percentage = round(n / sum(n) * 100, 1))

# HEP window type analysis (Primary vs Secondary window selection)
hep_window_type_analysis <- df_pipelines %>%
  filter(!is.na(hep_window_type) & hep_window_type != "unknown") %>%
  count(hep_window_type, sort = TRUE) %>%
  mutate(percentage = round(n / sum(n) * 100, 1))

# HEP Time of Interest windows (for window range analysis)
hep_window_data <- df_pipelines %>%
  filter(!hep_start %in% c("none", "unknown"),
         !hep_end %in% c("none", "unknown")) %>%
  mutate(
    start_time = as.numeric(hep_start),
    end_time = as.numeric(hep_end)
  ) %>%
  filter(!is.na(start_time), !is.na(end_time)) %>%
  distinct(PMID, hep_start, hep_end, hep_relative_to, .keep_all = TRUE)

# T-peak and R-peak window ranges
tpeak_window_stats <- hep_window_data %>%
  filter(hep_relative_to == "T-peak") %>%
  summarise(
    start_min = min(start_time),
    start_max = max(start_time),
    end_min = min(end_time),
    end_max = max(end_time),
    # Convert to R-peak equivalent timing (T-peak ~300ms after R-peak)
    rpeak_equiv_start_min = start_min + 300,
    rpeak_equiv_start_max = start_max + 300,
    rpeak_equiv_end_min = end_min + 300,
    rpeak_equiv_end_max = end_max + 300
  )

rpeak_window_stats <- hep_window_data %>%
  filter(hep_relative_to == "R-peak") %>%
  summarise(
    start_min = min(start_time),
    start_max = max(start_time),
    end_min = min(end_time),
    end_max = max(end_time)
  )

# Find the overlap region for R-peak studies
rpeak_overlap_analysis <- hep_window_data %>%
  filter(hep_relative_to == "R-peak") %>%
  {
    rpeak_data <- .
    median_start <- median(rpeak_data$start_time, na.rm = TRUE)
    median_end <- median(rpeak_data$end_time, na.rm = TRUE)
    studies_including_core <- rpeak_data %>%
      filter(start_time <= median_start & end_time >= median_end) %>%
      nrow()
    core_percentage <- round(studies_including_core / nrow(rpeak_data) * 100, 1)
    list(
      core_start = round(median_start, 0),
      core_end = round(median_end, 0),
      core_percentage = core_percentage
    )
  }

# Baseline window analysis 
baseline_window_data <- df_pipelines %>%
  filter(!is.na(baseline_start_ms), !is.na(baseline_end_ms)) %>%
  mutate(
    baseline_start_numeric = as.numeric(baseline_start_ms),
    baseline_end_numeric = as.numeric(baseline_end_ms)
  ) %>%
  filter(!is.na(baseline_start_numeric), !is.na(baseline_end_numeric))

baseline_pct <- round(nrow(baseline_window_data) / nrow(df_pipelines) * 100, 1)

# T-peak baseline analysis
tpeak_baseline_data <- baseline_window_data %>%
  filter(hep_relative_to == "T-peak") %>%
  summarise(
    n_studies = n_distinct(PMID),
    start_min = min(baseline_start_numeric),
    end_max = max(baseline_end_numeric)
  )

# R-peak baseline analysis
rpeak_baseline_data <- baseline_window_data %>%
  filter(hep_relative_to == "R-peak") %>%
  summarise(
    n_studies = n_distinct(PMID),
    start_min = min(baseline_start_numeric),
    end_max = max(baseline_end_numeric)
  )

# Baseline ending before QRS analysis
baseline_before_qrs_stats <- baseline_window_data %>%
  filter(hep_relative_to == "R-peak") %>%
  mutate(baseline_ends_before_qrs = baseline_end_numeric < 0) %>%
  summarise(
    total_studies = n_distinct(PMID),
    studies_before_qrs = n_distinct(PMID[baseline_ends_before_qrs]),
    percentage_before_qrs = round(studies_before_qrs / total_studies * 100, 1)
  )

# Significant effects analysis by method and reference
# Exact copy of plotting code logic from create_single_ecg_plot.R
df_signif <- df_pipelines %>% filter(significant_test == 1)

# Create merged start/end/ref columns exactly like plotting code
df_signif <- df_signif %>%
  mutate(
    merged_start = if_else(averaging_time == "1", as.character(hep_start), as.character(significant_start_ms)),
    merged_end   = if_else(averaging_time == "1", as.character(hep_end), as.character(significant_end_ms)),
    merged_ref   = if_else(averaging_time == "1", hep_relative_to, significant_relative_to)
  )

# Process exactly like create_time_windows_plot.R does for significant effects
significant_effects_data <- df_signif %>%
  filter(merged_ref %in% c("R-peak", "T-peak"), significant_test == 1) %>%
  mutate(
    hep_start = as.numeric(hep_start),
    hep_end   = as.numeric(hep_end),
    significant_start_ms = as.numeric(significant_start_ms),
    significant_end_ms   = as.numeric(significant_end_ms),
    start_time = if_else(averaging_time == "1", hep_start, significant_start_ms),
    end_time   = if_else(averaging_time == "1", hep_end, significant_end_ms),
    reference = merged_ref,
    # Add method_category for statistical comparison
    method_category = case_when(
      averaging_time == "1" & clustering == "0" ~ "Averaging",
      clustering == "1" & averaging_time == "0" ~ "Clustering",
      TRUE ~ "Other"
    )
  ) %>%
  filter(!is.na(start_time), !is.na(end_time))

# Overall significant effects ranges
sig_rpeak_range <- significant_effects_data %>%
  filter(reference == "R-peak") %>%
  summarise(
    start_min = min(start_time),
    start_max = max(start_time),
    end_min = min(end_time),
    end_max = max(end_time)
  )

sig_tpeak_range <- significant_effects_data %>%
  filter(reference == "T-peak") %>%
  summarise(
    start_min = min(start_time),
    start_max = max(start_time),
    end_min = min(end_time),
    end_max = max(end_time)
  )

# Method-specific analysis (clustering vs averaging) is now handled in the main statistical comparison chunk
# The chunks 'clustering_effects', 'averaging_effects', and the peak calculation chunks are removed as they are redundant.

# Statistical comparison for clustering vs averaging methods
# Function to find peak distribution values (like in cumulative plots) and compare them

# Helper function to calculate cumulative counts (from utils.R)
calculate_cumulative_counts <- function(df_subset, time_vec) { 
  if (nrow(df_subset) == 0) {
    return(rep(0, length(time_vec)))
  }
  counts <- numeric(length(time_vec))
  # Small offset to ensure intervals are checked correctly [start, end)
  precision_offset <- (time_vec[2] - time_vec[1]) / 2 

  for (i in 1:nrow(df_subset)) {
    start_i <- df_subset$start_time[i]
    end_i <- df_subset$end_time[i]
    
    # Skip if missing values
    if (is.na(start_i) || is.na(end_i)) next
    
    # Find time points that fall within this interval
    indices <- which(time_vec >= (start_i - precision_offset) & time_vec < (end_i - precision_offset))
    if (length(indices) > 0) {
      counts[indices] <- counts[indices] + 1
    }
  }
  return(counts) 
}

calculate_peak_distribution <- function(method_data) {

  # Calculate cumulative distribution like in the plots
  all_times <- c(method_data$start_time, method_data$end_time)
  time_range <- seq(floor(min(all_times)), ceiling(max(all_times)), by = 1)
  counts <- calculate_cumulative_counts(method_data, time_range)
  
  # Find peak of distribution - where most effects occur
  peak_time <- time_range[which.max(counts)]
  
  return(list(
    peak_time = peak_time,
    max_count = max(counts)
  ))
}

perform_statistical_comparison <- function(method1_data, method2_data) {

  # Calculate distributions for both methods
  dist1 <- calculate_peak_distribution(method1_data)
  dist2 <- calculate_peak_distribution(method2_data)
  
  # If peaks are identical or one has no data, skip statistical comparison
  if(is.na(dist1$peak_time) || is.na(dist2$peak_time) || 
     dist1$max_count == 0 || dist2$max_count == 0) {
    
    return(list(
      test_performed = FALSE,
      peak1 = dist1$peak_time,
      peak2 = dist2$peak_time,
      reason = "Insufficient data for comparison"
    ))
  }
  
  # Perform permutation test for peak difference
  observed_peak_diff <- abs(dist1$peak_time - dist2$peak_time)
  
  # Combine all data for permutation
  combined_data <- rbind(method1_data, method2_data)
  n1 <- nrow(method1_data)
  n2 <- nrow(method2_data)
  n_total <- n1 + n2
  
  # Perform permutation test (1000 permutations)
  n_permutations <- 1000
  set.seed(42) # For reproducibility
  permuted_diffs <- numeric(n_permutations)
  
  for(i in 1:n_permutations) {
    # Randomly permute the combined data
    shuffled_indices <- sample(n_total)
    perm_group1 <- combined_data[shuffled_indices[1:n1], ]
    perm_group2 <- combined_data[shuffled_indices[(n1+1):n_total], ]
    
    # Calculate peak difference for this permutation
    perm_dist1 <- calculate_peak_distribution(perm_group1)
    perm_dist2 <- calculate_peak_distribution(perm_group2)
    
    if(!is.na(perm_dist1$peak_time) && !is.na(perm_dist2$peak_time)) {
      permuted_diffs[i] <- abs(perm_dist1$peak_time - perm_dist2$peak_time)
    } else {
      permuted_diffs[i] <- 0
    }
  }
  
  # Calculate p-value: proportion of permuted differences >= observed difference
  p_value_perm <- mean(permuted_diffs >= observed_peak_diff)
  
  return(list(
    test_performed = TRUE,
    # Peak times from cumulative distribution (what you see in plots)
    peak1 = dist1$peak_time,
    peak2 = dist2$peak_time,
    peak_difference = observed_peak_diff,
    max_count1 = dist1$max_count,
    max_count2 = dist2$max_count,
    # Permutation test results
    permutation_test_performed = TRUE,
    permutation_p_value = p_value_perm,
    n_permutations = n_permutations,
    n1 = n1,
    n2 = n2
  ))
}

stat_comparison_results <- list()

# R-peak analysis
clustering_rpeak <- significant_effects_data %>%
  filter(method_category == "Clustering", reference == "R-peak") %>%
  filter(!is.na(start_time), !is.na(end_time))

averaging_rpeak <- significant_effects_data %>%
  filter(method_category == "Averaging", reference == "R-peak") %>%
  filter(!is.na(start_time), !is.na(end_time))

stat_comparison_results$rpeak <- perform_statistical_comparison(clustering_rpeak, averaging_rpeak)

# T-peak analysis
clustering_tpeak <- significant_effects_data %>%
  filter(method_category == "Clustering", reference == "T-peak") %>%
  filter(!is.na(start_time), !is.na(end_time))

averaging_tpeak <- significant_effects_data %>%
  filter(method_category == "Averaging", reference == "T-peak") %>%
  filter(!is.na(start_time), !is.na(end_time))

stat_comparison_results$tpeak <- perform_statistical_comparison(clustering_tpeak, averaging_tpeak)
```

# Cardiac Reference Event Selection

* R-peak reference: **`r hep_reference_all_pipelines$percentage[hep_reference_all_pipelines$hep_relative_to == "R-peak"]`%** of pipelines
* T-wave reference: **`r hep_reference_all_pipelines$percentage[hep_reference_all_pipelines$hep_relative_to == "T-peak"]`%** of pipelines

# HEP Analysis Time Windows

## T-wave Referenced Analysis

* Time range: **`r tpeak_window_stats$start_min`** to **`r tpeak_window_stats$end_max`** ms after T-wave
* R-peak equivalent: approx. **`r tpeak_window_stats$rpeak_equiv_start_min`** to **`r tpeak_window_stats$rpeak_equiv_end_max`** ms after R-peak

## R-peak Referenced Analysis

* Time range: **`r rpeak_window_stats$start_min`** to **`r rpeak_window_stats$end_max`** ms relative to R-peak
* Core overlap window: **`r rpeak_overlap_analysis$core_start`** to **`r rpeak_overlap_analysis$core_end`** ms
* Pipelines including core: **`r rpeak_overlap_analysis$core_percentage`%**

# Baseline Correction

## General Statistics

* Pipelines using baseline correction: **`r baseline_pct`%**

## T-wave Baseline Correction

* Studies using baseline: **`r tpeak_baseline_data$n_studies`** studies
* Baseline window: **`r tpeak_baseline_data$start_min`** to **`r tpeak_baseline_data$end_max`** ms before T-wave

## R-peak Baseline Correction

* Baseline window range: **`r rpeak_baseline_data$start_min`** to **`r rpeak_baseline_data$end_max`** ms around R-peak
* Studies ending baseline before QRS: **`r baseline_before_qrs_stats$percentage_before_qrs`%**

# Significant HER Effects Time Ranges

## R-peak Referenced Effects

* Significant effects range: **`r sig_rpeak_range$start_min`** to **`r sig_rpeak_range$end_max`** ms

## T-wave Referenced Effects

* Significant effects range: **`r sig_tpeak_range$start_min`** to **`r sig_tpeak_range$end_max`** ms

# Statistical Analysis Methods Comparison

## R-peak Analysis

* **Peak Distribution Analysis** (from cumulative plots):
  - Clustering peak: **`r sprintf("%.0f", stat_comparison_results$rpeak$peak1)`** ms
  - Averaging peak: **`r sprintf("%.0f", stat_comparison_results$rpeak$peak2)`** ms
  - Peak difference: **`r sprintf("%.0f", abs(stat_comparison_results$rpeak$peak1 - stat_comparison_results$rpeak$peak2))`** ms

* **Statistical Test** (Permutation test on peak positions):
  - Sample sizes: n₁ = **`r stat_comparison_results$rpeak$n1`**, n₂ = **`r stat_comparison_results$rpeak$n2`**
  - Permutation test: p **`r ifelse(stat_comparison_results$rpeak$permutation_p_value < 0.001, "< 0.001", paste("=", sprintf("%.3f", stat_comparison_results$rpeak$permutation_p_value)))`** (**`r stat_comparison_results$rpeak$n_permutations`** permutations)

## T-wave Analysis

* **Peak Distribution Analysis** (from cumulative plots):
  - Clustering peak: **`r sprintf("%.0f", stat_comparison_results$tpeak$peak1)`** ms
  - Averaging peak: **`r sprintf("%.0f", stat_comparison_results$tpeak$peak2)`** ms
  - Peak difference: **`r sprintf("%.0f", abs(stat_comparison_results$tpeak$peak1 - stat_comparison_results$tpeak$peak2))`** ms

* **Statistical Test** (Permutation test on peak positions):
  - Sample sizes: n₁ = **`r stat_comparison_results$tpeak$n1`**, n₂ = **`r stat_comparison_results$tpeak$n2`**
  - Permutation test: p **`r ifelse(stat_comparison_results$tpeak$permutation_p_value < 0.001, "< 0.001", paste("=", sprintf("%.3f", stat_comparison_results$tpeak$permutation_p_value)))`** (**`r stat_comparison_results$tpeak$n_permutations`** permutations)

## Analysis Window Definition

* Pipelines with a-priori defined analysis windows: **`r hep_window_type_analysis$percentage[hep_window_type_analysis$hep_window_type == "Primary"]`%**
* Pipelines using two-step procedures (data-dependent window selection): **`r hep_window_type_analysis$percentage[hep_window_type_analysis$hep_window_type == "Secondary"]`%**
