---
title: "Manuscript Summary"
subtitle: "A Systematic Review of Methods Used for Studying Heartbeat Evoked Responses"
output: 
  html_document:
    self_contained: false
    theme: null
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
library(cowplot)
library(dplyr)
library(eegUtils)
library(grid)
library(gridExtra)
library(gridGraphics)
library(ggimage)
library(ggplot2)
library(ggtext)
library(magick)
library(PRISMA2020)
library(purrr)
library(scales)
library(stringr)
library(testit)
library(tidyr)
library(viridis)
library(zeallot)

data_path <- file.path(getwd(), '../data')
func_path <- file.path(getwd(), '.')
derivatives_path <- file.path(data_path, 'derivatives')
df_included <- read.csv(file.path(derivatives_path, 'included.csv'))
df_screening <- read.csv(file.path(derivatives_path, 'screening.csv'))

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      results = "asis")

# Create study-level and pipeline-level datasets for efficiency
df_studies <- df_included %>% distinct(PMID, .keep_all = TRUE)
df_pipelines <- df_included

# EEG-only datasets
eeg_studies <- df_studies %>% filter(modality == "EEG")
eeg_pipelines <- df_pipelines %>% filter(modality == "EEG")

meg_studies <- df_studies %>% filter(modality == "MEG")
meg_pipelines <- df_pipelines %>% filter(modality == "MEG")
```

# Overview

This document provides all values mentioned in the manuscript "Heartbeat-evoked responses in MEG/EEG: A systematic review of methods and suggestions for analysis and reporting". All sections of this document apart from this overview match the corresponding section of the manuscript. Numbers highlighted in **bold** are also present in the manuscript.

## Important Distinction: Studies vs Pipelines

- **Studies**: Unique publications (identified by PMID). Each study represents one research paper.
- **Pipelines**: Individual analysis approaches within studies. Some studies report multiple analysis pipelines (e.g. different time windows, or statistical approaches).

# Methods

## Literature search

```{r data-export}
# Load the search data files
exports_path <- file.path(data_path, 'exports')

df_query1 <- read.csv(file.path(exports_path, '20240115_pubmed_query1.csv'))
df_query2 <- read.csv(file.path(exports_path, '20240724_pubmed_query2.csv'))
df_query2_rerun <- read.csv(file.path(exports_path, '20240805_pubmed_query2.csv'))
df_query3 <- read.csv(file.path(exports_path, '20240805_pubmed_query3.csv'))

df_merged <- df_query1 %>%
  bind_rows(df_query2) %>%
  bind_rows(df_query2_rerun) %>%
  bind_rows(df_query3) %>%
  distinct(PMID)
```

Table 1 - number of retrieved papers:

* 15.01.2024: **`r nrow(df_query1)`**
* 24.07.2024: **`r nrow(df_query2)`** (rerun: **`r nrow(df_query2_rerun)`**)
* 05.08.2024: **`r nrow(df_query3)`**
* After removing duplicates: **`r nrow(df_merged)`**

```{r literature-search, results='asis'}
screening_pubmed <- df_screening[df_screening$source == "pubmed",]
screening_manual <- df_screening[df_screening$source == "manual",]

total_retrieved_pubmed <- nrow(screening_pubmed)
total_included_pubmed <- nrow(screening_pubmed[screening_pubmed$Include == 1,])
total_retrieved_manual <- nrow(screening_manual)
total_included_manual <- nrow(screening_manual[screening_manual$Include == 1,])
```

Exported from Pubmed:

* Retrieved: **`r total_retrieved_pubmed`** studies
* Included: **`r total_included_pubmed`** studies

Manually added:

* Retrieved: **`r total_retrieved_manual`** studies
* Included: **`r total_included_manual`** studies

Final sample: **`r total_included_pubmed + total_included_manual`** studies

# Results

## Overview of the included studies

```{r literature-overview}
# Basic counts
total_pipelines <- nrow(df_pipelines)
total_studies <- nrow(df_studies)

# Year range (based on unique studies)
year_range <- df_studies %>% 
  summarise(min_year = min(Year, na.rm = TRUE), max_year = max(Year, na.rm = TRUE))

# Modality breakdown (unique studies)
modality_counts <- df_studies %>%
  count(modality) %>%
  mutate(percentage = round(n / sum(n) * 100, 1))
modality_eeg <- as.list(modality_counts[modality_counts$modality == "EEG",])
modality_meg <- as.list(modality_counts[modality_counts$modality == "MEG",])

# Task vs resting state - studies that have both vs only one type
study_types <- df_pipelines %>%
  filter(!is.na(rsHEP)) %>%
  group_by(PMID) %>%
  summarise(
    has_resting = any(rsHEP == 1),
    has_task = any(rsHEP == 0),
    .groups = "drop"
  ) %>%
  mutate(
    category = case_when(
      has_resting & has_task ~ "Both",
      has_resting & !has_task ~ "Rest", 
      !has_resting & has_task ~ "Task",
      TRUE ~ "Other"
    )
  ) %>%
  count(category) %>%
  mutate(percentage = round(n / sum(n) * 100, 1))
assert("All studies perform either task-based or resting-state analysis",
       nrow(study_types[study_types$category == "Other",]) == 0)

study_type_task <- as.list(study_types[study_types$category == "Task",])
study_type_rest <- as.list(study_types[study_types$category == "Rest",])
study_type_both <- as.list(study_types[study_types$category == "Both",])
```

```{r overview-stats}
# Calculate final sample stats
final_sample_stats <- df_studies %>%
  summarise(
    total_studies = n(),
    year_min = min(Year, na.rm = TRUE),
    year_max = max(Year, na.rm = TRUE)
  )

# Modality breakdown
modality_breakdown <- df_studies %>%
  count(modality) %>%
  mutate(percentage = round(n / sum(n) * 100, 1))

eeg_stats <- modality_breakdown %>% filter(modality == "EEG")
meg_stats <- modality_breakdown %>% filter(modality == "MEG")
```

In total, **`r final_sample_stats$total_studies`** studies published between **`r final_sample_stats$year_min`** and **`r final_sample_stats$year_max`** were included in the review. The vast majority of studies used EEG recordings (**`r eeg_stats$n`** studies, **`r eeg_stats$percentage`%**), while only **`r meg_stats$n`** studies (**`r meg_stats$percentage`%**) employed MEG to measure HERs.

Study type distribution:

* Task-based: **`r study_type_task$n`** studies (**`r study_type_task$percentage`%**)
* Resting-state: **`r study_type_rest$n`** studies (**`r study_type_rest$percentage`%**)
* Both: **`r study_type_both$n`** studies (**`r study_type_both$percentage`%**)

## Overview of methodological choices

```{r variations}
```

## M/EEG Acquisition & Preprocessing

### Channel Information

```{r channels}
# EEG channel statistics
channel_data <- eeg_studies %>%
  filter(!is.na(meeg_num_electrodes) & meeg_num_electrodes != "unknown") %>%
  distinct(PMID, meeg_num_electrodes) %>%
  mutate(channels_numeric = as.numeric(meeg_num_electrodes)) %>%
  filter(!is.na(channels_numeric))

channel_stats <- channel_data %>%
  summarise(
    min_channels = min(channels_numeric, na.rm = TRUE),
    max_channels = max(channels_numeric, na.rm = TRUE),
    median_channels = median(channels_numeric, na.rm = TRUE),
    n_studies = n()
  )
```

### Reference Schemes

```{r references}
# Reference processing
major_categories <- tolower(c(
  "Cz", "Nose", "Linked earlobes", "Linked mastoids",
  "FCz", "Common average", "Fpz", "CMS", "CMS and DRL",
  "unknown", "Laplacian reference", "REST"
))

# Process reference categories
eeg_studies_ref <- eeg_studies %>%
  mutate(across(
    .cols = c(reference_online, reference_offline),
    .fns = ~ case_when(
      tolower(.) %in% major_categories ~ tolower(.),
      TRUE ~ "Other"
    )
  ))

# Common reference category mapping 
ref_categories <- c(
  "common average" = "CAR",
  "linked mastoids" = "LM", 
  "linked earlobes" = "LE",
  "cz" = "Cz",
  "fcz" = "FCz",
  "fpz" = "Fpz",
  "cms" = "CMS",
  "cms and drl" = "CMS",
  "nose" = "Nose",
  "laplacian reference" = "LAP",
  "rest" = "REST",
  "other" = "Other",
  "unknown" = "N/M"
)

# Online reference distribution (studies) 
online_ref_counts <- eeg_studies_ref %>%
  filter(!is.na(reference_online)) %>%
  count(reference_online) %>%
  filter(reference_online %in% names(ref_categories)) %>%
  mutate(
    display_name = ref_categories[reference_online],
    percentage = round(n / sum(n) * 100, 1)
  ) %>%
  arrange(desc(n))

# Offline reference distribution (studies)
offline_ref_counts <- eeg_studies_ref %>%
  filter(!is.na(reference_offline)) %>%
  count(reference_offline) %>%
  filter(reference_offline %in% names(ref_categories)) %>%
  mutate(
    display_name = ref_categories[reference_offline],
    percentage = round(n / sum(n) * 100, 1)
  ) %>%
  arrange(desc(n))
```

For the data acquisition, we can observe some variability with respect to the used online reference. This variability is reduced during data processing, where the dominant choice is Common Average Reference (CAR, used in **`r offline_ref_counts$percentage[offline_ref_counts$display_name == "CAR"]`%** of the studies).

### Artifact Removal

```{r artifacts}
# Artifact removal statistics (pipelines)
artifact_stats <- df_pipelines %>%
  summarise(
    # Noisy epochs removal 
    noisy_epochs_pct = round(mean(grepl("noisy epoch", other_cleaning_strategy, ignore.case = TRUE) %in% TRUE, na.rm = TRUE) * 100, 0),
    
    # Bad channels removal 
    bad_channels_pct = round(mean(grepl("bad channels", other_cleaning_strategy, ignore.case = TRUE) %in% TRUE, na.rm = TRUE) * 100, 0),
    
    # Blink/EOG correction
    blink_correction_pct = round(mean(grepl("blink|eye|gratton", other_cleaning_strategy, ignore.case = TRUE) %in% TRUE, na.rm = TRUE) * 100, 0),

    # ICA usage
    ica_pct = round(mean(ICA == 1, na.rm = TRUE) * 100, 1),
    
    # Studies with ICA
    n_ica_pipelines = sum(ICA == 1, na.rm = TRUE),
    total_pipelines = n() 
  )

# Studies using ICA (unique studies)
ica_studies <- df_pipelines %>%
  group_by(PMID) %>%
  summarise(uses_ica = any(ICA == 1, na.rm = TRUE)) %>%
  summarise(
    n_ica_studies = sum(uses_ica),
    total_studies = n(),
    ica_study_pct = round(mean(uses_ica) * 100, 1)
  )

# Component rejection types (studies with ICA)
component_types_df <- df_pipelines %>%
  filter(ICA == 1) %>%
  distinct(PMID, rejected_components) %>%
  filter(rejected_components != "", rejected_components != "unknown") %>%
  mutate(pipeline_id = row_number())

# Clean rejected_components
component_types_df$rejected_components <- sapply(component_types_df$rejected_components, function(x) {
  x <- gsub("[\r\n]+", ",", x)    
  x <- gsub(",+", ",", x)         
  x <- gsub("^,|,$", "", x)       
  comps <- unlist(strsplit(x, ","))
  comps <- unique(trimws(comps))
  comps <- comps[comps != ""]
  paste(comps, collapse = ",")
})

# Count total studies before splitting
total_ica_studies <- nrow(component_types_df)

component_types <- component_types_df %>%
  separate_rows(rejected_components, sep = ",") %>%
  mutate(
    rejected_components = trimws(rejected_components),
    rejected_components = tolower(rejected_components)
  ) %>%
  # Apply component mapping
  mutate(rejected_components = case_when(
    rejected_components == "eye movements" ~ "Ocular",
    rejected_components == "blinks" ~ "Ocular", 
    rejected_components == "muscle" ~ "Muscle",
    rejected_components == "cfa" ~ "CFA",
    rejected_components == "channel noise" ~ "Channel noise",
    rejected_components == "line noise" ~ "Line noise",
    rejected_components == "other" ~ "Other",
    TRUE ~ rejected_components
  )) %>%
  filter(rejected_components != "") %>%
  group_by(rejected_components) %>%
  summarise(count = n_distinct(pipeline_id), .groups = "drop") %>%
  arrange(desc(count)) %>%
  mutate(percentage = round(count / total_ica_studies * 100, 1))
```

## Artifact Removal Statistics

In terms of artifact reduction, many studies reported the removal of noisy epochs (**`r artifact_stats$noisy_epochs_pct`%**) and bad channels (**`r artifact_stats$bad_channels_pct`%**). Independent Component Analysis (ICA) is by far the most commonly used technique used by **`r ica_studies$ica_study_pct`%** of all studies to remove artifacts related to cardiac, eye movement, muscle or other nuisance sources.

### ICA Usage Statistics

* Studies using ICA: **`r ica_studies$ica_study_pct`%** (**`r ica_studies$n_ica_studies`**/**`r ica_studies$total_studies`**)

### ICA Component Types Removed

* `r component_types$rejected_components[1]`: **`r component_types$percentage[1]`%**
* `r component_types$rejected_components[2]`: **`r component_types$percentage[2]`%**
* `r component_types$rejected_components[3]`: **`r component_types$percentage[3]`%**
* remaining noise components: **`r component_types$percentage[4] + component_types$percentage[5] + component_types$percentage[6]`%**
## Filter Settings

```{r filters}
# Filter statistics
filter_data <- df_pipelines %>%
  filter(!is.na(high_pass) & !is.na(low_pass)) %>%
  distinct(PMID, high_pass, low_pass, .keep_all = TRUE)

filter_stats <- filter_data %>%
  summarise(
    n_valid = n(),
    high_pass_range_min = min(high_pass, na.rm = TRUE),
    high_pass_range_max = max(high_pass, na.rm = TRUE),
    low_pass_range_min = min(low_pass, na.rm = TRUE), 
    low_pass_range_max = max(low_pass, na.rm = TRUE)
  )

# Most common high-pass filter values (studies)
common_highpass <- filter_data %>%
  count(high_pass, sort = TRUE) %>%
  head(3)

# Most common low-pass filter values (studies)
common_lowpass <- filter_data %>%
  count(low_pass, sort = TRUE) %>%
  head(3)

```

## Filter Settings

When analysing relatively slow evoked responses, like the HER, optimal filter settings are an important consideration to not remove or induce effects. We observe that across studies, filtering is most frequently done between **`r common_highpass$high_pass[1]` Hz** and **`r common_lowpass$low_pass[1]` Hz**, with the most dominant high-pass filter cutoffs at **`r paste(common_highpass$high_pass, collapse = ", ")` Hz** (Fig. 3E).

# ECG Acquisition

```{r ecg}
```

# Dealing with cardiac field artifacts

```{r cfa}
# ICA timing (studies using ICA)
ica_timing <- df_studies %>%
  filter(ICA == 1 & !is.na(ica_on_epochs)) %>%
  count(ica_on_epochs) %>%
  mutate(
    timing = case_when(
      ica_on_epochs == 0 ~ "Continuous",
      ica_on_epochs == 1 ~ "Epoched",
      TRUE ~ "Unknown"
    ),
    percentage = round(n / sum(n) * 100, 1)
  )

# CFA identification approaches (studies)
cfa_approach_counts <- df_studies %>%
  filter(!is.na(cfa_rej_approach) & 
         cfa_rej_approach != "" & 
         tolower(str_trim(cfa_rej_approach)) != "unknown") %>%
  mutate(cfa_rej_approach_clean = str_to_title(tolower(str_trim(cfa_rej_approach)))) %>%
  count(cfa_rej_approach_clean, sort = TRUE) %>%
  mutate(percentage = round(n / sum(n) * 100, 1)) %>%
  rename(cfa_rej_approach = cfa_rej_approach_clean)

# CFA identification criteria (studies)
cfa_criteria_counts <- df_studies %>%
  mutate(cfa_rej_criteria = tolower(cfa_rej_criteria)) %>%
  filter(!is.na(cfa_rej_criteria), cfa_rej_criteria != "", cfa_rej_criteria != "unknown") %>%
  distinct(PMID, cfa_rej_criteria) %>%
  mutate(pipeline_id = row_number()) %>%
  separate_rows(cfa_rej_criteria, sep = ",") %>%
  mutate(
    cfa_rej_criteria = str_replace_all(cfa_rej_criteria, "[\r\n]", " "),
    cfa_rej_criteria = str_trim(cfa_rej_criteria, side = "both"),
    cfa_rej_criteria = case_when(
      cfa_rej_criteria == "time course" ~ "Time Course",
      cfa_rej_criteria == "topography" ~ "Topography", 
      cfa_rej_criteria == "power spectrum" ~ "Power Spectrum",
      cfa_rej_criteria == "phase consistency" ~ "Phase Consistency",
      cfa_rej_criteria == "iclabel" ~ "Algorithm",
      cfa_rej_criteria == "corrmap" ~ "Algorithm",
      cfa_rej_criteria == "correlation" ~ "Correlation",
      cfa_rej_criteria == "sasica" ~ "Algorithm",
      TRUE ~ str_to_title(cfa_rej_criteria)
    )
  ) %>%
  filter(cfa_rej_criteria != "", cfa_rej_criteria != "unknown") %>%
  distinct(pipeline_id, cfa_rej_criteria, .keep_all = TRUE) %>%
  group_by(cfa_rej_criteria) %>%
  summarise(count = n_distinct(pipeline_id), .groups = "drop") %>%
  arrange(desc(count)) %>%
  mutate(
    total_pipelines = length(unique(df_studies$PMID[!is.na(df_studies$cfa_rej_criteria) & 
                                                    df_studies$cfa_rej_criteria != "" & 
                                                    tolower(df_studies$cfa_rej_criteria) != "unknown"])),
    percentage = round(count / total_pipelines * 100, 1)
  )

# Number of rejected cardiac ICs (studies)
cardiac_ic_stats <- df_studies %>%
  filter(!is.na(rejected_cardiac_ics)) %>%
  summarise(
    n_studies = n(),
    min_ics = min(rejected_cardiac_ics, na.rm = TRUE),
    max_ics = max(rejected_cardiac_ics, na.rm = TRUE),
    median_ics = median(rejected_cardiac_ics, na.rm = TRUE)
  )

# Other CFA removal strategies (studies)
other_cfa_strategies <- df_studies %>%
  filter(!is.na(other_cfa_removal_strategy) & 
         other_cfa_removal_strategy != "" & 
         tolower(str_trim(other_cfa_removal_strategy)) != "unknown") %>%
  mutate(
    # Clean and standardize strategy names
    strategy_clean = case_when(
      other_cfa_removal_strategy == "limit analysis to time of minimal artifact" ~ 
        "Minimal artifact window",
      str_detect(tolower(other_cfa_removal_strategy), "^rr at least") ~ 
        "RR interval\nconstraints",
      tolower(other_cfa_removal_strategy) %in% c(
        "subtract/regress ecg from eeg"
      ) ~ "Subtract/regress ECG from EEG",
      tolower(other_cfa_removal_strategy) == "subtract rshep from taskhep" ~ 
        "subtract rsHEP\nfrom task HEP",
      tolower(other_cfa_removal_strategy) == "pca on heps" ~ "PCA on\nHEP",
            tolower(other_cfa_removal_strategy) == "csd" ~ "CSD",
      TRUE ~ str_to_title(str_trim(other_cfa_removal_strategy))
    )
  ) %>%
  count(strategy_clean, sort = TRUE) %>%
  mutate(percentage = round(n / sum(n) * 100, 1)) %>%
  rename(strategy = strategy_clean)
```

## ICA Application Timing

Independent component analysis (ICA) is by far the most commonly used technique used by **`r ica_studies$ica_study_pct`%** of all studies

* Continuous: **`r if(nrow(ica_timing[ica_timing$timing == "Continuous",]) > 0) ica_timing$percentage[ica_timing$timing == "Continuous"] else 0`%**
* Epoched: **`r if(nrow(ica_timing[ica_timing$timing == "Epoched",]) > 0) ica_timing$percentage[ica_timing$timing == "Epoched"] else 0`%**

## CFA Identification Approaches

* Not reported: **`r round((1 - sum(cfa_approach_counts$n) / ica_studies$n_ica_studies) * 100, 1)`%** of studies using ICA
* `r cfa_approach_counts$cfa_rej_approach[1]`: **`r cfa_approach_counts$percentage[1]`%**
* `r cfa_approach_counts$cfa_rej_approach[2]`: **`r cfa_approach_counts$percentage[2]`%**
* `r cfa_approach_counts$cfa_rej_approach[3]`: **`r cfa_approach_counts$percentage[3]`%**

## CFA Identification Criteria

* `r cfa_criteria_counts$cfa_rej_criteria[1]`: **`r cfa_criteria_counts$percentage[1]`%**
* `r cfa_criteria_counts$cfa_rej_criteria[2]`: **`r cfa_criteria_counts$percentage[2]`%**
* `r cfa_criteria_counts$cfa_rej_criteria[3]`: **`r cfa_criteria_counts$percentage[3]`%**
* `r cfa_criteria_counts$cfa_rej_criteria[6]`: **`r cfa_criteria_counts$percentage[6]`%**
* `r cfa_criteria_counts$cfa_rej_criteria[4]`: **`r cfa_criteria_counts$percentage[4]`%**
* `r cfa_criteria_counts$cfa_rej_criteria[5]`: **`r cfa_criteria_counts$percentage[5]`%**


## Rejected Cardiac ICs

* Studies reporting number: **`r cardiac_ic_stats$n_studies`**
* Range: **`r cardiac_ic_stats$min_ics`** - **`r cardiac_ic_stats$max_ics`**
* Median: **`r cardiac_ic_stats$median_ics`**

```{r no-cfa-analysis}
# Papers with no CFA approach (studies level)
no_cfa_analysis <- df_studies %>%
  mutate(
    # Check if study uses ICA AND mentions CFA in rejected components
    uses_ica_for_cfa = (ICA == 1 & 
                        rejected_components != "" &
                        rejected_components != "unknown" &
                        grepl("CFA", rejected_components, ignore.case = TRUE)),
    # Check if study has other CFA removal strategies
    has_other_cfa = (!is.na(other_cfa_removal_strategy) & 
                     other_cfa_removal_strategy != "" & 
                     tolower(str_trim(other_cfa_removal_strategy)) != "unknown"),
    # Study has some CFA approach if it uses ICA for CFA OR has other CFA strategies
    has_any_cfa_approach = (uses_ica_for_cfa | has_other_cfa),
    # Study has no CFA approach if it doesn't use ICA for CFA AND has no other CFA strategies
    no_cfa_approach = !has_any_cfa_approach
  )

# Calculate summary statistics
no_cfa_stats <- no_cfa_analysis %>%
  summarise(
    total_studies = n(),
    studies_with_ica_for_cfa = sum(uses_ica_for_cfa, na.rm = TRUE),
    studies_with_other_cfa = sum(has_other_cfa, na.rm = TRUE),
    studies_with_any_cfa = sum(has_any_cfa_approach, na.rm = TRUE),
    studies_with_no_cfa = sum(no_cfa_approach, na.rm = TRUE),
    pct_with_ica_for_cfa = round(studies_with_ica_for_cfa / total_studies * 100, 1),
    pct_with_other_cfa = round(studies_with_other_cfa / total_studies * 100, 1),
    pct_with_any_cfa = round(studies_with_any_cfa / total_studies * 100, 1),
    pct_with_no_cfa = round(studies_with_no_cfa / total_studies * 100, 1)
  )

# Breakdown by modality
no_cfa_by_modality <- df_studies %>%
  mutate(
    uses_ica_for_cfa = (ICA == 1 & 
                        !is.na(rejected_components) & 
                        rejected_components != "" &
                        rejected_components != "unknown" &
                        grepl("cfa|cardiac", rejected_components, ignore.case = TRUE)),
    has_other_cfa = (!is.na(other_cfa_removal_strategy) & 
                     other_cfa_removal_strategy != "" & 
                     tolower(str_trim(other_cfa_removal_strategy)) != "unknown"),
    has_any_cfa_approach = (uses_ica_for_cfa | has_other_cfa),
    no_cfa_approach = !has_any_cfa_approach
  ) %>%
  group_by(modality) %>%
  summarise(
    total_studies = n(),
    studies_with_no_cfa = sum(no_cfa_approach, na.rm = TRUE),
    pct_with_no_cfa = round(studies_with_no_cfa / total_studies * 100, 1),
    .groups = "drop"
  )
```

## Other CFA Removal Strategies

* `r other_cfa_strategies$strategy[1]`: **`r other_cfa_strategies$n[1]`** studies (**`r other_cfa_strategies$percentage[1]`%**)
* `r other_cfa_strategies$strategy[2]`: **`r other_cfa_strategies$n[2]`** studies (**`r other_cfa_strategies$percentage[2]`%**)
* `r other_cfa_strategies$strategy[3]`: **`r other_cfa_strategies$n[3]`** studies (**`r other_cfa_strategies$percentage[3]`%**)

## Studies Without Any CFA Approach

* Studies with no CFA approach: **`r no_cfa_stats$pct_with_no_cfa`%** (**`r no_cfa_stats$studies_with_no_cfa`**/**`r no_cfa_stats$total_studies`**)
* Studies with ICA for CFA: **`r no_cfa_stats$pct_with_ica_for_cfa`%** (**`r no_cfa_stats$studies_with_ica_for_cfa`**/**`r no_cfa_stats$total_studies`**)
* Studies with other CFA strategies: **`r no_cfa_stats$pct_with_other_cfa`%** (**`r no_cfa_stats$studies_with_other_cfa`**/**`r no_cfa_stats$total_studies`**)
* Studies with any CFA approach: **`r no_cfa_stats$pct_with_any_cfa`%** (**`r no_cfa_stats$studies_with_any_cfa`**/**`r no_cfa_stats$total_studies`**)

### By Modality:

* EEG: **`r no_cfa_by_modality$pct_with_no_cfa[no_cfa_by_modality$modality == "EEG"]`%** (**`r no_cfa_by_modality$studies_with_no_cfa[no_cfa_by_modality$modality == "EEG"]`**/**`r no_cfa_by_modality$total_studies[no_cfa_by_modality$modality == "EEG"]`** studies) with no CFA approach
* MEG: **`r no_cfa_by_modality$pct_with_no_cfa[no_cfa_by_modality$modality == "MEG"]`%** (**`r no_cfa_by_modality$studies_with_no_cfa[no_cfa_by_modality$modality == "MEG"]`**/**`r no_cfa_by_modality$total_studies[no_cfa_by_modality$modality == "MEG"]`** studies) with no CFA approach
```

# HEP Time Windows

```{r timewindows}
# HEP Time of Interest windows
hep_window_data <- df_pipelines %>%
  filter(!hep_start %in% c("none", "unknown"),
         !hep_end %in% c("none", "unknown")) %>%
  mutate(
    start_time = as.numeric(hep_start),
    end_time = as.numeric(hep_end)
  ) %>%
  filter(!is.na(start_time), !is.na(end_time)) %>%
  distinct(PMID, hep_start, hep_end, hep_relative_to, .keep_all = TRUE)

# Overall HEP window statistics
hep_window_stats <- hep_window_data %>%
  summarise(
    n_pipelines = n(),
    start_range_min = min(start_time),
    start_range_max = max(start_time), 
    end_range_min = min(end_time),
    end_range_max = max(end_time),
    duration_min = min(end_time - start_time),
    duration_max = max(end_time - start_time)
  )

# HEP reference scheme distribution (studies with valid HEP windows)
hep_reference_counts <- hep_window_data %>%
  distinct(PMID, hep_relative_to) %>%
  filter(!is.na(hep_relative_to) & hep_relative_to != "unknown") %>%
  count(hep_relative_to, sort = TRUE) %>%
  mutate(percentage = round(n / sum(n) * 100, 1))

# R-peak specific analysis
rpeak_window_data <- hep_window_data %>%
  filter(hep_relative_to == "R-peak")

rpeak_window_stats <- if(nrow(rpeak_window_data) > 0) {
  rpeak_window_data %>%
    summarise(
      n_pipelines = n(),
      start_range_min = min(start_time),
      start_range_max = max(start_time),
      end_range_min = min(end_time),
      end_range_max = max(end_time),
      duration_min = min(end_time - start_time),
      duration_max = max(end_time - start_time)
    )
} else {
  data.frame(n_pipelines = 0, start_range_min = NA, start_range_max = NA,
             end_range_min = NA, end_range_max = NA, duration_min = NA, duration_max = NA)
}

# Most common R-peak time windows analysis
rpeak_common_windows <- if(nrow(rpeak_window_data) > 0) {
  rpeak_window_data %>%
    # Create time window strings for grouping
    mutate(time_window = paste(start_time, "to", end_time, "ms")) %>%
    count(time_window, start_time, end_time, sort = TRUE) %>%
    mutate(
      percentage = round(n / sum(n) * 100, 1),
      n_studies = n  # Since we used distinct(PMID, ...) in hep_window_data
    ) %>%
    head(5)  # Top 5 most common windows
} else {
  data.frame(time_window = character(0), start_time = numeric(0), 
             end_time = numeric(0), n = numeric(0), percentage = numeric(0), n_studies = numeric(0))
}

# Find the overlap region that most studies include
rpeak_overlap_analysis <- if(nrow(rpeak_window_data) > 0) {
  # Find the most common overlapping region
  all_start_times <- rpeak_window_data$start_time
  all_end_times <- rpeak_window_data$end_time
  
  # Use a more inclusive approach: find the region that most studies overlap with
  # Use median start time and median end time as core boundaries
  median_start <- median(all_start_times, na.rm = TRUE)
  median_end <- median(all_end_times, na.rm = TRUE)
  
  # Count how many studies include this core region (overlap with median start to median end)
  studies_including_core <- rpeak_window_data %>%
    filter(start_time <= median_start & end_time >= median_end) %>%
    nrow()
  
  core_percentage <- round(studies_including_core / nrow(rpeak_window_data) * 100, 1)
  
  
  list(
    core_start = round(median_start, 0),
    core_end = round(median_end, 0),
    studies_including_core = studies_including_core,
    total_rpeak_studies = nrow(rpeak_window_data),
    core_percentage = core_percentage
  )
} else {
  list(core_start = NA, core_end = NA, studies_including_core = 0, 
       total_rpeak_studies = 0, core_percentage = 0)
}

# T-peak specific analysis  
tpeak_window_data <- hep_window_data %>%
  filter(hep_relative_to == "T-peak")

tpeak_window_stats <- if(nrow(tpeak_window_data) > 0) {
  tpeak_window_data %>%
    summarise(
      n_pipelines = n(),
      start_range_min = min(start_time),
      start_range_max = max(start_time),
      end_range_min = min(end_time),
      end_range_max = max(end_time),
      duration_min = min(end_time - start_time),
      duration_max = max(end_time - start_time)
    )
} else {
  data.frame(n_pipelines = 0, start_range_min = NA, start_range_max = NA,
             end_range_min = NA, end_range_max = NA, duration_min = NA, duration_max = NA)
}

# Baseline window analysis 
baseline_window_data <- df_pipelines %>%
  filter(!is.na(baseline_start_ms), !is.na(baseline_end_ms)) %>%
  mutate(
    baseline_start_numeric = as.numeric(baseline_start_ms),
    baseline_end_numeric = as.numeric(baseline_end_ms)
  ) %>%
  filter(!is.na(baseline_start_numeric), !is.na(baseline_end_numeric))

baseline_stats <- baseline_window_data %>%
  summarise(
    n_pipelines = n(),
    start_range_min = min(baseline_start_numeric),
    start_range_max = max(baseline_start_numeric),
    end_range_min = min(baseline_end_numeric),
    end_range_max = max(baseline_end_numeric),
    duration_min = min(baseline_end_numeric - baseline_start_numeric),
    duration_max = max(baseline_end_numeric - baseline_start_numeric)
  )

baseline_pct <- round(nrow(baseline_window_data) / nrow(df_pipelines) * 100, 1)

# Baseline correction by reference peak (R-peak vs T-peak)
baseline_by_reference <- df_pipelines %>%
  filter(!is.na(baseline_start_ms), !is.na(baseline_end_ms),
         !is.na(hep_relative_to), hep_relative_to != "unknown") %>%
  mutate(
    baseline_start_numeric = as.numeric(baseline_start_ms),
    baseline_end_numeric = as.numeric(baseline_end_ms)
  ) %>%
  filter(!is.na(baseline_start_numeric), !is.na(baseline_end_numeric)) %>%
  group_by(hep_relative_to) %>%
  summarise(
    n_pipelines = n(),
    n_studies = n_distinct(PMID),
    start_range_min = min(baseline_start_numeric),
    start_range_max = max(baseline_start_numeric),
    end_range_min = min(baseline_end_numeric),
    end_range_max = max(baseline_end_numeric),
    .groups = "drop"
  )

# Analysis of baseline windows ending before QRS complex (to avoid CFA contamination)
baseline_before_qrs <- baseline_window_data %>%
  filter(!is.na(hep_relative_to), hep_relative_to != "unknown") %>%
  mutate(
    # For R-peak reference: baseline ends before 0 ms (QRS complex)
    # For T-peak reference: need to account for typical T-peak timing (~300ms after R-peak)
    baseline_ends_before_qrs = case_when(
      hep_relative_to == "R-peak" ~ baseline_end_numeric < 0,
      hep_relative_to == "T-peak" ~ baseline_end_numeric < 0, 
      TRUE ~ FALSE
    )
  )

# Calculate percentage of studies with baseline ending before QRS
baseline_before_qrs_stats <- baseline_before_qrs %>%
  summarise(
    total_studies_with_baseline = n_distinct(PMID),
    studies_ending_before_qrs = n_distinct(PMID[baseline_ends_before_qrs]),
    percentage_before_qrs = round(studies_ending_before_qrs / total_studies_with_baseline * 100, 1)
  )

# Breakdown by reference scheme
baseline_before_qrs_by_ref <- baseline_before_qrs %>%
  group_by(hep_relative_to) %>%
  summarise(
    total_studies = n_distinct(PMID),
    studies_ending_before_qrs = n_distinct(PMID[baseline_ends_before_qrs]),
    percentage_before_qrs = round(studies_ending_before_qrs / total_studies * 100, 1),
    .groups = "drop"
  )

# Significant effects window analysis (using method_category)
significant_effects_data <- df_pipelines %>%
  filter(significant_test == 1) %>%
  mutate(
    hep_start_numeric = as.numeric(hep_start),
    hep_end_numeric = as.numeric(hep_end),
    significant_start_numeric = as.numeric(significant_start_ms),
    significant_end_numeric = as.numeric(significant_end_ms),
    # Use HEP windows for Averaging, significant windows for Clustering
    start_time = case_when(
      method_category == "Averaging" ~ hep_start_numeric,
      method_category == "Clustering" ~ significant_start_numeric,
      TRUE ~ hep_start_numeric  
    ),
    end_time = case_when(
      method_category == "Averaging" ~ hep_end_numeric,
      method_category == "Clustering" ~ significant_end_numeric,
      TRUE ~ hep_end_numeric  
    ),
    reference = case_when(
      method_category == "Averaging" ~ hep_relative_to,
      method_category == "Clustering" ~ significant_relative_to,
      TRUE ~ hep_relative_to  
    )
  ) %>%
  filter(!is.na(start_time), !is.na(end_time))

significant_window_stats <- if(nrow(significant_effects_data) > 0) {
  significant_effects_data %>%
    summarise(
      n_pipelines = n(),
      start_range_min = min(start_time),
      start_range_max = max(start_time),
      end_range_min = min(end_time), 
      end_range_max = max(end_time),
      duration_min = min(end_time - start_time),
      duration_max = max(end_time - start_time)
    )
} else {
  data.frame(n_pipelines = 0, start_range_min = NA, start_range_max = NA,
             end_range_min = NA, end_range_max = NA, duration_min = NA, duration_max = NA)
}
```

## HEP Time Windows

* Pipelines with valid HEP windows: **`r hep_window_stats$n_pipelines`**
* Overall HEP start time range: **`r hep_window_stats$start_range_min`** to **`r hep_window_stats$start_range_max`** ms
* Overall HEP end time range: **`r hep_window_stats$end_range_min`** to **`r hep_window_stats$end_range_max`** ms
* Overall HEP window duration range: **`r hep_window_stats$duration_min`** to **`r hep_window_stats$duration_max`** ms

## HEP Reference Peak Distribution

* `r as.character(hep_reference_counts$hep_relative_to[1])`: **`r hep_reference_counts$n[1]`** studies (**`r hep_reference_counts$percentage[1]`%**)
* `r as.character(hep_reference_counts$hep_relative_to[2])`: **`r hep_reference_counts$n[2]`** studies (**`r hep_reference_counts$percentage[2]`%**)
* `r as.character(hep_reference_counts$hep_relative_to[3])`: **`r hep_reference_counts$n[3]`** studies (**`r hep_reference_counts$percentage[3]`%**)

## R-peak Referenced Analysis

`r if(rpeak_window_stats$n_pipelines > 0) paste0("* Pipelines using R-peak reference: **", rpeak_window_stats$n_pipelines, "**\n* R-peak start time range: **", rpeak_window_stats$start_range_min, "** to **", rpeak_window_stats$start_range_max, "** ms\n* R-peak end time range: **", rpeak_window_stats$end_range_min, "** to **", rpeak_window_stats$end_range_max, "** ms\n* R-peak window duration range: **", rpeak_window_stats$duration_min, "** to **", rpeak_window_stats$duration_max, "** ms") else "No R-peak referenced analyses found"`

### Most Common R-peak Time Windows

`r if(nrow(rpeak_common_windows) > 0) { paste(sapply(1:min(3, nrow(rpeak_common_windows)), function(i) paste0("* ", rpeak_common_windows$time_window[i], ": **", rpeak_common_windows$n_studies[i], "** studies (**", rpeak_common_windows$percentage[i], "%**)")), collapse = "\n") } else "No common time windows found"`
    }
  }
  
### Core Time Window (included by most studies)

`r if(!is.na(rpeak_overlap_analysis$core_start)) paste0("* Core window: **", rpeak_overlap_analysis$core_start, "** to **", rpeak_overlap_analysis$core_end, "** ms\n* Studies including this core: **", rpeak_overlap_analysis$core_percentage, "%** (**", rpeak_overlap_analysis$studies_including_core, "**/**", rpeak_overlap_analysis$total_rpeak_studies, "**)") else "No core window analysis available"`

## T-peak Referenced Analysis

`r if(tpeak_window_stats$n_pipelines > 0) paste0("* Pipelines using T-peak reference: **", tpeak_window_stats$n_pipelines, "**\n* T-peak start time range: **", tpeak_window_stats$start_range_min, "** to **", tpeak_window_stats$start_range_max, "** ms\n* T-peak end time range: **", tpeak_window_stats$end_range_min, "** to **", tpeak_window_stats$end_range_max, "** ms\n* T-peak window duration range: **", tpeak_window_stats$duration_min, "** to **", tpeak_window_stats$duration_max, "** ms") else "* No T-peak referenced analyses found"`

## Baseline Correction

* Pipelines using baseline correction: **`r baseline_pct`%** (**`r nrow(baseline_window_data)`**/**`r nrow(df_pipelines)`**)

`r if(nrow(baseline_window_data) > 0) paste0("* Overall baseline start time range: **", baseline_stats$start_range_min, "** to **", baseline_stats$start_range_max, "** ms\n* Overall baseline end time range: **", baseline_stats$end_range_min, "** to **", baseline_stats$end_range_max, "** ms\n* Overall baseline duration range: **", baseline_stats$duration_min, "** to **", baseline_stats$duration_max, "** ms") else "No baseline correction data available"`

## Baseline Correction by Reference Peak

`r if(nrow(baseline_by_reference) > 0) { paste(sapply(1:nrow(baseline_by_reference), function(i) { ref_peak <- as.character(baseline_by_reference$hep_relative_to[i]); n_pipes <- baseline_by_reference$n_pipelines[i]; n_studies <- baseline_by_reference$n_studies[i]; start_min <- baseline_by_reference$start_range_min[i]; start_max <- baseline_by_reference$start_range_max[i]; end_min <- baseline_by_reference$end_range_min[i]; end_max <- baseline_by_reference$end_range_max[i]; paste0("* ", ref_peak, ": **", n_pipes, "** pipelines from **", n_studies, "** studies\n  - Start range: **", start_min, "** to **", start_max, "** ms\n  - End range: **", end_min, "** to **", end_max, "** ms") }), collapse = "\n") } else "* No reference-specific baseline data available"`

## Baseline Windows Ending Before QRS Complex

* Studies with baseline ending before QRS: **`r baseline_before_qrs_stats$percentage_before_qrs`%** (**`r baseline_before_qrs_stats$studies_ending_before_qrs`**/**`r baseline_before_qrs_stats$total_studies_with_baseline`**)

### By Reference Scheme

`r if(nrow(baseline_before_qrs_by_ref) > 0) { paste(sapply(1:nrow(baseline_before_qrs_by_ref), function(i) { ref_peak <- as.character(baseline_before_qrs_by_ref$hep_relative_to[i]); total <- baseline_before_qrs_by_ref$total_studies[i]; before_qrs <- baseline_before_qrs_by_ref$studies_ending_before_qrs[i]; pct <- baseline_before_qrs_by_ref$percentage_before_qrs[i]; paste0("* ", ref_peak, ": **", pct, "%** (**", before_qrs, "**/**", total, "** studies)") }), collapse = "\n") } else "* No reference scheme data available"`

## Significant Effects Windows

* Pipelines with significant effects: **`r significant_window_stats$n_pipelines`**

`r if(significant_window_stats$n_pipelines > 0) paste0("* Effects start time range: **", significant_window_stats$start_range_min, "** to **", significant_window_stats$start_range_max, "** ms\n* Effects end time range: **", significant_window_stats$end_range_min, "** to **", significant_window_stats$end_range_max, "** ms\n* Effects duration range: **", significant_window_stats$duration_min, "** to **", significant_window_stats$duration_max, "** ms") else "No significant effects data available"`

# Significant effects by reference peak
significant_by_reference <- if(nrow(significant_effects_data) > 0) {
  significant_effects_data %>%
    filter(!is.na(reference), reference != "unknown") %>%
    group_by(reference) %>%
    summarise(
      n_pipelines = n(),
      start_range_min = min(start_time),
      start_range_max = max(start_time),
      end_range_min = min(end_time),
      end_range_max = max(end_range),
      duration_min = min(end_time - start_time),
      duration_max = max(end_time - start_time),
      .groups = "drop"
    )
} else {
  data.frame()
}

if(nrow(significant_by_reference) > 0) {
  cat("\n### Significant Effects by Reference Peak:\n")
  for(i in 1:nrow(significant_by_reference)) {
    ref_peak <- as.character(significant_by_reference$reference[i])
    n_pipes <- significant_by_reference$n_pipelines[i]
    start_min <- significant_by_reference$start_range_min[i]
    start_max <- significant_by_reference$start_range_max[i]
    end_min <- significant_by_reference$end_range_min[i]
    end_max <- significant_by_reference$end_range_max[i]
    dur_min <- significant_by_reference$duration_min[i]
    dur_max <- significant_by_reference$duration_max[i]
    
    cat("- **", ref_peak, "**: ", n_pipes, " pipelines\n")
    cat("  - Start range: ", start_min, " to ", start_max, " ms\n")
    cat("  - End range: ", end_min, " to ", end_max, " ms\n")
    cat("  - Duration range: ", dur_min, " to ", dur_max, " ms\n")
  }
}

# Peak effect timing analysis by method and reference
peak_effects_analysis <- if(nrow(significant_effects_data) > 0) {
  significant_effects_data %>%
    filter(!is.na(reference), reference != "unknown") %>%
    # Use the method_category directly
    filter(method_category %in% c("Averaging", "Clustering")) %>%
    group_by(method_category, reference) %>%
    summarise(
      n_pipelines = n(),
      # Find core regions using median approach
      median_start = median(start_time, na.rm = TRUE),
      median_end = median(end_time, na.rm = TRUE),
      # Count studies that include the core region
      studies_in_core = sum(start_time <= median(start_time, na.rm = TRUE) & 
                           end_time >= median(end_time, na.rm = TRUE), na.rm = TRUE),
      core_percentage = round(studies_in_core / n() * 100, 1),
      .groups = "drop"
    ) %>%
    # For T-peak, add equivalent R-peak timing (assuming ~300ms T-peak delay)
    mutate(
      rpeak_equivalent_start = if_else(reference == "T-peak", median_start + 300, median_start),
      rpeak_equivalent_end = if_else(reference == "T-peak", median_end + 300, median_end)
    )
} else {
  data.frame()
}

cat("\n### Peak Effect Timing by Analysis Method:\n")
if(nrow(peak_effects_analysis) > 0) {
  # Clustering analysis
  cluster_data <- peak_effects_analysis %>% filter(method_category == "Clustering")
  if(nrow(cluster_data) > 0) {
    cat("**Clustering analysis core effect regions:**\n")
    for(i in 1:nrow(cluster_data)) {
      ref_peak <- cluster_data$reference[i]
      median_start <- round(cluster_data$median_start[i], 1)
      median_end <- round(cluster_data$median_end[i], 1)
      core_pct <- cluster_data$core_percentage[i]
      n_studies <- cluster_data$studies_in_core[i]
      total_studies <- cluster_data$n_pipelines[i]
      
      if(ref_peak == "R-peak") {
        cat("- **R-peak referenced**: ", median_start, "-", median_end, " ms (", core_pct, "% of studies, ", n_studies, "/", total_studies, ")\n")
      } else if(ref_peak == "T-peak") {
        rpeak_start <- round(cluster_data$rpeak_equivalent_start[i], 1)
        rpeak_end <- round(cluster_data$rpeak_equivalent_end[i], 1)
        cat("- **T-peak referenced**: ", median_start, "-", median_end, " ms (≈", rpeak_start, "-", rpeak_end, " ms after R-peak; ", core_pct, "% of studies, ", n_studies, "/", total_studies, ")\n")
      }
    }
  }
  
  # Averaging analysis
  avg_data <- peak_effects_analysis %>% filter(method_category == "Averaging")
  if(nrow(avg_data) > 0) {
    cat("\n**Averaging analysis core effect regions:**\n")
    for(i in 1:nrow(avg_data)) {
      ref_peak <- avg_data$reference[i]
      median_start <- round(avg_data$median_start[i], 1)
      median_end <- round(avg_data$median_end[i], 1)
      core_pct <- avg_data$core_percentage[i]
      n_studies <- avg_data$studies_in_core[i]
      total_studies <- avg_data$n_pipelines[i]
      
      if(ref_peak == "R-peak") {
        cat("- **R-peak referenced**: ", median_start, "-", median_end, " ms (", core_pct, "% of studies, ", n_studies, "/", total_studies, ")\n")
      } else if(ref_peak == "T-peak") {
        rpeak_start <- round(avg_data$rpeak_equivalent_start[i], 1)
        rpeak_end <- round(avg_data$rpeak_equivalent_end[i], 1)
        cat("- **T-peak referenced**: ", median_start, "-", median_end, " ms (≈", rpeak_start, "-", rpeak_end, " ms after R-peak; ", core_pct, "% of studies, ", n_studies, "/", total_studies, ")\n")
      }
    }
  }
} else {
  cat("**No peak effect timing data available**\n")
}
```

# HEP Topography

```{r topography}
```

# Statistical Analysis

```{r statistics}
```


---
*Generated on `r Sys.Date()`*
