---
title: "Manuscript Summary"
subtitle: "A Systematic Review of Methods Used for Studying Heartbeat Evoked Responses"
output: 
  html_document:
    self_contained: false
    theme: null
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
source("init_workspace.R")

# Paths
data_path <- file.path(getwd(), 'data')
func_path <- file.path(getwd(), 'functions')
derivatives_path <- file.path(data_path, 'derivatives')
df_included <- read.csv(file.path(derivatives_path, 'included.csv'))
df_screening <- read.csv(file.path(derivatives_path, 'screening.csv'))

# Helper function to determine if percentages should refer to studies or pipelines
check_studies_or_pipelines <- function(df, variable_column, group_col = "PMID") {
  df_distinct <- df %>% distinct(!!sym(group_col), !!sym(variable_column))
  multiple_rows_per_group <- any(table(df_distinct[[group_col]]) > 1)
  if (multiple_rows_per_group) {
    return("pipelines")
  } else {
    return("studies")
  }
}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      results = "asis")

# Create study-level and pipeline-level datasets for efficiency
df_studies <- df_included %>% distinct(PMID, .keep_all = TRUE)
df_pipelines <- df_included
```

```{r helper-functions}
get_row <- function(df, column, value) {
  as.list(df[df[[column]] == value,])
}
```

## Overview

This document provides all values mentioned in the manuscript "Heartbeat-evoked responses in MEG/EEG: A systematic review of methods with suggestions for analysis and reporting". All sections of this document apart from this overview match the corresponding section of the manuscript. Numbers highlighted in **bold** are also present in the manuscript.

### Important Distinction: Studies vs Pipelines

- **Studies**: Unique publications (identified by PMID). Each study represents one research paper.
- **Pipelines**: Individual analysis approaches within studies. Some studies report multiple analysis pipelines (e.g. different time windows, or statistical approaches).

## 2. Methods

### 2.1. Literature search

```{r data-export}
# Get the number of papers in Pubmed export
export_stats <- get_export_stats(file.path(data_path, 'exports'))
```

Table 1 - number of retrieved papers:

* 15.01.2024: **`r export_stats$num_query1`**
* 24.07.2024: **`r export_stats$num_query2`** (rerun: **`r export_stats$num_query2_rerun`**)
* 05.08.2024: **`r export_stats$num_query3`**
* After removing duplicates: **`r export_stats$num_merged`**

```{r literature-search, results='asis'}
screening_pubmed <- df_screening[df_screening$source == "pubmed",]
screening_manual <- df_screening[df_screening$source == "manual",]

total_retrieved_pubmed <- nrow(screening_pubmed)
total_included_pubmed <- nrow(screening_pubmed[screening_pubmed$Include == 1,])
total_retrieved_manual <- nrow(screening_manual)
total_included_manual <- nrow(screening_manual[screening_manual$Include == 1,])
```

Exported from Pubmed:

* Retrieved: **`r total_retrieved_pubmed`** studies
* Included: **`r total_included_pubmed`** studies

Manually added:

* Retrieved: **`r total_retrieved_manual`** studies
* Included: **`r total_included_manual`** studies

Final sample: **`r total_included_pubmed + total_included_manual`** studies

### 2.3. Data analysis

Analysis parameters:

* Entropy - binning continuous variables if at least **`r params$entropy_unique_threshold`** unique values are present
* Power computation - power threshold: TODO
* Power computation - significance level: TODO
* Number of permutations for testing peak differences: TODO

## 3. Results

### 3.1. Overview of the included studies

```{r literature-overview}
# Basic counts
total_studies <- nrow(df_studies)

# Year range (based on unique studies)
year_range <- df_studies %>% 
  summarise(min_year = min(Year, na.rm = TRUE), 
            max_year = max(Year, na.rm = TRUE))

# Modality breakdown (unique studies)
modality_counts <- df_studies %>%
  count(modality) %>%
  mutate(percentage = round(n / sum(n) * 100, 1))
modality_eeg <- get_row(modality_counts, "modality", "EEG")
modality_meg <- get_row(modality_counts, "modality", "MEG")

# Task vs resting state - studies that have both vs only one type
study_types <- df_studies %>%
  count(study_category) %>%
  mutate(percentage = round(n / sum(n) * 100, 1))

study_type_task <- get_row(study_types, "study_category", "Task")
study_type_rest <- get_row(study_types, "study_category", "Rest")
study_type_both <- get_row(study_types, "study_category", "Both")
```

Total studies: **`r total_studies`** (**`r year_range$min_year`**-**`r year_range$max_year`**)

Modality:

* EEG: **`r modality_eeg$n`** studies (**`r modality_eeg$percentage`%**)
* MEG: **`r modality_meg$n`** studies (**`r modality_meg$percentage`%**)

Study type distribution:

* Task-based: **`r study_type_task$n`** studies (**`r study_type_task$percentage`%**)
* Resting-state: **`r study_type_rest$n`** studies (**`r study_type_rest$percentage`%**)
* Both: **`r study_type_both$n`** studies (**`r study_type_both$percentage`%**)
 
### 3.2. Overview of methodological choices

```{r multiple-choices}
total_pipelines <- nrow(df_pipelines)

# Get target columns from pipeline steps
target_columns <- unlist(pipeline_steps, use.names = FALSE)

# Calculate percentage of studies with multiple choices for each method
multiple_df <- multiple_choices(df_pipelines, target_columns) %>%
  mutate(percentage = round(percentage * 100, 0))

multiple_stats <- get_row(multiple_df, "Column", "statistics")
multiple_hep_start <- get_row(multiple_df, "Column", "hep_start")  # pick as maximum among start and end
```

Total pipelines: **`r total_pipelines`** 

Studies using multiple choices for:

* Statistical tests: **`r multiple_stats$percentage`%** (**`r multiple_stats$count`** / **`r multiple_stats$total`**)

* HER window start or end times: **`r multiple_hep_start$percentage`%** (**`r multiple_hep_start$count`** / **`r multiple_hep_start$total`**)

```{r missing-info}
# Variables with >40% missing info
missing_df <- missing_information(df_pipelines, target_columns) %>%
  mutate(percentage = round(percentage * 100, 0))

missing_cfa_ics <- get_row(missing_df, "Column", "rejected_cardiac_ics")
missing_ecg_ground <- get_row(missing_df, "Column", "ecg_ground")
missing_ecg_locations <- get_row(missing_df, "Column", "ecg_locations")

missing_df_top <- missing_df %>% 
  filter(percentage >= 40) %>%
  arrange(-percentage) %>%
  select(Column, percentage)
```


Missing information:

* cardiac IC rejection information (among those using CFA removal): **`r missing_cfa_ics$percentage`%** (**`r missing_cfa_ics$count`** / **`r missing_cfa_ics$total`**)

* unknown ECG ground location: **`r missing_ecg_ground$percentage`%** (**`r missing_ecg_ground$count`** / **`r missing_ecg_ground$total`**)

* ECG electrode locations: **`r missing_ecg_locations$percentage`%** (**`r missing_ecg_locations$count`** / **`r missing_ecg_locations$total`**)

```{r high-missing-table, results='asis'}
knitr::kable(missing_df_top, 
             caption = "Variables with >40% missing values across studies",
             col.names = c("Variable", "Missing (%)"))
```

## M/EEG Acquisition & Preprocessing

### Sensor Information

```{r channels}
#Sensor statistics
sensor_stats <- df_pipelines %>%
distinct(PMID, meeg_num_electrodes) %>%
  summarise(
    min_channels = min(meeg_num_electrodes),
    max_channels = max(meeg_num_electrodes),
    median_channels = median(meeg_num_electrodes),
    n_studies = n()
  )
```

### Reference Schemes

```{r references}
# Reference processing
major_categories <- tolower(c(
  "Cz", "Nose", "Linked earlobes", "Linked mastoids",
  "FCz", "Common average", "Fpz", "CMS", "CMS and DRL",
  "unknown", "Laplacian reference", "REST"
))

# Process reference categories
df_ref <- df_pipelines %>% 
  filter(modality == "EEG") %>%
  mutate(across(
    .cols = c(reference_online, reference_offline),
    .fns = ~ case_when(
      tolower(.) %in% major_categories ~ tolower(.),
      TRUE ~ "Other"
    )
  ))

# Common reference category mapping 
ref_categories <- c(
  "common average" = "CAR",
  "linked mastoids" = "LM", 
  "linked earlobes" = "LE",
  "cz" = "Cz",
  "fcz" = "FCz",
  "fpz" = "Fpz",
  "cms" = "CMS",
  "cms and drl" = "CMS",
  "nose" = "Nose",
  "laplacian reference" = "LAP",
  "rest" = "REST",
  "other" = "Other",
  "unknown" = "N/M"
)

# Online reference distribution
online_ref_counts <- df_ref %>% 
  distinct(PMID, reference_online) %>%
  count(reference_online) %>%
  filter(reference_online %in% names(ref_categories)) %>%
  mutate(
    display_name = ref_categories[reference_online],
    percentage = round(n / sum(n) * 100, 1)
  ) %>%
  arrange(desc(n))

# Check if online references are at study or pipeline level
online_ref_level <- check_studies_or_pipelines(df_ref, "reference_online")

# Offline reference distribution
offline_ref_counts <- df_ref %>% 
  distinct(PMID, reference_offline)%>%
  count(reference_offline) %>%
  filter(reference_offline %in% names(ref_categories)) %>%
  mutate(
    display_name = ref_categories[reference_offline],
    percentage = round(n / sum(n) * 100, 1)
  ) %>%
  arrange(desc(n))

# Check if offline references are at study or pipeline level
offline_ref_level <- check_studies_or_pipelines(df_ref, "reference_offline")
```

Online reference: Linked mastoids (**`r online_ref_counts$percentage[online_ref_counts$display_name == "LM"]`%** (`r online_ref_counts$n[online_ref_counts$display_name == "LM"]`/`r sum(online_ref_counts$n)`) `r online_ref_level`), Cz (**`r online_ref_counts$percentage[online_ref_counts$display_name == "Cz"]`%** (`r online_ref_counts$n[online_ref_counts$display_name == "Cz"]`/`r sum(online_ref_counts$n)`) `r online_ref_level`)

Offline reference: Common Average Reference (**`r offline_ref_counts$percentage[offline_ref_counts$display_name == "CAR"]`%** (`r offline_ref_counts$n[offline_ref_counts$display_name == "CAR"]`/`r sum(offline_ref_counts$n)`) `r offline_ref_level`))

### Artifact Removal

```{r artifacts}
# Artifact removal statistics
artifact_stats <- df_pipelines %>%
  summarise(
    # Noisy epochs removal 
    noisy_epochs_pct = round(mean(grepl("noisy epoch", other_cleaning_strategy, ignore.case = TRUE) %in% TRUE, na.rm = TRUE) * 100, 0),
    
    # Bad channels removal 
    bad_channels_pct = round(mean(grepl("bad channels", other_cleaning_strategy, ignore.case = TRUE) %in% TRUE, na.rm = TRUE) * 100, 0),
    
    # Blink/EOG correction
    blink_correction_pct = round(mean(grepl("blink|eye|gratton", other_cleaning_strategy, ignore.case = TRUE) %in% TRUE, na.rm = TRUE) * 100, 0),

    # ICA usage
    ica_pct = round(mean(ICA == 1, na.rm = TRUE) * 100, 1),

    # Pipelines with ICA
    n_ica_studies = sum(ICA == 1, na.rm = TRUE),
    total_studies = n() 
  )

# Check if artifact removal strategies are at study or pipeline level
noisy_epochs_level <- check_studies_or_pipelines(df_pipelines, "other_cleaning_strategy")
bad_channels_level <- check_studies_or_pipelines(df_pipelines, "other_cleaning_strategy")
ica_level <- check_studies_or_pipelines(df_pipelines, "ICA")

# Studies using ICA
ica_studies <- df_pipelines %>%
  group_by(PMID) %>%
  summarise(uses_ica = any(ICA == 1, na.rm = TRUE)) %>%
  summarise(
    n_ica_studies = sum(uses_ica),
    total_studies = n(),
    ica_study_pct = round(mean(uses_ica) * 100, 1)
  )

# Studies using ICA specifically for cfa removal
ica_for_cfa_studies <- df_pipelines %>%
  group_by(PMID) %>%
  summarise(
    uses_ica_for_cfa = any(ICA == 1 & 
                           rejected_components != "" &
                           grepl("cfa", rejected_components, ignore.case = TRUE)),
    .groups = "drop"
  ) %>%
  summarise(
    n_ica_cfa_studies = sum(uses_ica_for_cfa),
    total_studies = n(),
    ica_cfa_study_pct = round(mean(uses_ica_for_cfa) * 100, 1)
  )

# Component rejection types
component_types_df <- df_pipelines %>%
  filter(ICA == 1) %>%
  distinct(PMID, rejected_components) %>%
  filter(rejected_components != "", rejected_components != "unknown") %>%
  mutate(pipeline_id = row_number())

# Check if component types are at study or pipeline level
component_types_level <- check_studies_or_pipelines(df_pipelines %>% filter(ICA == 1), "rejected_components")

# Clean rejected_components
component_types_df$rejected_components <- sapply(component_types_df$rejected_components, function(x) {
  x <- gsub("[\r\n]+", ",", x)    
  x <- gsub(",+", ",", x)         
  x <- gsub("^,|,$", "", x)       
  comps <- unlist(strsplit(x, ","))
  comps <- unique(trimws(comps))
  comps <- comps[comps != ""]
  paste(comps, collapse = ",")
})

# Count total pipelines before splitting
total_ica_pipelines <- nrow(component_types_df)

# Create component types data
component_types_expanded <- component_types_df %>%
  separate_rows(rejected_components, sep = ",") %>%
  mutate(
    rejected_components = trimws(rejected_components),
    rejected_components = tolower(rejected_components)
  ) %>%
  mutate(rejected_components = case_when(
    rejected_components == "eye movements" ~ "Ocular",
    rejected_components == "blinks" ~ "Ocular", 
    rejected_components == "muscle" ~ "Muscle",
    rejected_components == "cfa" ~ "CFA",
    rejected_components == "channel noise" ~ "Channel noise",
    rejected_components == "line noise" ~ "Line noise",
    rejected_components == "other" ~ "Other",
    TRUE ~ str_to_title(rejected_components)
  )) %>%
  filter(rejected_components != "")

# Calculate percentages based on distinct pipeline_ids 
component_types <- component_types_expanded %>%
  group_by(rejected_components) %>%
  summarise(count = n_distinct(pipeline_id), .groups = "drop") %>%
  arrange(desc(count)) %>%
  mutate(percentage = round(count / total_ica_pipelines * 100, 1))  
```


Artifact removal:

* Noisy epochs: **`r artifact_stats$noisy_epochs_pct`%** (`r sum(grepl("noisy epoch", df_studies$other_cleaning_strategy, ignore.case = TRUE), na.rm = TRUE)`/`r nrow(df_studies)`) `r noisy_epochs_level`
* Bad channels: **`r artifact_stats$bad_channels_pct`%** (`r sum(grepl("bad channels", df_studies$other_cleaning_strategy, ignore.case = TRUE), na.rm = TRUE)`/`r nrow(df_studies)`) `r bad_channels_level`
* ICA usage: **`r ica_studies$ica_study_pct`%** (`r ica_studies$n_ica_studies`/`r ica_studies$total_studies`) studies
* ICA for CFA: **`r ica_for_cfa_studies$ica_cfa_study_pct`%** (`r ica_for_cfa_studies$n_ica_cfa_studies`/`r ica_for_cfa_studies$total_studies`) studies

ICA component types removed:

* `r component_types$rejected_components[1]`: **`r component_types$percentage[1]`%** (`r component_types$count[1]`/`r total_ica_pipelines`) `r component_types_level`
* `r component_types$rejected_components[2]`: **`r component_types$percentage[2]`%** (`r component_types$count[2]`/`r total_ica_pipelines`) `r component_types_level`
* `r component_types$rejected_components[3]`: **`r component_types$percentage[3]`%** (`r component_types$count[3]`/`r total_ica_pipelines`) `r component_types_level`
* Other noise: **`r component_types$percentage[4] + component_types$percentage[5] + component_types$percentage[6]`%** (`r component_types$count[4] + component_types$count[5] + component_types$count[6]`/`r total_ica_pipelines`) `r component_types_level`

### Filter Settings

```{r filters}
# Filter statistics
filter_data <- df_pipelines %>%
  filter(!is.na(high_pass) & !is.na(low_pass)) %>%
  distinct(PMID, high_pass, low_pass, .keep_all = TRUE)

filter_stats <- filter_data %>%
  summarise(
    n_valid = n(),
    high_pass_range_min = min(high_pass),
    high_pass_range_max = max(high_pass),
    low_pass_range_min = min(low_pass), 
    low_pass_range_max = max(low_pass)
  )

# Most common high-pass filter values (studies)
common_highpass <- filter_data %>%
  count(high_pass, sort = TRUE) %>%
  head(3)

# Most common low-pass filter values (studies)
common_lowpass <- filter_data %>%
  count(low_pass, sort = TRUE) %>%
  head(3)

```

Filter settings: **`r common_highpass$high_pass[1]`**-**`r common_lowpass$low_pass[1]` Hz** (most common)

High-pass cutoffs: **`r paste(common_highpass$high_pass, collapse = ", ")` Hz**

### ECG Acquisition

```{r ecg_num_electrodes}
two_ecg_electrodes <- df_included %>%
  distinct(PMID, ecg_num_electrodes) %>%
  group_by(ecg_num_electrodes) %>%
  filter(ecg_num_electrodes == 2) %>%
  summarize(count = n()) %>%
  mutate(freq = count / total_studies * 100)
two_ecg_electrodes_count <- two_ecg_electrodes$count
two_ecg_electrodes_freq <- round(two_ecg_electrodes$freq, 1)
```

Studies that use 2 ECG electrodes: `r two_ecg_electrodes_count` (**`r two_ecg_electrodes_freq`**%)

```{r ecg_num_leads}
ecg_leads <- df_included %>%
  distinct(PMID, ecg_lead) %>%
  group_by(ecg_lead) %>%
  summarize(count = n()) %>%
  mutate(freq = round(count / total_studies * 100, 1))
lead_i <- ecg_leads[ecg_leads$ecg_lead == "Lead I", ]
lead_ii <- ecg_leads[ecg_leads$ecg_lead == "Lead II", ]
lead_iii <- ecg_leads[ecg_leads$ecg_lead == "Lead III", ]
lead_unclassified <- ecg_leads[ecg_leads$ecg_lead == "N/C", ]

# Check if ECG leads are at study or pipeline level
ecg_lead_level <- check_studies_or_pipelines(df_included, "ecg_lead")
```

Number of studies that use different ECG leads:

* Lead II: `r lead_ii$count` (**`r lead_ii$freq`**%) `r ecg_lead_level`
* Lead I: `r lead_i$count` (**`r lead_i$freq`**%) `r ecg_lead_level`
* Lead III: `r lead_iii$count` (**`r lead_iii$freq`**%) `r ecg_lead_level`
* Unclassified: `r lead_unclassified$count` (**`r lead_unclassified$freq`**%) `r ecg_lead_level`

### Dealing with cardiac field artifacts

```{r cfa}
# ICA epoch/continuous
ica_timing <- df_studies %>%
  filter(ICA == 1 & !is.na(ica_on_epochs)) %>%
  count(ica_on_epochs) %>%
  mutate(
    timing = case_when(
      ica_on_epochs == 0 ~ "Continuous",
      ica_on_epochs == 1 ~ "Epoched",
      TRUE ~ "Unknown"
    ),
    percentage = round(n / sum(n) * 100, 1)
  )

# Check if ICA timing is at study or pipeline level
ica_timing_level <- check_studies_or_pipelines(df_pipelines %>% filter(ICA == 1), "ica_on_epochs")

# CFA identification approaches (studies - no difference to unique pipelines)
cfa_approach_counts <- df_studies %>%
  filter(cfa_rej_approach != "" & 
         tolower(str_trim(cfa_rej_approach)) != "unknown") %>%
  mutate(cfa_rej_approach_clean = str_to_title(tolower(str_trim(cfa_rej_approach)))) %>%
  count(cfa_rej_approach_clean, sort = TRUE) %>%
  mutate(percentage = round(n / sum(n) * 100, 1)) %>%
  rename(cfa_rej_approach = cfa_rej_approach_clean)

# Check if CFA approaches are at study or pipeline level
cfa_approach_level <- check_studies_or_pipelines(df_pipelines, "cfa_rej_approach")

# CFA identification criteria (studies) - using same logic as plotting function
cfa_criteria_mapping <- c(
  "time course" = "Time Course",
  "topography" = "Topography",
  "power spectrum" = "Power Spectrum",
  "phase consistency" = "Phase Consistency",  # Note: plotting function uses "Phase\nConsistency" but we'll use this for text
  "iclabel" = "Algorithm",
  "corrmap" = "Algorithm",
  "correlation" = "Correlation",
  "sasica" = "Algorithm"
)
cfa_criteria_counts <- df_studies %>%
  filter(!is.na(cfa_rej_criteria), cfa_rej_criteria != "", tolower(cfa_rej_criteria) != "unknown") %>%
  distinct(PMID, cfa_rej_criteria) %>%
  separate_rows(cfa_rej_criteria, sep = ",") %>%
  mutate(
    cfa_rej_criteria = str_trim(str_replace_all(tolower(cfa_rej_criteria), "[\r\n]", " ")),
    cfa_rej_criteria = ifelse(cfa_rej_criteria %in% names(cfa_criteria_mapping),
                              cfa_criteria_mapping[cfa_rej_criteria],
                              str_to_title(cfa_rej_criteria))
  ) %>%
  count(cfa_rej_criteria, name = "count") %>%
  mutate(
    total_pipelines = n_distinct(df_studies$PMID[df_studies$cfa_rej_criteria != "" & tolower(df_studies$cfa_rej_criteria) != "unknown"]),
    percentage = round(count / total_pipelines * 100, 1)
  ) %>%
  arrange(desc(count))

# Check if CFA criteria are at study or pipeline level
cfa_criteria_level <- check_studies_or_pipelines(df_pipelines, "cfa_rej_criteria")

# Number of rejected cardiac ICs (studies)
cardiac_ic_stats <- df_studies %>%
  filter(!is.na(rejected_cardiac_ics)) %>%
  summarise(
    n_studies = n(),
    min_ics = min(rejected_cardiac_ics, na.rm = TRUE),
    max_ics = max(rejected_cardiac_ics, na.rm = TRUE),
    median_ics = median(rejected_cardiac_ics, na.rm = TRUE)
  )

# Other CFA removal strategies (pipelines)
# For minimal artifact window, we need to match plotting function logic 
# by only counting studies with valid time window data
minimal_artifact_valid_count <- df_pipelines %>%
  distinct(PMID, other_cfa_removal_strategy, .keep_all = TRUE) %>%
  filter(str_detect(tolower(other_cfa_removal_strategy), "limit analysis to time of minimal artifact")) %>%
  filter(!is.na(hep_start), !is.na(hep_end),
         is.finite(hep_start), is.finite(hep_end)) %>%
  nrow()

other_cfa_strategies <- df_pipelines %>%
  filter(other_cfa_removal_strategy != "" & 
         tolower(str_trim(other_cfa_removal_strategy)) != "unknown") %>%
  distinct(PMID, other_cfa_removal_strategy) %>%  
  mutate(
    strategy_clean = case_when(
      other_cfa_removal_strategy == "limit analysis to time of minimal artifact" ~ 
        "Minimal artifact window",
      !is.na(str_match(tolower(other_cfa_removal_strategy), "rr at least\\s*(\\d+)\\s*ms")[,1]) ~ 
        "RR interval\nconstraints",
      tolower(other_cfa_removal_strategy) %in% c(
        "subtract/regress ecg from eeg"
      ) ~ "Subtract/regress ECG from EEG",
      tolower(other_cfa_removal_strategy) == "subtract rshep from taskhep" ~ 
        "subtract rsHEP\nfrom task HEP",
      tolower(other_cfa_removal_strategy) == "pca on heps" ~ "PCA on\nHEP",
      tolower(other_cfa_removal_strategy) == "csd" ~ "CSD",
      TRUE ~ str_to_title(str_trim(other_cfa_removal_strategy))
    )
  ) %>%
  # Remove duplicates after strategy cleaning again (for RR constraints that appear with other strategies)
  distinct(PMID, strategy_clean) %>%
  count(strategy_clean, sort = TRUE) %>%
  mutate(
    n = case_when(
      strategy_clean == "Minimal artifact window" ~ minimal_artifact_valid_count,
      TRUE ~ n
    ),
    percentage = round(n / total_studies * 100, 1),
    # Calculate level for each strategy
    level = map_chr(strategy_clean, function(strat) {
      # For RR interval constraints, it's always at study level
      if (strat == "RR interval\nconstraints") {
        return("studies")
      }
      
      # Get the original strategy names that map to this cleaned strategy
      original_strategies <- df_pipelines %>%
        filter(other_cfa_removal_strategy != "" & 
               tolower(str_trim(other_cfa_removal_strategy)) != "unknown") %>%
        mutate(
          strategy_clean = case_when(
            other_cfa_removal_strategy == "limit analysis to time of minimal artifact" ~ 
              "Minimal artifact window",
            !is.na(str_match(tolower(other_cfa_removal_strategy), "rr at least\\s*(\\d+)\\s*ms")[,1]) ~ 
              "RR interval\nconstraints",
            tolower(other_cfa_removal_strategy) %in% c(
              "subtract/regress ecg from eeg"
            ) ~ "Subtract/regress ECG from EEG",
            tolower(other_cfa_removal_strategy) == "subtract rshep from taskhep" ~ 
              "subtract rsHEP\nfrom task HEP",
            tolower(other_cfa_removal_strategy) == "pca on heps" ~ "PCA on\nHEP",
            tolower(other_cfa_removal_strategy) == "csd" ~ "CSD",
            TRUE ~ str_to_title(str_trim(other_cfa_removal_strategy))
          )
        ) %>%
        filter(strategy_clean == strat) %>%
        distinct(PMID, other_cfa_removal_strategy)
      
      if (nrow(original_strategies) == 0) return("studies")
      
      # Check if this specific strategy has multiple values per PMID
      check_studies_or_pipelines(original_strategies, "other_cfa_removal_strategy")
    })
  ) %>%
  arrange(desc(n)) %>%  # Re-sort after correction
  rename(strategy = strategy_clean)

# Papers with no CFA approach (studies)
no_cfa_analysis <- df_studies %>%
  mutate(
    # Check if study uses ICA & CFA in rejected components
    uses_ica_for_cfa = (ICA == 1 & 
                        rejected_components != "" &
                        rejected_components != "unknown" &
                        grepl("CFA", rejected_components, ignore.case = TRUE)),
    # Check if study has other CFA removal strategies
    has_other_cfa = (!is.na(other_cfa_removal_strategy) & 
                     other_cfa_removal_strategy != "" & 
                     tolower(str_trim(other_cfa_removal_strategy)) != "unknown"),
    has_any_cfa_approach = (uses_ica_for_cfa | has_other_cfa),
    no_cfa_approach = !has_any_cfa_approach
  )

# Calculate summary statistics
no_cfa_stats <- no_cfa_analysis %>%
  summarise(
    total_studies = n(),
    studies_with_ica_for_cfa = sum(uses_ica_for_cfa, na.rm = TRUE),
    studies_with_other_cfa = sum(has_other_cfa, na.rm = TRUE),
    studies_with_any_cfa = sum(has_any_cfa_approach, na.rm = TRUE),
    studies_with_no_cfa = sum(no_cfa_approach, na.rm = TRUE),
    pct_with_ica_for_cfa = round(studies_with_ica_for_cfa / total_studies * 100, 1),
    pct_with_other_cfa = round(studies_with_other_cfa / total_studies * 100, 1),
    pct_with_any_cfa = round(studies_with_any_cfa / total_studies * 100, 1),
    pct_with_no_cfa = round(studies_with_no_cfa / total_studies * 100, 1)
  )

# RR interval constraints analysis
rr_interval_pipelines <- df_pipelines %>%
  mutate(rr_match = str_match(tolower(other_cfa_removal_strategy), "rr at least\\s*(\\d+)\\s*ms")) %>%
  filter(!is.na(rr_match[,2])) %>%
  mutate(min_rr_value = as.numeric(rr_match[,2])) %>%
  filter(!is.na(min_rr_value), is.finite(min_rr_value)) %>%
  distinct(PMID, min_rr_value)

# Calculate IBI min max and number of studies
ibi_stats <- rr_interval_pipelines %>%
  summarise(
    min_ibi = min(min_rr_value, na.rm = TRUE),
    max_ibi = max(min_rr_value, na.rm = TRUE),
    n_studies = n()
  )

```

ICA for CFA: **`r no_cfa_stats$studies_with_ica_for_cfa`**/**`r no_cfa_stats$total_studies`**

ICA timing (`r ica_timing_level`):

* Continuous: **`r ica_timing$percentage[ica_timing$timing == "Continuous"]`%** (`r ica_timing$n[ica_timing$timing == "Continuous"]`/`r sum(ica_timing$n)`)
* Epoched: **`r ica_timing$percentage[ica_timing$timing == "Epoched"]`%** (`r ica_timing$n[ica_timing$timing == "Epoched"]`/`r sum(ica_timing$n)`)

Minimum IBI constraints: **`r ibi_stats$min_ibi`** to **`r ibi_stats$max_ibi`** ms (`r ibi_stats$n_studies` studies)

## CFA Identification Approaches

* Not reported: **`r round((1 - sum(cfa_approach_counts$n) / ica_studies$n_ica_studies) * 100, 1)`%** of studies using ICA (`r ica_studies$n_ica_studies - sum(cfa_approach_counts$n)`/`r ica_studies$n_ica_studies`)

CFA approaches (`r cfa_approach_level`):
* `r cfa_approach_counts$cfa_rej_approach[1]`: **`r cfa_approach_counts$percentage[1]`%** (`r cfa_approach_counts$n[1]`/`r sum(cfa_approach_counts$n)`)
* `r cfa_approach_counts$cfa_rej_approach[2]`: **`r cfa_approach_counts$percentage[2]`%** (`r cfa_approach_counts$n[2]`/`r sum(cfa_approach_counts$n)`)
* `r cfa_approach_counts$cfa_rej_approach[3]`: **`r cfa_approach_counts$percentage[3]`%** (`r cfa_approach_counts$n[3]`/`r sum(cfa_approach_counts$n)`)

## CFA Identification Criteria

CFA criteria (`r cfa_criteria_level`):
* `r cfa_criteria_counts$cfa_rej_criteria[1]`: **`r cfa_criteria_counts$percentage[1]`%** (`r cfa_criteria_counts$count[1]`/`r cfa_criteria_counts$total_pipelines[1]`)
* `r cfa_criteria_counts$cfa_rej_criteria[2]`: **`r cfa_criteria_counts$percentage[2]`%** (`r cfa_criteria_counts$count[2]`/`r cfa_criteria_counts$total_pipelines[2]`)
* `r cfa_criteria_counts$cfa_rej_criteria[3]`: **`r cfa_criteria_counts$percentage[3]`%** (`r cfa_criteria_counts$count[3]`/`r cfa_criteria_counts$total_pipelines[3]`)
* `r cfa_criteria_counts$cfa_rej_criteria[6]`: **`r cfa_criteria_counts$percentage[6]`%** (`r cfa_criteria_counts$count[6]`/`r cfa_criteria_counts$total_pipelines[6]`)
* `r cfa_criteria_counts$cfa_rej_criteria[4]`: **`r cfa_criteria_counts$percentage[4]`%** (`r cfa_criteria_counts$count[4]`/`r cfa_criteria_counts$total_pipelines[4]`)
* `r cfa_criteria_counts$cfa_rej_criteria[5]`: **`r cfa_criteria_counts$percentage[5]`%** (`r cfa_criteria_counts$count[5]`/`r cfa_criteria_counts$total_pipelines[5]`)

## Rejected Cardiac ICs

* Studies reporting number: **`r cardiac_ic_stats$n_studies`** out of **`r no_cfa_stats$studies_with_ica_for_cfa`** studies that removed CFA-related ICs (`r cardiac_ic_stats$n_studies`/`r no_cfa_stats$studies_with_ica_for_cfa`)
* Range: **`r cardiac_ic_stats$min_ics`** - **`r cardiac_ic_stats$max_ics`**
* Median: **`r cardiac_ic_stats$median_ics`**

## Other CFA Removal Strategies

Other CFA strategies:
* `r other_cfa_strategies$strategy[3]`: `r other_cfa_strategies$n[3]` studies (**`r other_cfa_strategies$percentage[3]`%**) (`r other_cfa_strategies$level[3]`)
* `r other_cfa_strategies$strategy[4]`: `r other_cfa_strategies$n[4]` studies (**`r other_cfa_strategies$percentage[4]`%**) (`r other_cfa_strategies$level[4]`)
* `r other_cfa_strategies$strategy[5]`: `r other_cfa_strategies$n[5]` studies (**`r other_cfa_strategies$percentage[5]`%**) (`r other_cfa_strategies$level[5]`)
* `r other_cfa_strategies$strategy[6]`: `r other_cfa_strategies$n[6]` studies (**`r other_cfa_strategies$percentage[6]`%**) (`r other_cfa_strategies$level[6]`)

### Limit time range / analysis window

* `r other_cfa_strategies$strategy[1]`: `r other_cfa_strategies$n[1]` studies (**`r other_cfa_strategies$percentage[1]`%**) (`r other_cfa_strategies$level[1]`)
* `r other_cfa_strategies$strategy[2]`: **`r other_cfa_strategies$n[2]`** studies (**`r other_cfa_strategies$percentage[2]`%**) (`r other_cfa_strategies$level[2]`)

### Studies Without Any CFA Approach

* Studies with any CFA approach: **`r no_cfa_stats$pct_with_any_cfa`**% (`r no_cfa_stats$studies_with_any_cfa`/`r no_cfa_stats$total_studies`)

### IBI Statistics

* Minimum IBI: **`r ibi_stats$min_ibi`** ms
* Maximum IBI: **`r ibi_stats$max_ibi`** ms
* Number of studies: **`r ibi_stats$n_studies`**

## HEP Time Windows

```{r timewindows}
# Clustering vs Averaging
hep_determination_analysis <- df_pipelines %>%
  group_by(PMID) %>%
  summarise(
    has_averaging = any(method_category == "Averaging"),
    has_clustering = any(method_category == "Clustering"),
    .groups = "drop"
  ) %>%
  mutate(
    determination_category = case_when(
      has_averaging & has_clustering ~ "Both",
      has_averaging & !has_clustering ~ "Averaging",
      !has_averaging & has_clustering ~ "Clustering",
      TRUE ~ "Other"
    )
  ) %>%
  filter(determination_category != "Other")

hep_determination_stats <- hep_determination_analysis %>%
  count(determination_category) %>%
  mutate(percentage = round(n / sum(n) * 100, 1))

hep_determination_level <- check_studies_or_pipelines(df_pipelines, "hep_relative_to")

#R-peak vs T-peak
hep_reference_analysis <- df_pipelines %>%
  group_by(PMID) %>%
  summarise(
    has_rpeak = any(hep_relative_to == "R-peak"),
    has_tpeak = any(hep_relative_to == "T-peak"),
    .groups = "drop"
  ) %>%
  mutate(
    reference_category = case_when(
      has_rpeak & has_tpeak ~ "Both",
      has_rpeak & !has_tpeak ~ "R-peak",
      !has_rpeak & has_tpeak ~ "T-peak",
      TRUE ~ "Other"
    )
  ) %>%
  filter(reference_category != "Other")

hep_reference_stats <- hep_reference_analysis %>%
  count(reference_category) %>%
  mutate(percentage = round(n / sum(n) * 100, 1))

# Check if HEP reference is at study or pipeline level
hep_reference_level <- check_studies_or_pipelines(df_pipelines, "hep_relative_to")

# Baseline correction 
baseline_correction_analysis <- df_pipelines %>%
  distinct(PMID, baseline_defined, .keep_all = TRUE) %>%
  group_by(PMID) %>%
  summarise(
    has_yes = any(baseline_defined == "Yes"),
    has_no = any(baseline_defined == "No"),
    .groups = "drop"
  ) %>%
  mutate(
    baseline_category = case_when(
      has_yes & has_no ~ "Both",
      has_yes & !has_no ~ "Yes",
      !has_yes & has_no ~ "No",
      TRUE ~ "Other"
    )
  ) %>%
  filter(baseline_category != "Other") %>%
  mutate(baseline_category = factor(baseline_category, 
                                  levels = c("Yes", "No", "Both")))

# % studies using baseline calculated using absolute number of studies to also include "unknown"
baseline_correction_stats <- baseline_correction_analysis %>%
  count(baseline_category) %>%
  mutate(
    percentage_within_reporting = round(n / sum(n) * 100, 1),
    percentage_of_all_studies = round(n / total_studies * 100, 1)
  )

# Check if baseline correction is at study or pipeline level
baseline_correction_level <- check_studies_or_pipelines(df_pipelines, "baseline_defined")

# Calculate overall baseline percentage for output
baseline_pct <- baseline_correction_stats %>%
  filter(baseline_category %in% c("Yes", "Both")) %>%
  summarise(total_pct = sum(percentage_within_reporting)) %>%
  pull(total_pct)

# Baseline correction - Studies with R-peak analysis
baseline_rpeak_studies <- df_pipelines %>%
  filter(hep_relative_to == "R-peak") %>%
  group_by(PMID) %>%
  summarise(
    has_yes = any(baseline_defined == "Yes"),
    has_no = any(baseline_defined == "No"),
    .groups = "drop"
  ) %>%
  mutate(
    baseline_category = case_when(
      has_yes & has_no ~ "Both",
      has_yes & !has_no ~ "Yes",
      !has_yes & has_no ~ "No",
      TRUE ~ "Other"
    )
  ) %>%
  filter(baseline_category != "Other")

baseline_rpeak_summary <- baseline_rpeak_studies %>%
  summarise(
    total_studies = hep_reference_stats$n[hep_reference_stats$reference_category == "R-peak"] + 
                   hep_reference_stats$n[hep_reference_stats$reference_category == "Both"],
    studies_with_baseline = sum(baseline_category %in% c("Yes", "Both")),
    percentage_with_baseline = round(studies_with_baseline / total_studies * 100, 1)
  )

# Baseline correction - Studies with T-peak analysis  
baseline_tpeak_studies <- df_pipelines %>%
  filter(hep_relative_to == "T-peak") %>%
  group_by(PMID) %>%
  summarise(
    has_yes = any(baseline_defined == "Yes"),
    has_no = any(baseline_defined == "No"),
    .groups = "drop"
  ) %>%
  mutate(
    baseline_category = case_when(
      has_yes & has_no ~ "Both",
      has_yes & !has_no ~ "Yes",
      !has_yes & has_no ~ "No",
      TRUE ~ "Other"
    )
  ) %>%
  filter(baseline_category != "Other")

baseline_tpeak_summary <- baseline_tpeak_studies %>%
  summarise(
    total_studies = hep_reference_stats$n[hep_reference_stats$reference_category == "T-peak"] + 
                   hep_reference_stats$n[hep_reference_stats$reference_category == "Both"],
    studies_with_baseline = sum(baseline_category %in% c("Yes", "Both")),
    percentage_with_baseline = round(studies_with_baseline / total_studies * 100, 1)
  )

# Primary vs Secondary
  hep_window_type_analysis <- df_pipelines %>%
  group_by(PMID) %>%
  summarise(
    has_primary = any(hep_window_type == "Primary"),
    has_secondary = any(hep_window_type == "Secondary"),
    .groups = "drop"
  ) %>%
  mutate(
    window_type_category = case_when(
      has_primary & has_secondary ~ "Both",
      has_primary & !has_secondary ~ "Primary",
      !has_primary & has_secondary ~ "Secondary",
      TRUE ~ "Other"
    )
  ) %>%
  filter(window_type_category != "Other") %>%
  mutate(window_type_category = factor(window_type_category, 
                                      levels = c("Primary", "Secondary", "Both")))


hep_window_type_stats <- hep_window_type_analysis %>%
  count(window_type_category) %>%
  mutate(percentage = round(n / sum(n) * 100, 1))

# baseline start / end times
baseline_window_stats <- df_pipelines %>%
  filter(!is.na(baseline_start_ms), !is.na(baseline_end_ms))

# Baseline window ranges by reference type
baseline_rpeak_range <- baseline_window_stats %>%
  filter(hep_relative_to == "R-peak") %>%
  summarise(
    range_start = min(baseline_start_ms),
    range_end = max(baseline_end_ms),
    total_studies = n_distinct(PMID),
    studies_ending_before_qrs = n_distinct(PMID[baseline_end_ms < 0]),
    percentage_ending_before_qrs = round(studies_ending_before_qrs / total_studies * 100, 1)
  )

baseline_tpeak_range <- baseline_window_stats %>%
  filter(hep_relative_to == "T-peak") %>%
  summarise(
    range_start = min(baseline_start_ms),
    range_end = max(baseline_end_ms),
    total_studies = n_distinct(PMID)
  )

# Create baseline data for output sections
rpeak_baseline_data <- list(
  start_min = baseline_rpeak_range$range_start,
  end_max = baseline_rpeak_range$range_end
)

tpeak_baseline_data <- list(
  n_studies = baseline_tpeak_range$total_studies,
  start_min = baseline_tpeak_range$range_start,
  end_max = baseline_tpeak_range$range_end
)

baseline_before_qrs_stats <- list(
  percentage_before_qrs = baseline_rpeak_range$percentage_ending_before_qrs
)

# HEP Time of Interest windows
hep_window_data <- df_pipelines %>%
  filter(!hep_start %in% c("none", "unknown"),
         !hep_end %in% c("none", "unknown")) %>%
  mutate(
    start_time = as.numeric(hep_start),
    end_time = as.numeric(hep_end)
  ) %>%
  filter(!is.na(start_time), !is.na(end_time)) %>%
  distinct(PMID, hep_start, hep_end, hep_relative_to, .keep_all = TRUE)

# T-peak and R-peak window ranges
tpeak_window_stats <- hep_window_data %>%
  filter(hep_relative_to == "T-peak") %>%
  summarise(
    start_min = min(start_time),
    start_max = max(start_time),
    end_min = min(end_time),
    end_max = max(end_time),
    # Convert to R-peak equivalent timing (T-peak ~300ms after R-peak)
    rpeak_equiv_start_min = start_min + 300,
    rpeak_equiv_start_max = start_max + 300,
    rpeak_equiv_end_min = end_min + 300,
    rpeak_equiv_end_max = end_max + 300
  )

rpeak_window_stats <- hep_window_data %>%
  filter(hep_relative_to == "R-peak") %>%
  summarise(
    start_min = min(start_time),
    start_max = max(start_time),
    end_min = min(end_time),
    end_max = max(end_time)
  )

  # Find the overlap region for R-peak studies using cumsum-based inflection points
  # Split by averaging vs clustering approaches
  rpeak_overlap_analysis <- hep_window_data %>%
    filter(hep_relative_to == "R-peak") %>%
    split(.$method_category) %>%
    map(function(data) {
      if (nrow(data) == 0) return(NULL)
      
      all_edges <- sort(unique(c(data$start_time, data$end_time)))
      start_counts <- tabulate(match(data$start_time, all_edges), nbins = length(all_edges))
      end_counts <- tabulate(match(data$end_time, all_edges), nbins = length(all_edges))
      starts_cumsum <- cumsum(start_counts)
      ends_cumsum <- cumsum(end_counts)
      start_diffs <- diff(starts_cumsum)
      core_start_idx <- which.max(start_diffs) + 1
      core_start <- all_edges[core_start_idx]
      end_diffs <- diff(ends_cumsum)
      core_end_idx <- which.max(end_diffs) + 1
      core_end <- all_edges[core_end_idx]
      
      # Count studies that overlap with the core window (any overlap)
      studies_overlapping_core <- data %>%
        filter(!(end_time < core_start | start_time > core_end)) %>%
        nrow()
      
      # Keep the original "fully including" calculation for comparison
      studies_fully_including_core <- data %>%
        filter(start_time <= core_start & end_time >= core_end) %>%
        nrow()
      
      list(
        core_start = round(core_start, 0),
        core_end = round(core_end, 0),
        # Use overlap as primary metric (more meaningful)
        core_percentage = round(studies_overlapping_core / nrow(data) * 100, 1),
        core_count = studies_overlapping_core,
        total_rpeak = nrow(data),
        # Additional info
        fully_including_percentage = round(studies_fully_including_core / nrow(data) * 100, 1),
        fully_including_count = studies_fully_including_core,
        median_window_size = round(median(data$end_time - data$start_time), 0),
        core_window_size = round(core_end - core_start, 0)
      )
    }) %>%
    compact()  # Remove NULL entries


# Significant effects 
df_signif <- df_pipelines %>% filter(significant_test == 1)

# Create merged start/end/ref columns 
df_signif <- df_signif %>%
  mutate(
    merged_start = if_else(averaging_time == "1", as.character(hep_start), as.character(significant_start_ms)),
    merged_end   = if_else(averaging_time == "1", as.character(hep_end), as.character(significant_end_ms)),
    merged_ref   = if_else(averaging_time == "1", hep_relative_to, significant_relative_to)
  )

significant_effects_data <- df_signif %>%
  filter(merged_ref %in% c("R-peak", "T-peak"), significant_test == 1) %>%
  mutate(
    hep_start = as.numeric(hep_start),
    hep_end   = as.numeric(hep_end),
    significant_start_ms = as.numeric(significant_start_ms),
    significant_end_ms   = as.numeric(significant_end_ms),
    start_time = if_else(averaging_time == "1", hep_start, significant_start_ms),
    end_time   = if_else(averaging_time == "1", hep_end, significant_end_ms),
    reference = merged_ref
  ) %>%
  filter(!is.na(start_time), !is.na(end_time))

# Overall significant effects ranges
sig_rpeak_range <- significant_effects_data %>%
  filter(reference == "R-peak") %>%
  summarise(
    start_min = min(start_time),
    start_max = max(start_time),
    end_min = min(end_time),
    end_max = max(end_time)
  )

sig_tpeak_range <- significant_effects_data %>%
  filter(reference == "T-peak") %>%
  summarise(
    start_min = min(start_time),
    start_max = max(start_time),
    end_min = min(end_time),
    end_max = max(end_time)
  )

# Compare peak of significant effects for clustering vs averaging 

# R-peak analysis
clustering_rpeak <- significant_effects_data %>%
  filter(method_category == "Clustering", reference == "R-peak") %>%
  filter(!is.na(start_time), !is.na(end_time))

averaging_rpeak <- significant_effects_data %>%
  filter(method_category == "Averaging", reference == "R-peak") %>%
  filter(!is.na(start_time), !is.na(end_time))

# T-peak analysis
clustering_tpeak <- significant_effects_data %>%
  filter(method_category == "Clustering", reference == "T-peak") %>%
  filter(!is.na(start_time), !is.na(end_time))

averaging_tpeak <- significant_effects_data %>%
  filter(method_category == "Averaging", reference == "T-peak") %>%
  filter(!is.na(start_time), !is.na(end_time))

# Perform the statistical comparisons
stat_comparison_results <- list()
stat_comparison_results$rpeak <- perform_peak_timing_comparison(clustering_rpeak, averaging_rpeak)
stat_comparison_results$tpeak <- perform_peak_timing_comparison(clustering_tpeak, averaging_tpeak)
```

## Cardiac Reference Event Selection

HEP reference events (`r hep_reference_level`):
* R-peak reference: **`r hep_reference_stats$percentage[hep_reference_stats$reference_category == "R-peak"]`%** of studies (`r hep_reference_stats$n[hep_reference_stats$reference_category == "R-peak"]`/`r sum(hep_reference_stats$n)`)
* T-wave reference: **`r hep_reference_stats$percentage[hep_reference_stats$reference_category == "T-peak"]`%** of studies (`r hep_reference_stats$n[hep_reference_stats$reference_category == "T-peak"]`/`r sum(hep_reference_stats$n)`)

## HEP Analysis Time Windows

### T-wave Referenced Analysis

* Time range: **`r tpeak_window_stats$start_min`** to **`r tpeak_window_stats$end_max`** ms after T-wave
* R-peak equivalent: approx. **`r tpeak_window_stats$rpeak_equiv_start_min`** to **`r tpeak_window_stats$rpeak_equiv_end_max`** ms after R-peak

### R-peak Referenced Analysis

* Time range: **`r rpeak_window_stats$start_min`** to **`r rpeak_window_stats$end_max`** ms relative to R-peak

**Core overlap windows by analysis method:**
`r if("Averaging" %in% names(rpeak_overlap_analysis)) paste0("* Averaging: **", rpeak_overlap_analysis$Averaging$core_start, "** to **", rpeak_overlap_analysis$Averaging$core_end, "** ms (", rpeak_overlap_analysis$Averaging$core_window_size, "ms window)")` 
`r if("Averaging" %in% names(rpeak_overlap_analysis)) paste0("  - Studies overlapping with core: ", rpeak_overlap_analysis$Averaging$core_percentage, "% (", rpeak_overlap_analysis$Averaging$core_count, "/", rpeak_overlap_analysis$Averaging$total_rpeak, ")")` 
`r if("Averaging" %in% names(rpeak_overlap_analysis)) paste0("  - Studies fully including core: ", rpeak_overlap_analysis$Averaging$fully_including_percentage, "% (", rpeak_overlap_analysis$Averaging$fully_including_count, "/", rpeak_overlap_analysis$Averaging$total_rpeak, ")")` 
`r if("Averaging" %in% names(rpeak_overlap_analysis)) paste0("  - Median window size: ", rpeak_overlap_analysis$Averaging$median_window_size, "ms")` 

`r if("Clustering" %in% names(rpeak_overlap_analysis)) paste0("* Clustering: **", rpeak_overlap_analysis$Clustering$core_start, "** to **", rpeak_overlap_analysis$Clustering$core_end, "** ms (", rpeak_overlap_analysis$Clustering$core_window_size, "ms window)")` 
`r if("Clustering" %in% names(rpeak_overlap_analysis)) paste0("  - Studies overlapping with core: ", rpeak_overlap_analysis$Clustering$core_percentage, "% (", rpeak_overlap_analysis$Clustering$core_count, "/", rpeak_overlap_analysis$Clustering$total_rpeak, ")")` 
`r if("Clustering" %in% names(rpeak_overlap_analysis)) paste0("  - Studies fully including core: ", rpeak_overlap_analysis$Clustering$fully_including_percentage, "% (", rpeak_overlap_analysis$Clustering$fully_including_count, "/", rpeak_overlap_analysis$Clustering$total_rpeak, ")")` 
`r if("Clustering" %in% names(rpeak_overlap_analysis)) paste0("  - Median window size: ", rpeak_overlap_analysis$Clustering$median_window_size, "ms")`

## Baseline Correction

### General Statistics

**Overall baseline correction usage across all studies:**
* Studies using baseline correction: **`r baseline_correction_stats %>% filter(baseline_category %in% c("Yes", "No", "Both")) %>% summarise(total_pct = sum(percentage_of_all_studies)) %>% pull(total_pct)`%** (`r sum(baseline_correction_stats$n[baseline_correction_stats$baseline_category %in% c("Yes", "No", "Both")])`/`r total_studies`)

**Among studies that reported baseline correction information:**
* Studies using baseline correction: **`r baseline_correction_stats %>% filter(baseline_category %in% c("Yes", "Both")) %>% summarise(total_pct = sum(percentage_within_reporting)) %>% pull(total_pct)`%** (`r sum(baseline_correction_stats$n[baseline_correction_stats$baseline_category %in% c("Yes", "Both")])`/`r sum(baseline_correction_stats$n)`)
* Studies not using baseline correction: **`r baseline_correction_stats %>% filter(baseline_category == "No") %>% pull(percentage_within_reporting)`%** (`r baseline_correction_stats %>% filter(baseline_category == "No") %>% pull(n)`/`r sum(baseline_correction_stats$n)`)

Baseline correction (`r baseline_correction_level`):
* Pipelines using baseline correction: **`r baseline_pct`%** (`r sum(baseline_correction_stats$n[baseline_correction_stats$baseline_category %in% c("Yes", "Both")])`/`r total_studies`)

### T-wave Baseline Correction

* Studies using baseline: **`r tpeak_baseline_data$n_studies`** studies
* Baseline window: **`r tpeak_baseline_data$start_min`** to **`r tpeak_baseline_data$end_max`** ms before T-wave

### R-peak Baseline Correction

* Baseline window range: **`r rpeak_baseline_data$start_min`** to **`r rpeak_baseline_data$end_max`** ms around R-peak
* Studies ending baseline before QRS: **`r baseline_before_qrs_stats$percentage_before_qrs`%** (`r baseline_rpeak_range$studies_ending_before_qrs`/`r baseline_rpeak_range$total_studies`)

## Significant HER Effects Time Ranges

### R-peak Referenced Effects

* Significant effects range: **`r sig_rpeak_range$start_min`** to **`r sig_rpeak_range$end_max`** ms

### T-wave Referenced Effects

* Significant effects range: **`r sig_tpeak_range$start_min`** to **`r sig_tpeak_range$end_max`** ms

## Statistical Analysis Methods Comparison

### R-peak Analysis

* **Peak Distribution Analysis** (from cumulative plots):
  - Clustering peak: **`r sprintf("%.0f", stat_comparison_results$rpeak$peak1)`** ms
  - Averaging peak: **`r sprintf("%.0f", stat_comparison_results$rpeak$peak2)`** ms
  - Peak difference: `r sprintf("%.0f", abs(stat_comparison_results$rpeak$peak1 - stat_comparison_results$rpeak$peak2))` ms

* **Statistical Test** (Permutation test on peak positions):
  - Sample sizes: n₁ = `r stat_comparison_results$rpeak$n1`, n₂ = `r stat_comparison_results$rpeak$n2`
  - Permutation test: p **`r ifelse(stat_comparison_results$rpeak$permutation_p_value < 0.001, "< 0.001", paste("=", sprintf("%.3f", stat_comparison_results$rpeak$permutation_p_value)))`** (**`r stat_comparison_results$rpeak$n_permutations`** permutations)

### T-wave Analysis

* **Peak Distribution Analysis** (from cumulative plots):
  - Clustering peak: **`r sprintf("%.0f", stat_comparison_results$tpeak$peak1)`** ms
  - Averaging peak: **`r sprintf("%.0f", stat_comparison_results$tpeak$peak2)`** ms
  - Peak difference: `r sprintf("%.0f", abs(stat_comparison_results$tpeak$peak1 - stat_comparison_results$tpeak$peak2))` ms

* **Statistical Test** (Permutation test on peak positions):
  - Sample sizes: n₁ = `r stat_comparison_results$tpeak$n1`, n₂ = `r stat_comparison_results$tpeak$n2`
  - Permutation test: p **`r ifelse(stat_comparison_results$tpeak$permutation_p_value < 0.001, "< 0.001", paste("=", sprintf("%.3f", stat_comparison_results$tpeak$permutation_p_value)))`** (**`r stat_comparison_results$tpeak$n_permutations`** permutations)

### Analysis Window Definition

HEP determination method (`r hep_determination_level`):
* Studies using averaging: **`r hep_determination_stats$percentage[hep_determination_stats$determination_category == "Averaging"]`%** (`r hep_determination_stats$n[hep_determination_stats$determination_category == "Averaging"]`/`r sum(hep_determination_stats$n)`)
* Studies using clustering: **`r hep_determination_stats$percentage[hep_determination_stats$determination_category == "Clustering"]`%** (`r hep_determination_stats$n[hep_determination_stats$determination_category == "Clustering"]`/`r sum(hep_determination_stats$n)`)
* Studies using both approaches: **`r hep_determination_stats$percentage[hep_determination_stats$determination_category == "Both"]`%** (`r hep_determination_stats$n[hep_determination_stats$determination_category == "Both"]`/`r sum(hep_determination_stats$n)`)

* Studies with a-priori defined analysis windows: **`r hep_window_type_stats$percentage[hep_window_type_stats$window_type_category == "Primary"]`%** (`r hep_window_type_stats$n[hep_window_type_stats$window_type_category == "Primary"]`/`r sum(hep_window_type_stats$n)`)
* Studies using two-step procedures (data-dependent window selection): **`r hep_window_type_stats$percentage[hep_window_type_stats$window_type_category == "Secondary"]`%** (`r hep_window_type_stats$n[hep_window_type_stats$window_type_category == "Secondary"]`/`r sum(hep_window_type_stats$n)`)

## HEP dependent variables analysis

```{r hep-values}
hep_value_studies <- df_pipelines %>%
  filter(value != "none") %>%
  distinct(PMID, value) %>%
  count(value, sort = TRUE) %>%
  mutate(percentage = round(n / sum(n) * 100, 1))

# Check if HEP values are at study or pipeline level
hep_value_level <- check_studies_or_pipelines(df_pipelines, "value")
```

HEP values (`r hep_value_level`):
* `r hep_value_studies$value[1]`: **`r hep_value_studies$n[1]`** studies (**`r hep_value_studies$percentage[1]`%**)
* `r hep_value_studies$value[2]`: **`r hep_value_studies$n[2]`** studies (**`r hep_value_studies$percentage[2]`%**)
* `r hep_value_studies$value[3]`: **`r hep_value_studies$n[3]`** studies (**`r hep_value_studies$percentage[3]`%**)
* Other measures: **`r sum(hep_value_studies$n[4:nrow(hep_value_studies)])`** studies (**`r sum(hep_value_studies$percentage[4:nrow(hep_value_studies)])`%**)


## Statistical Analysis and power considerations

```{r stats}

# Calculate percentages for statistical test families
statistical_test_stats <- df_pipelines %>%
  distinct(PMID, statistics) %>%
  filter(statistics != "unknown" & statistics != "none") %>% 
  count(statistics) %>%
  mutate(percentage = round(n / sum(n) * 100, 1)) %>%
  arrange(desc(percentage))

# Check if statistical tests are at study or pipeline level
statistics_level <- check_studies_or_pipelines(df_pipelines, "statistics")

# Calculate percentages for analysis type
analysis_type_stats <- df_pipelines %>%
  mutate(
    is_group_or_condition = if_else(grepl("group", tolower(hypothesis)), TRUE, FALSE),
    is_correlation = if_else(grepl("correlation", tolower(hypothesis)), TRUE, FALSE)
  ) %>%
  summarise(
    pct_group_or_condition = round(mean(is_group_or_condition, na.rm = TRUE) * 100, 1),
    pct_correlation = round(mean(is_correlation, na.rm = TRUE) * 100, 1)
  )

# Participant statistics
participants_stats <- df_pipelines %>%
  distinct(PMID, sample_size) %>%
  summarise(
    participants_min = min(sample_size, na.rm = TRUE),
    participants_max = max(sample_size, na.rm = TRUE),
    participants_median = median(sample_size, na.rm = TRUE),
    participants_n = sum(!is.na(sample_size))
  )

# Estimated and original # Trials per pipeline statistics
trials_stats <- df_pipelines %>%
  filter(!is.na(trials_Mean)) %>%
  summarise(
    min_trials = min(trials_Mean, na.rm = TRUE),
    max_trials = max(trials_Mean, na.rm = TRUE),
    mean_trials = round(median(trials_Mean, na.rm = TRUE), 1)
  )

# Check if trials are at study or pipeline level
trials_level <- check_studies_or_pipelines(df_pipelines, "trials_Mean")

#Missing HER Trials
pct_missing_trials_original <- results_df_missing %>%
  filter(Column == "trials_original") %>%
  mutate(Percent = round(Metric * 100, 1)) %>%
  pull(Percent)


# Statistical tests split by clustering vs averaging - most common for each method
stats_table <- df_pipelines %>%
  filter(statistics != "unknown" & statistics != "none" & 
         method_category %in% c("Averaging", "Clustering")) %>%
  distinct(PMID, statistics, method_category) %>%
  count(method_category, statistics) %>%
  group_by(method_category) %>%
  mutate(
    total_in_category = sum(n),
    percentage = round(n / total_in_category * 100, 1)
  ) %>%
  arrange(method_category, desc(percentage)) %>%
  slice_head(n = 3) %>%
  ungroup() %>%
  select(method_category, statistics, n, percentage) %>%
  rename(
    "Analysis Method" = method_category,
    "Statistical Test" = statistics,
    "Studies (n)" = n,
    "Percentage (%)" = percentage
  )


# Calculate minimum detectable effect sizes (Hedges' g) for each pipeline
hedges_column <- compute_effect_columns(df_pipelines, 
                                        test_type_col = statistics, 
                                        sample_size_col = sample_size, 
                                        groups_col = groups, 
                                        conditions_col = conditions)

# Combine with original data
hedges_data <- bind_cols(df_pipelines, hedges_column) %>%
              distinct(PMID, hedges_g, .keep_all = TRUE) %>%
              filter(clustering ==0)

# Average of Coll et al. (2020) reported average effect size
# not sure if this is the right way to do it
coll_average_effect <- mean(c(0.35, 0.37, 0.49, 0.72))

# Calculate percentage of pipelines that could detect each individual Coll et al. effect size
individual_effect_sizes <- c(0.35, 0.37, 0.49, 0.72)
effect_size_names <- c("interoceptive_performance", "attention_to_heart", "clinical_vs_control", "arousal")

# Calculate power for each individual effect size
power_stats <- map2_dfr(individual_effect_sizes, effect_size_names, function(effect_size, name) {
  hedges_data %>%
    summarise(
      effect_type = name,
      effect_size = effect_size,
      total_pipelines = n(),
      pipelines_detecting = sum(hedges_g <= effect_size, na.rm = TRUE),
      percentage_detecting = round(pipelines_detecting / total_pipelines * 100, 1)
    )
})

# Calculate percentage of pipelines that could detect the Coll et al. average effect size
pipelines_detect_coll <- hedges_data %>%
  summarise(
    total_pipelines = n(),
    pipelines_detecting_coll = sum(hedges_g <= coll_average_effect, na.rm = TRUE),
    percentage_detecting_coll = round(pipelines_detecting_coll / total_pipelines * 100, 0)
  )

# Calculate minimal detectable effect size statistics
hedges_g_stats <- hedges_data %>%
  summarise(
    min_hedges_g = round(min(hedges_g, na.rm = TRUE), 2),
    max_hedges_g = round(max(hedges_g, na.rm = TRUE), 2),
    median_hedges_g = round(median(hedges_g, na.rm = TRUE), 2)
  )

# Preregistration
pct_prereg <- df_pipelines %>%
  distinct(PMID, Preregistration) %>%
  summarise(
    percentage = round(mean(Preregistration, na.rm = TRUE) * 100, 1)
  ) %>%
  pull(percentage)

# publication bias
non_sig_results <- df_pipelines %>%
  group_by(PMID) %>%
  filter(all(significant_test == 0, na.rm = TRUE)) %>%
  distinct(PMID, .keep_all = TRUE) %>%
  ungroup() 

```

Number of participants per pipeline: Min: **`r participants_stats$participants_min`**, Max: **`r participants_stats$participants_max`**, Median: **`r participants_stats$participants_median`**

Number of groups: **`r min(df_pipelines$groups, na.rm = TRUE)`** - **`r max(df_pipelines$groups, na.rm = TRUE)`** 

Number of conditions: **`r min(df_pipelines$conditions, na.rm = TRUE)`** - **`r max(df_pipelines$conditions, na.rm = TRUE)`** 

Percentage of pipelines with group or condition analysis: **`r analysis_type_stats$pct_group_or_condition`%** (`r sum(grepl("group", tolower(df_pipelines$hypothesis)), na.rm = TRUE)`/`r sum(!is.na(df_pipelines$hypothesis))`)

Percentage of pipelines with correlation analysis: **`r analysis_type_stats$pct_correlation`%** (`r sum(grepl("correlation", tolower(df_pipelines$hypothesis)), na.rm = TRUE)`/`r sum(!is.na(df_pipelines$hypothesis))`)

Number of trials per pipeline: Min: **`r trials_stats$min_trials`**, Max: **`r trials_stats$max_trials`**, Median: **`r trials_stats$mean_trials `**

Percentage of missing HEP epoch info: **`r pct_missing_trials_original`%**

### Statistical Analysis Methods

Statistical test families (`r statistics_level`):

* **`r statistical_test_stats$statistics[1]`**: **`r statistical_test_stats$percentage[1]`%** (`r statistical_test_stats$n[1]` studies)
* **`r statistical_test_stats$statistics[2]`**: **`r statistical_test_stats$percentage[2]`%** (`r statistical_test_stats$n[2]` studies)  
* **`r statistical_test_stats$statistics[3]`**: **`r statistical_test_stats$percentage[3]`%** (`r statistical_test_stats$n[3]` studies)
* **`r statistical_test_stats$statistics[4]`**: **`r statistical_test_stats$percentage[4]`%** (`r statistical_test_stats$n[4]` studies)

#### Statistical Tests by Analysis Method

```{r stats-by-method-table, results='asis'}
knitr::kable(stats_table, 
             caption = "Most common statistical test families by analysis method (Averaging vs Clustering)",
             align = c("l", "l", "c", "c"))
```

### Power Analysis

Only **`r pipelines_detect_coll$percentage_detecting_coll`%** of pipelines (`r pipelines_detect_coll$pipelines_detecting_coll`/`r pipelines_detect_coll$total_pipelines`) had sufficient power to detect the average effect size reported by Coll et al. (2020).

The resulting minimal detectable effect sizes range from **`r hedges_g_stats$min_hedges_g`** to **`r hedges_g_stats$max_hedges_g`**, with a median of **`r hedges_g_stats$median_hedges_g`** Hedges' g.

- **`r power_stats$percentage_detecting[power_stats$effect_type == "interoceptive_performance"]`%** of pipelines had enough power to detect Hedges' g of 0.35 (interoceptive performance meta-estimate)
- **`r power_stats$percentage_detecting[power_stats$effect_type == "attention_to_heart"]`%** of pipelines could reliably detect Hedges' g of 0.37 (attention to heart meta-estimate)
- **`r power_stats$percentage_detecting[power_stats$effect_type == "clinical_vs_control"]`%** of pipelines could reliably detect Hedges' g of 0.49 (clinical vs. control groups meta-estimate)
- **`r power_stats$percentage_detecting[power_stats$effect_type == "arousal"]`%** of pipelines could reliably detect Hedges' g of 0.72 (arousal meta-estimate).

These observations suggest that **`r 100 - max(power_stats$percentage_detecting)`%** to **`r 100 - min(power_stats$percentage_detecting)`%** of pipelines may have yielded underpowered and potentially unreliable findings.

### Preregistration
Percentage of pipelines with preregistration: **`r pct_prereg`%** 

### publication bias

Number and percentage of studies without significant results: **`r nrow(non_sig_results)`** studies (**`r round(nrow(non_sig_results) / total_studies * 100, 1)`%**)

### Control Analyses

```{r control analyses}

  control_variable_synonyms <- get_control_variable_mappings()
  
  ## 1. Pre-processing 
  df_unique    <- dplyr::distinct(df_included, PMID, controls)
  df_controls  <- ifelse(is.na(df_unique$controls), "", df_unique$controls)
  
  # accumulate patterns per category
  category_patterns <- list()
  for (nm in names(control_variable_synonyms)) {
    meta <- control_variable_synonyms[[nm]]
    category_patterns[[meta$category]] <-
      c(category_patterns[[meta$category]], nm, meta$synonyms)
  }
  categories <- names(category_patterns)
  
  # TRUE/FALSE presence matrix
  category_presence <- matrix(
    FALSE,
    nrow = nrow(df_unique),
    ncol = length(categories),
    dimnames = list(NULL, categories)
  )
  for (cat in categories) {
    pat <- paste0("\\b(", paste(unique(category_patterns[[cat]]), collapse = "|"), ")\\b")
    category_presence[, cat] <- stringr::str_detect(
      tolower(df_controls),
      tolower(pat)
    )
  }
  
  ## 2. Long data frame for hist_panel() 
  control_long_df <- category_presence %>%
    as.data.frame() %>%
    dplyr::mutate(PMID = df_unique$PMID) %>%
    tidyr::pivot_longer(
      cols      = categories,
      names_to  = "category",
      values_to = "present"
    ) %>%
    dplyr::filter(present) %>%          # keep only matches
    dplyr::select(PMID, category)
  
  controls_level <- check_studies_or_pipelines(df_included, "controls")
  
  ecg_heartbeat_df_distinct <- distinct(control_long_df, PMID, category)

  # Get counts and calculate proportions
  ecg_heartbeat_counts_df <- ecg_heartbeat_df_distinct%>%
    count(category) %>%
    arrange(desc(n)) %>%  # Sort by frequency
    mutate(prop = n / sum(n))  # Calculate proportions

# Calculate percentage for ECG and Heartbeat-Related Controls
ecg_heartbeat_related_pct <- ecg_heartbeat_counts_df %>%
  filter(category == "ECG and Heartbeat-Related Controls") %>%
  pull(prop) * 100

# only ECG controls

## 0. Look-ups
control_variable_synonyms <- get_control_variable_mappings()
target_cat <- "ECG and Heartbeat-Related Controls"

# Identify ECG control variables
ecg_vars <- names(control_variable_synonyms)[
  vapply(
    control_variable_synonyms,
    function(meta) identical(meta$category, target_cat),
    logical(1)
  )
]
if (length(ecg_vars) == 0)
  stop("No variables mapped to the category ‘", target_cat, "’.")

## 2. Build a (word-boundary) regex for *each* variable
make_pat <- function(var) {
  terms <- c(
    var,                                   # the variable name (list key)
    control_variable_synonyms[[var]]$synonyms %||% character(0)
  )
  paste0("\\b(", paste(unique(terms), collapse = "|"), ")\\b")
}
var_patterns <- setNames(lapply(ecg_vars, make_pat), ecg_vars)

## 3. Pre-process the data 
df_unique   <- dplyr::distinct(df_included, PMID, controls)
df_controls <- ifelse(is.na(df_unique$controls), "", df_unique$controls)

## 4. TRUE/FALSE presence matrix at *variable* level
presence_vars <- sapply(
  var_patterns,
  function(pat) stringr::str_detect(tolower(df_controls), tolower(pat))
)

## 5. Long data frame 
ecg_control_long_df <- presence_vars |>
  as.data.frame() |>
  dplyr::mutate(PMID = df_unique$PMID) |>
  tidyr::pivot_longer(
    cols      = ecg_vars,
    names_to  = "variable",
    values_to = "present"
  ) |>
  dplyr::filter(present) |>
  dplyr::select(PMID, variable)

ecg_df_distinct <- distinct(ecg_control_long_df, PMID, variable)

# Get counts and calculate proportions
ecg_counts_df <- ecg_df_distinct %>%
  count(variable) %>%
  arrange(desc(n)) %>%  # Sort by frequency
  mutate(prop = n / sum(n))  # Calculate proportions

# Calculate percentage for ECG and Heartbeat-Related Controls
ecg_related_pct <- ecg_counts_df %>%
  filter(variable == "ECG") %>%
  pull(prop) * 100

# RR control analyses
RR_related_pct <- ecg_counts_df %>%
  filter(variable == "RR Interval") %>%
  pull(prop) * 100

#HRV control analyses
HRV_related_pct <- ecg_heartbeat_counts_df %>%
  filter(category == "Heart Rate Variability (HRV) Controls") %>%
  pull(prop) * 100

# Blood pressure
BP_related_pct <- ecg_heartbeat_counts_df %>%
  filter(category == "Cardiovascular and Blood Pressure Controls") %>%
  pull(prop) * 100

## surrogate heartbeat analyses
ecg_related_pct <- ecg_counts_df %>%
  filter(variable == "Surrogate Heartbeats") %>%
  pull(prop) * 100
```

Control variables (`r controls_level`):
**`r sprintf("%.1f", ecg_related_pct)`%** of pipelines (`r ecg_counts_df$n[1]`/`r nrow(ecg_df_distinct)`) control for ECG.

**`r sprintf("%.1f", ecg_heartbeat_related_pct)`%** of pipelines (`r ecg_heartbeat_counts_df$n[1]`/`r nrow(ecg_heartbeat_df_distinct)`) control for overall heartbeat-related variables.

RR Interval: **`r sprintf("%.1f", RR_related_pct)`%** of pipelines (`r ecg_counts_df$n[ecg_counts_df$variable == "RR Interval"]`/`r nrow(ecg_df_distinct)`) control for RR intervals.

Heart rate variability controls: **`r sprintf("%.1f", HRV_related_pct)`%** of pipelines (`r ecg_heartbeat_counts_df$n[ecg_heartbeat_counts_df$category == "Heart Rate Variability (HRV) Controls"]`/`r nrow(ecg_heartbeat_df_distinct)`) control for HRV.

Blood pressure controls: **`r sprintf("%.1f", BP_related_pct)`%** of pipelines (`r ecg_heartbeat_counts_df$n[ecg_heartbeat_counts_df$category == "Cardiovascular and Blood Pressure Controls"]`/`r nrow(ecg_heartbeat_df_distinct)`) control for blood pressure.

Surrogate heartbeat controls: **`r sprintf("%.1f", ecg_related_pct)`%** of pipelines (`r ecg_counts_df$n[ecg_counts_df$variable == "Surrogate Heartbeats"]`/`r nrow(ecg_df_distinct)`) control for surrogate heartbeats.
Surrogate heartbeat controls: **`r ecg_related_pct`%** of pipelines (`r ecg_counts_df$n[ecg_counts_df$variable == "Surrogate Heartbeats"]`/`r nrow(ecg_df_distinct)`) control for surrogate heartbeats.
