---
title: "Manuscript Summary"
subtitle: "A Systematic Review of Methods Used for Studying Heartbeat Evoked Responses"
output: 
  html_document:
    self_contained: false
    theme: null
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
source("init_workspace.R")

# Paths
data_path <- file.path(getwd(), 'data')
func_path <- file.path(getwd(), 'functions')
derivatives_path <- file.path(data_path, 'derivatives')
df_included <- read.csv(file.path(derivatives_path, 'included.csv'))
df_screening <- read.csv(file.path(derivatives_path, 'screening.csv'))

# Helper function to determine if percentages should refer to studies or pipelines
check_studies_or_pipelines <- function(df, variable_column, group_col = "PMID") {
  df_distinct <- df %>% distinct(!!sym(group_col), !!sym(variable_column))
  multiple_rows_per_group <- any(table(df_distinct[[group_col]]) > 1)
  if (multiple_rows_per_group) {
    return("pipelines")
  } else {
    return("studies")
  }
}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      results = "asis")

# Create study-level and pipeline-level datasets for efficiency
df_studies <- df_included %>% distinct(PMID, .keep_all = TRUE)
df_pipelines <- df_included
```

```{r helper-functions}
get_row <- function(df, column, value) {
  as.list(df[df[[column]] == value,])
}

get_summary <- function(df, column, 
                        digits_min = 0, digits_max = 0, digits_median = 1) {
  list(
    min = round(min(df[[column]], na.rm = TRUE), digits = digits_min),
    max = round(max(df[[column]], na.rm = TRUE), digits = digits_max),
    median = round(median(df[[column]], na.rm = TRUE), digits = digits_median)
  )
}

disp_results <- function(df, 
                         column = "column",
                         percentage = "percentage",
                         count = "count",
                         total = "total",
                         level = "level") {
  for (i in 1:nrow(df)) {
    row <- df[i, ]
    cat(
      paste0(
        '  * ', row[[column]], ': ',
        '**', row[[percentage]], '%**', 
        ' (**', row[[count]], '** / **', row[[total]], '** ', row[[level]], ')\n'
      )
    )
  }
}
```

# Overview

This document provides all values mentioned in the manuscript "Heartbeat-evoked responses in MEG/EEG: A systematic review of methods with suggestions for analysis and reporting". All sections of this document apart from this overview match the corresponding section of the manuscript. Numbers highlighted in **bold** are also present in the manuscript.

## Important Distinction: Studies vs Pipelines

- **Studies**: Unique publications (identified by PMID). Each study represents one research paper.
- **Pipelines**: Individual analysis approaches within studies. Some studies report multiple analysis pipelines (e.g. different time windows, or statistical approaches).

# 2. Methods

## 2.1. Literature search

```{r data-export}
# Get the number of papers in Pubmed export
export_stats <- get_export_stats(file.path(data_path, 'exports'))
```

Table 1 - number of retrieved papers:

* 15.01.2024: **`r export_stats$num_query1`**
* 24.07.2024: **`r export_stats$num_query2`** (rerun: **`r export_stats$num_query2_rerun`**)
* 05.08.2024: **`r export_stats$num_query3`**
* After removing duplicates: **`r export_stats$num_merged`**

```{r literature-search, results='asis'}
screening_pubmed <- df_screening[df_screening$source == "pubmed",]
screening_manual <- df_screening[df_screening$source == "manual",]

total_retrieved_pubmed <- nrow(screening_pubmed)
total_included_pubmed <- nrow(screening_pubmed[screening_pubmed$Include == 1,])
total_retrieved_manual <- nrow(screening_manual)
total_included_manual <- nrow(screening_manual[screening_manual$Include == 1,])
```

Exported from Pubmed:

* Retrieved: **`r total_retrieved_pubmed`** studies
* Included: **`r total_included_pubmed`** studies

Manually added:

* Retrieved: **`r total_retrieved_manual`** studies
* Included: **`r total_included_manual`** studies

Final sample: **`r total_included_pubmed + total_included_manual`** studies

## 2.3. Data analysis

Analysis parameters:

* Entropy - binning continuous variables if at least **`r params$entropy_unique_threshold`** unique values are present
* Power computation - significance level: **`r params$hedges_sig_level * 100`%**
* Power computation - power threshold: **`r params$hedges_power_level * 100`%**
* Number of permutations for testing peak differences: **`r params$peak_stats_permutations`**

# 3. Results

## 3.1. Overview of the included studies

```{r literature-overview}
# Basic counts
total_studies <- nrow(df_studies)

# Year range (based on unique studies)
year_range <- df_studies %>% 
  summarise(min_year = min(Year, na.rm = TRUE), 
            max_year = max(Year, na.rm = TRUE))

# Modality breakdown (unique studies)
modality_counts <- df_studies %>%
  count(modality) %>%
  mutate(percentage = round_custom(n / sum(n) * 100))
modality_eeg <- get_row(modality_counts, "modality", "EEG")
modality_meg <- get_row(modality_counts, "modality", "MEG")

# Task vs resting state - studies that have both vs only one type
study_types <- df_studies %>%
  count(study_category) %>%
  mutate(percentage = round_custom(n / sum(n) * 100))

study_type_task <- get_row(study_types, "study_category", "Task")
study_type_rest <- get_row(study_types, "study_category", "Rest")
study_type_both <- get_row(study_types, "study_category", "Both")
```

Total studies: **`r total_studies`** (**`r year_range$min_year`**-**`r year_range$max_year`**)

Modality:

* EEG: **`r modality_eeg$n`** studies (**`r modality_eeg$percentage`%**)
* MEG: **`r modality_meg$n`** studies (**`r modality_meg$percentage`%**)

Study type distribution:

* Task-based: **`r study_type_task$n`** studies (**`r study_type_task$percentage`%**)
* Resting-state: **`r study_type_rest$n`** studies (**`r study_type_rest$percentage`%**)
* Both: **`r study_type_both$n`** studies (**`r study_type_both$percentage`%**)
 
## 3.2. Overview of methodological choices

```{r multiple-choices}
total_pipelines <- nrow(df_pipelines)

# Get target columns from pipeline steps
target_columns <- unlist(pipeline_steps, use.names = FALSE)

# Calculate percentage of studies with multiple choices for each method
multiple_df <- multiple_choices(df_pipelines, target_columns) %>%
  mutate(percentage = round_custom(percentage * 100))

multiple_stats <- get_row(multiple_df, "Column", "statistics")
multiple_hep_start <- get_row(multiple_df, "Column", "hep_start")  # pick as maximum among start and end
```

Total pipelines: **`r total_pipelines`** 

### Multiple choices

Studies using multiple choices for:

* Statistical tests: **`r multiple_stats$percentage`%** (**`r multiple_stats$count`** / **`r multiple_stats$total`**)

* HER window start or end times: **`r multiple_hep_start$percentage`%** (**`r multiple_hep_start$count`** / **`r multiple_hep_start$total`**)

```{r missing-info}
# Variables with >40% missing info
missing_df <- missing_information(df_pipelines, target_columns) %>%
  mutate(percentage = round_custom(percentage * 100))

missing_cfa_ics <- get_row(missing_df, "Column", "rejected_cardiac_ics")
missing_ecg_ground <- get_row(missing_df, "Column", "ecg_ground")
missing_ecg_locations <- get_row(missing_df, "Column", "ecg_locations")

missing_df_top <- missing_df %>% 
  filter(percentage >= 40) %>%
  arrange(-percentage) %>%
  select(Column, count, total, percentage)
```

### Missing information

* cardiac IC rejection information (among those using CFA removal): **`r missing_cfa_ics$percentage`%** (**`r missing_cfa_ics$count`** / **`r missing_cfa_ics$total`**)

* unknown ECG ground location: **`r missing_ecg_ground$percentage`%** (**`r missing_ecg_ground$count`** / **`r missing_ecg_ground$total`**)

* ECG electrode locations: **`r missing_ecg_locations$percentage`%** (**`r missing_ecg_locations$count`** / **`r missing_ecg_locations$total`**)

```{r high-missing-table, results='asis'}
knitr::kable(missing_df_top, 
             caption = "Variables with >40% missing values across studies",
             col.names = c("Variable", "Missing", "Total", "Missing (%)"))
```

## 3.3. M/EEG acquisition & preprocessing

### Online reference

```{r online-reference}
# Online reference distribution
df_ref <- df_pipelines %>% preprocess_reference()
online_ref_counts <- hist_discrete(df_ref, "reference_online",
                                   modality_filter = "EEG",
                                   allowed = ref_mapping[online_ref_categories]) %>%
  mutate(percentage = round_custom(percentage))

online_ref_lm <- get_row(online_ref_counts, "reference_online", "LinkM")
online_ref_cz <- get_row(online_ref_counts, "reference_online", "Cz")
```

* Linked mastoids: **`r online_ref_lm$percentage`%** (**`r online_ref_lm$n`** / **`r online_ref_lm$total`**) `r online_ref_lm$level`
* Cz: **`r online_ref_cz$percentage`%** (**`r online_ref_cz$n`** / **`r online_ref_cz$total`**) `r online_ref_cz$level`

### Offline reference

```{r offline-reference}
# Offline reference distribution
offline_ref_counts <- hist_discrete(df_ref, "reference_offline",
                                    modality_filter = "EEG",
                                    allowed = ref_mapping[offline_ref_categories]) %>%
  mutate(percentage = round_custom(percentage))

offline_ref_car <- get_row(offline_ref_counts, "reference_offline", "CAR")
```

* Common average: **`r offline_ref_car$percentage`%** (**`r offline_ref_car$n`** / **`r offline_ref_car$total`**) `r offline_ref_car$level`

### Filter settings

```{r filters}
# Filter statistics
filter_data <- df_pipelines %>%
  filter(!is.na(high_pass) & !is.na(low_pass)) %>%
  distinct(PMID, high_pass, low_pass, .keep_all = TRUE)

# Most common high-pass filter values (studies)
common_highpass <- filter_data %>%
  count(high_pass, sort = TRUE) %>%
  head(3)
```

* Most common high-pass cutoffs: **`r paste(sort(common_highpass$high_pass), collapse = ", ")` Hz**

### Artifact removal

```{r artifacts}
artifact_removal <- get_usage_studies(df_pipelines,
                                      c('clean_noisy_epochs',
                                        'clean_bad_channels')) %>%
  mutate(percentage = round_custom(percentage * 100))

noisy_epochs <- get_row(artifact_removal, "column", "clean_noisy_epochs")
bad_channels <- get_row(artifact_removal, "column", "clean_bad_channels")

df_pipelines$ica_used <- df_pipelines$ICA == 1
ica_used <- get_usage_pipelines(df_pipelines, c('ica_used'), distinct = T) %>%
  mutate(percentage = round_custom(percentage * 100))
```

* Noisy epochs: **`r noisy_epochs$percentage`%** (**`r noisy_epochs$count`** / **`r noisy_epochs$total`**) `r noisy_epochs$level`
* Bad channels: **`r bad_channels$percentage`%** (**`r bad_channels$count`** / **`r bad_channels$total`**) `r bad_channels$level`
* ICA usage: **`r ica_used$percentage`%** (**`r ica_used$count`** / **`r ica_used$total`**) `r ica_used$level`

### Types of rejected ICA components

```{r rejected-components}
# Component rejection types
component_types_df <- rejections_per_component_type(df_pipelines) %>%
  mutate(percentage = round_custom(percentage * 100))

for (i in 1:3) {
  row <- component_types_df[i, ]
  cat(
    paste0(
      '  * ', row$rejected_components, ': ',
      '**', row$percentage, '%**', 
      ' (**', row$count, '** / **', row$total, '**) ', row$level, '\n'
    )
  )
}
```

## 3.4. ECG Acquisition

```{r ecg-as-control}
controls_df <- control_counts(df_pipelines, level = "variable") %>%
  mutate(percentage = round_custom(percentage * 100))
ecg_as_control <- get_row(controls_df, "variable", "ECG")
```

Studies that use ECG as a control variable: **`r ecg_as_control$percentage`%** (**`r ecg_as_control$count`** / **`r ecg_as_control$total`**) `r ecg_as_control$level`

```{r ecg_num_electrodes}
# Map "unknown" to 9 so that it isn't lost during conversion to numeric
df_pipelines <- df_pipelines %>%
  mutate(ecg_num_electrodes = replace(ecg_num_electrodes,
                                      ecg_num_electrodes == "unknown", 9))

ecg_electrodes_df <- hist_continuous(df_pipelines, "ecg_num_electrodes",
                                     binwidth = 1, force.numeric = T) %>%
  mutate(percentage = round_custom(percentage))
two_ecg_electrodes <- get_row(ecg_electrodes_df, "ecg_num_electrodes", 2)
```

Studies that use 2 ECG electrodes: **`r two_ecg_electrodes$percentage`**% (**`r two_ecg_electrodes$count`** / **`r two_ecg_electrodes$total`**) `r two_ecg_electrodes$level`

```{r ecg_num_leads}
leads_df <- hist_discrete(df_pipelines, "ecg_lead") %>%
  mutate(percentage = round_custom(percentage))
ecg_lead_i <- get_row(leads_df, "ecg_lead", "Lead I")
ecg_lead_ii <- get_row(leads_df, "ecg_lead", "Lead II")
ecg_lead_iii <- get_row(leads_df, "ecg_lead", "Lead III")
ecg_lead_nc <- get_row(leads_df, "ecg_lead", "N/C")
```

Number of studies that use different ECG leads:

* Lead II: **`r ecg_lead_ii$percentage`%** (**`r ecg_lead_ii$n`** / **`r ecg_lead_ii$total`** `r ecg_lead_ii$level`)
* Lead I: **`r ecg_lead_i$percentage`%** (**`r ecg_lead_i$n`** / **`r ecg_lead_i$total`** `r ecg_lead_i$level`)
* Lead III: **`r ecg_lead_iii$percentage`%** (**`r ecg_lead_iii$n`** / **`r ecg_lead_iii$total`** `r ecg_lead_iii$level`)
* Unclassified: **`r ecg_lead_nc$percentage`%** (**`r ecg_lead_nc$n`** / **`r ecg_lead_nc$total`** `r ecg_lead_nc$level`)

## 3.5. Dealing with cardiac artifacts

```{r cfa-strategies}
# Papers with any CFA approach
df_controls <- add_control_presence(df_pipelines, level = "variable")

df_pipelines <- df_pipelines %>%
  mutate(
    # Check if study has other CFA removal strategies
    has_other_cfa = (!is.na(other_cfa_removal_strategy) & 
                     other_cfa_removal_strategy != "" & 
                     tolower(str_trim(other_cfa_removal_strategy)) != "unknown"),
    controls_for_ecg = df_controls[["ECG"]],
    has_any_cfa_strategy = (reject_cfa_ics | has_other_cfa | controls_for_ecg)
  )
any_cfa_strategy <- get_usage_studies(df_pipelines, "has_any_cfa_strategy") %>%
  mutate(percentage = round_custom(percentage * 100))

ica_for_cfa <- get_usage_studies(df_pipelines, "reject_cfa_ics") %>%
  mutate(percentage = round_custom(percentage * 100))
```

Studies using any strategy for dealing with CFA: **`r any_cfa_strategy$percentage`%** (**`r any_cfa_strategy$count`** / **`r any_cfa_strategy$total`**) `r any_cfa_strategy$level`

ICA used to remove CFA: **`r ica_for_cfa$percentage`%** (**`r ica_for_cfa$count`** / **`r ica_for_cfa$total`**) `r ica_for_cfa$level`

```{r ica-continuous-or-epochs}
df_used_ica <- df_pipelines %>% filter(ICA == 1)
ica_on_epochs <- get_usage_studies(df_used_ica, c('ica_on_epochs')) %>%
  mutate(percentage = round_custom(percentage * 100))
ica_continuous <- get_usage_studies(df_used_ica, 
                                    c('ica_on_epochs'), negate = T) %>%
  mutate(percentage = round_custom(percentage * 100))
```

### ICA applied to what data?

* Continuous: **`r ica_continuous$percentage`%** (**`r ica_continuous$count`** / **`r ica_continuous$total`**) `r ica_continuous$level`
* Epoched: **`r ica_on_epochs$percentage`%** (**`r ica_on_epochs$count`** / **`r ica_on_epochs$total`**) `r ica_on_epochs$level`

### CFA rejection approach

```{r cfa-rejection-approach}
cfa_rej_approach <- hist_discrete(df_included %>% 
                                    filter(reject_cfa_ics), 
                                  "cfa_rej_approach") %>%
  mutate(percentage = round_custom(percentage))

# Amount of reports = total - amount of unknowns
cfa_rej_approach_known <- get_row(cfa_rej_approach, "cfa_rej_approach", "unknown")
cfa_rej_approach_known$n = cfa_rej_approach_known$total - cfa_rej_approach_known$n
cfa_rej_approach_known$percentage = round_custom(cfa_rej_approach_known$n / 
                                                   cfa_rej_approach_known$total * 100)
```

* Reported CFA approach: **`r cfa_rej_approach_known$percentage`%** (**`r cfa_rej_approach_known$n`** / **`r cfa_rej_approach_known$total`**) `r cfa_rej_approach_known$level`

* Breakdown:

```{r cfa-rejection-approach-results}
for (i in 1:nrow(cfa_rej_approach)) {
  row <- cfa_rej_approach[i, ]
  cat(
    paste0(
      '  * ', row$cfa_rej_approach, ': ',
      '**', row$percentage, '%**', 
      ' (**', row$n, '** / **', row$total, '** ', row$level, ')\n'
    )
  )
}
```

### CFA rejection criteria

```{r cfa-rejection-criteria}
criteria_counts <- cfa_criteria_counts(df_included,
                                       mapping = allowed$cfa_criteria) %>%
  mutate(percentage = round_custom(percentage * 100))

for (i in 1:nrow(criteria_counts)) {
  row <- criteria_counts[i, ]
  cat(
    paste0(
      '  * ', row$cfa_rej_criteria, ': ',
      '**', row$percentage, '%**', 
      ' (**', row$count, '** / **', row$total, '** ', row$level, ')\n'
    )
  )
}
```

### Removal of CFA-related ICs

```{r cfa-related-ics}
# Number of studies that reported the number of rejected ICs
df_pipelines$report_rejected_cfa_ics <- !is.na(df_pipelines$rejected_cardiac_ics)
report_cfa <- get_usage_studies(df_pipelines %>% filter(reject_cfa_ics == 1),
                                c("report_rejected_cfa_ics")) %>%
  mutate(percentage = round_custom(percentage * 100))

# Number of rejected cardiac ICs (studies)
cardiac_ic_stats <- get_summary(df_pipelines %>%
                                  filter(!is.na(rejected_cardiac_ics)),
                                "rejected_cardiac_ics")
```

* Reported the number: **`r report_cfa$percentage`%** (**`r report_cfa$count`** / **`r report_cfa$total`**) `r report_cfa$level`
* Range: **`r cardiac_ic_stats$min`** - **`r cardiac_ic_stats$max`**, median = **`r cardiac_ic_stats$median`**

### Other CFA removal strategies

```{r other-cfa-strategies}
strategy_df <- get_usage_studies(df_pipelines, names(allowed$other_cfa_removal)) %>%
  arrange(-percentage) %>%
  mutate(column = str_replace_all(allowed$other_cfa_removal[column], '\n', ' '),
         percentage = round_custom(percentage * 100))

for (i in 1:nrow(strategy_df)) {
  row <- strategy_df[i, ]
  cat(
    paste0(
      '  * ', row$column, ': ',
      '**', row$percentage, '%**', 
      ' (**', row$count, '** / **', row$total, '** ', row$level, ')\n'
    )
  )
}
```

### Minimal CFA window

```{r minimal-cfa-window}
minimal_cfa_window <- get_usage_studies(df_pipelines, 
                                        c('cfa_use_minimal_artifact_window')) %>%
  mutate(percentage = round_custom(percentage * 100))

```

* Number of studies: **`r minimal_cfa_window$percentage`%** (**`r minimal_cfa_window$count`** / **`r minimal_cfa_window$total`**) `r minimal_cfa_window$level`

### Minimal RR interval

```{r minimal-rr}
minimal_rr <- get_usage_studies(df_pipelines,
                                c('cfa_use_minimal_rr')) %>%
  mutate(percentage = round_custom(percentage * 100))

ibi_stats <- get_summary(df_pipelines, "cfa_minimal_rr")
```

* Number of studies: **`r minimal_rr$percentage`%** (**`r minimal_rr$count`** / **`r minimal_rr$total`**) `r minimal_rr$level`
* Minimum RR range: **`r ibi_stats$min`** - **`r ibi_stats$max`** ms

## 3.6. Epoching and baseline correction

### HER reference event

```{r hep-reference-event}
hep_reference_stats <- hist_discrete(df_pipelines, "reference_category") %>%
  mutate(percentage = round_custom(percentage))

disp_results(hep_reference_stats, column = "reference_category", count = "n")
```

### Baseline correction

```{r baseline-correction}
df_pipelines$baseline_correction_stated <- df_pipelines$baseline_category != "Unknown"
baseline_correction_stated <- get_usage_studies(df_pipelines, 
                                                "baseline_correction_stated") %>%
  mutate(percentage = round_custom(percentage * 100))

baseline_correction_stats <- hist_discrete(df_pipelines %>%
                                             filter(baseline_correction_stated),
                                           "baseline_category") %>%
  mutate(percentage = round_custom(percentage))

baseline_correction_yes <- get_row(baseline_correction_stats, "baseline_category", "Yes")
baseline_correction_no <- get_row(baseline_correction_stats, "baseline_category", "No")
```

* Clearly stated: **`r baseline_correction_stated$percentage`%** (**`r baseline_correction_stated$count`** / **`r baseline_correction_stated$total`**) `r baseline_correction_stated$level`

* Among all reports:

  * Performed: **`r baseline_correction_yes$percentage`%** (**`r baseline_correction_yes$n`** / **`r baseline_correction_yes$total`**) `r baseline_correction_yes$level`
  
  * Did not perform: **`r baseline_correction_no$percentage`%** (**`r baseline_correction_no$n`** / **`r baseline_correction_no$total`**) `r baseline_correction_no$level`

```{r baseline-correction-split-by-event}
# Baseline correction - Studies with R-peak analysis
baseline_rpeak_studies <- df_pipelines %>%
  filter(hep_relative_to == "R-peak") %>%
  group_by(PMID) %>%
  summarise(
    has_yes = any(baseline_defined == "Yes"),
    has_no = any(baseline_defined == "No"),
    .groups = "drop"
  ) %>%
  mutate(
    baseline_category = case_when(
      has_yes & has_no ~ "Both",
      has_yes & !has_no ~ "Yes",
      !has_yes & has_no ~ "No",
      TRUE ~ "Other"
    )
  ) %>%
  filter(baseline_category != "Other")

baseline_rpeak_summary <- baseline_rpeak_studies %>%
  summarise(
    total_studies = hep_reference_stats$n[hep_reference_stats$reference_category == "R-peak"] + 
                    hep_reference_stats$n[hep_reference_stats$reference_category == "Both"],
    studies_with_baseline = sum(baseline_category %in% c("Yes", "Both")),
    percentage_with_baseline = round_custom(studies_with_baseline / total_studies * 100)
  )

# Baseline correction - Studies with T-peak analysis  
baseline_tpeak_studies <- df_pipelines %>%
  filter(hep_relative_to == "T-peak") %>%
  group_by(PMID) %>%
  summarise(
    has_yes = any(baseline_defined == "Yes"),
    has_no = any(baseline_defined == "No"),
    .groups = "drop"
  ) %>%
  mutate(
    baseline_category = case_when(
      has_yes & has_no ~ "Both",
      has_yes & !has_no ~ "Yes",
      !has_yes & has_no ~ "No",
      TRUE ~ "Other"
    )
  ) %>%
  filter(baseline_category != "Other")

baseline_tpeak_summary <- baseline_tpeak_studies %>%
  summarise(
    total_studies = hep_reference_stats$n[hep_reference_stats$reference_category == "T-peak"] + 
                   hep_reference_stats$n[hep_reference_stats$reference_category == "Both"],
    studies_with_baseline = sum(baseline_category %in% c("Yes", "Both")),
    percentage_with_baseline = round_custom(studies_with_baseline / total_studies * 100)
  )
```

* Studies using baseline split by reference event:

  * R-peak: **`r baseline_rpeak_summary$percentage_with_baseline`%** (**`r baseline_rpeak_summary$studies_with_baseline`** / **`r baseline_rpeak_summary$total_studies`**) studies
  
  * T-peak: **`r baseline_tpeak_summary$percentage_with_baseline`%** (**`r baseline_tpeak_summary$studies_with_baseline`** / **`r baseline_tpeak_summary$total_studies`**) studies

### Baseline windows

```{r baseline-windows}
# baseline start / end times
baseline_window_stats <- df_pipelines %>%
  filter(!is.na(baseline_start_ms), !is.na(baseline_end_ms))

# Baseline window ranges by reference type
baseline_rpeak_range <- baseline_window_stats %>%
  filter(hep_relative_to == "R-peak") %>%
  summarise(
    range_start = min(baseline_start_ms),
    range_end = max(baseline_end_ms),
    total_studies = n_distinct(PMID),
    studies_ending_before_qrs = n_distinct(PMID[baseline_end_ms < 0]),
    percentage_ending_before_qrs = round(studies_ending_before_qrs / total_studies * 100, 1)
  )

baseline_tpeak_range <- baseline_window_stats %>%
  filter(hep_relative_to == "T-peak") %>%
  summarise(
    range_start = min(baseline_start_ms),
    range_end = max(baseline_end_ms),
    total_studies = n_distinct(PMID)
  )

# Create baseline data for output sections
rpeak_baseline_data <- list(
  start_min = baseline_rpeak_range$range_start,
  end_max = baseline_rpeak_range$range_end
)

tpeak_baseline_data <- list(
  n_studies = baseline_tpeak_range$total_studies,
  start_min = baseline_tpeak_range$range_start,
  end_max = baseline_tpeak_range$range_end
)

baseline_before_qrs_stats <- list(
  percentage_before_qrs = baseline_rpeak_range$percentage_ending_before_qrs
)
```

 * R-peak: **`r rpeak_baseline_data$start_min`** to **`r rpeak_baseline_data$end_max`** ms around R-peak
 
 * R-peak, end before QRS: **`r baseline_before_qrs_stats$percentage_before_qrs`%** (**`r baseline_rpeak_range$studies_ending_before_qrs`** / **`r baseline_rpeak_range$total_studies`**) studies
 
 * T-peak: **`r tpeak_baseline_data$start_min`** to **`r tpeak_baseline_data$end_max`** ms before T-wave

## 3.7. HER Time Windows

### Values used

```{r her-values}
total_studies <- length(unique(df_pipelines$PMID))
hep_value_studies <- df_pipelines %>%
  filter(value != "none") %>%
  distinct(PMID, value) %>%
  count(value, sort = TRUE) %>%
  mutate(total = total_studies,
         percentage = round_custom(n / total * 100))

# Check if HEP values are at study or pipeline level
hep_value_level <- check_studies_or_pipelines(df_pipelines, "value")
```

* `r hep_value_studies$value[1]`: **`r hep_value_studies$n[1]`** / **`r total_studies`** studies (**`r hep_value_studies$percentage[1]`%**)

* `r hep_value_studies$value[2]`: **`r hep_value_studies$n[2]`** / **`r total_studies`** studies (**`r hep_value_studies$percentage[2]`%**)

* `r hep_value_studies$value[3]`: **`r hep_value_studies$n[3]`** / **`r total_studies`** studies (**`r hep_value_studies$percentage[3]`%**)

### Analyzed time windows

```{r her-analyzed-windows}
hep_window_data <- df_pipelines %>%
  filter(!hep_start %in% c("none", "unknown"),
         !hep_end %in% c("none", "unknown")) %>%
  mutate(
    start_time = as.numeric(hep_start),
    end_time = as.numeric(hep_end)
  ) %>%
  filter(!is.na(start_time), !is.na(end_time)) %>%
  distinct(PMID, hep_start, hep_end, hep_relative_to, .keep_all = TRUE)

tpeak_window_stats <- hep_window_data %>%
  filter(hep_relative_to == "T-peak") %>%
  summarise(
    start_min = min(start_time),
    start_max = max(start_time),
    end_min = min(end_time),
    end_max = max(end_time),
  )

rpeak_window_stats <- hep_window_data %>%
  filter(hep_relative_to == "R-peak") %>%
  summarise(
    start_min = min(start_time),
    start_max = max(start_time),
    end_min = min(end_time),
    end_max = max(end_time)
  )
```

* T-wave: **`r tpeak_window_stats$start_min`** to **`r tpeak_window_stats$end_max`** ms after T-wave

* R-peak: **`r rpeak_window_stats$start_min`** to **`r rpeak_window_stats$end_max`** ms relative to R-peak

### Analysis approach

```{r her-analysis-approach}
approach_stats <- hist_discrete(df_included %>%
                                  filter(determination_category != "None"), 
                                "determination_category") %>%
  mutate(percentage = round_custom(percentage))

disp_results(approach_stats, column = "determination_category", count = "n")
```

### Significant effects

```{r significant-effects}
# Significant effects 
df_signif <- df_pipelines %>% filter(significant_test == 1)

# Create merged start/end/ref columns 
df_signif <- df_signif %>%
  mutate(
    merged_start = if_else(averaging_time == "1", 
                           as.character(hep_start), 
                           as.character(significant_start_ms)),
    merged_end   = if_else(averaging_time == "1", 
                           as.character(hep_end), 
                           as.character(significant_end_ms)),
    merged_ref   = if_else(averaging_time == "1", 
                           hep_relative_to, 
                           significant_relative_to)
  )

significant_effects_data <- df_signif %>%
  filter(merged_ref %in% c("R-peak", "T-peak"), significant_test == 1) %>%
  mutate(
    hep_start = as.numeric(hep_start),
    hep_end   = as.numeric(hep_end),
    significant_start_ms = as.numeric(significant_start_ms),
    significant_end_ms   = as.numeric(significant_end_ms),
    start_time = if_else(averaging_time == "1", hep_start, significant_start_ms),
    end_time   = if_else(averaging_time == "1", hep_end, significant_end_ms),
    reference = merged_ref
  ) %>%
  filter(!is.na(start_time), !is.na(end_time))

# Overall significant effects ranges
sig_rpeak_range <- significant_effects_data %>%
  filter(reference == "R-peak") %>%
  summarise(
    start_min = min(start_time),
    start_max = max(start_time),
    end_min = min(end_time),
    end_max = max(end_time)
  )

sig_tpeak_range <- significant_effects_data %>%
  filter(reference == "T-peak") %>%
  summarise(
    start_min = min(start_time),
    start_max = max(start_time),
    end_min = min(end_time),
    end_max = max(end_time)
  )
```

* R-peak: **`r sig_rpeak_range$start_min`** to **`r sig_rpeak_range$end_max`** ms

* T-wave: **`r sig_tpeak_range$start_min`** to **`r sig_tpeak_range$end_max`** ms

### Comparison of effect latencies

```{r effect-latency-comparison}
# R-peak analysis
clustering_rpeak <- significant_effects_data %>%
  filter(method_category == "Clustering", 
         reference == "R-peak") %>%
  filter(!is.na(start_time), !is.na(end_time))

averaging_rpeak <- significant_effects_data %>%
  filter(method_category == "Averaging", 
         reference == "R-peak") %>%
  filter(!is.na(start_time), !is.na(end_time))

# T-peak analysis
clustering_tpeak <- significant_effects_data %>%
  filter(method_category == "Clustering", 
         reference == "T-peak") %>%
  filter(!is.na(start_time), !is.na(end_time))

averaging_tpeak <- significant_effects_data %>%
  filter(method_category == "Averaging", 
         reference == "T-peak") %>%
  filter(!is.na(start_time), !is.na(end_time))

# Perform the statistical comparisons
stat_comparison_results <- list()
stat_comparison_results$rpeak <- perform_peak_timing_comparison(
  clustering_rpeak, averaging_rpeak,
  n_permutations = params$peak_stats_permutations
)
stat_comparison_results$tpeak <- perform_peak_timing_comparison(
  clustering_tpeak, averaging_tpeak, 
  n_permutations = params$peak_stats_permutations
)
```

#### R-peak Analysis

* **Peak Distribution Analysis** (from cumulative plots):
  - Clustering peak: **`r sprintf("%.0f", stat_comparison_results$rpeak$peak1)`** ms
  - Averaging peak: **`r sprintf("%.0f", stat_comparison_results$rpeak$peak2)`** ms
  - Peak difference: `r sprintf("%.0f", abs(stat_comparison_results$rpeak$peak1 - stat_comparison_results$rpeak$peak2))` ms

* **Statistical Test** (Permutation test on peak positions):
  - Sample sizes: n₁ = `r stat_comparison_results$rpeak$n1`, n₂ = `r stat_comparison_results$rpeak$n2`
  - Permutation test: p **`r ifelse(stat_comparison_results$rpeak$permutation_p_value < 0.001, "< 0.001", paste("=", sprintf("%.3f", stat_comparison_results$rpeak$permutation_p_value)))`** (**`r stat_comparison_results$rpeak$n_permutations`** permutations)

#### T-wave Analysis

* **Peak Distribution Analysis** (from cumulative plots):
  - Clustering peak: **`r sprintf("%.0f", stat_comparison_results$tpeak$peak1)`** ms
  - Averaging peak: **`r sprintf("%.0f", stat_comparison_results$tpeak$peak2)`** ms
  - Peak difference: `r sprintf("%.0f", abs(stat_comparison_results$tpeak$peak1 - stat_comparison_results$tpeak$peak2))` ms

* **Statistical Test** (Permutation test on peak positions):
  - Sample sizes: n₁ = `r stat_comparison_results$tpeak$n1`, n₂ = `r stat_comparison_results$tpeak$n2`
  - Permutation test: p **`r ifelse(stat_comparison_results$tpeak$permutation_p_value < 0.001, "< 0.001", paste("=", sprintf("%.3f", stat_comparison_results$tpeak$permutation_p_value)))`** (**`r stat_comparison_results$tpeak$n_permutations`** permutations)

### Analysis Window Definition

```{r her-window-type}
window_type_stats <- hist_discrete(df_included, "window_type_category") %>%
  mutate(percentage = round_custom(percentage))

window_type_primary <- get_row(window_type_stats, "window_type_category", "Primary")
window_type_both <- get_row(window_type_stats, "window_type_category", "Both")
```

* Primary (a-priori defined) analysis windows: **`r window_type_primary$percentage`%** (**`r window_type_primary$n`** / **`r window_type_primary$total`** `r window_type_primary$level`)
* Studies using two-step procedures (data-dependent window selection): **`r window_type_both$percentage`%** (**`r window_type_both$n`** / **`r window_type_both$total`** `r window_type_both$level`)

## 3.8. Statistical analysis and power considerations

### Parameters - power estimation

* Power threshold: **`r params$hedges_power_level * 100`%**
* Significance level: **`r params$hedges_sig_level * 100`%**

### Overview

Overview of numbers presented in Fig. 7:

```{r participants-groups-conditions}
participants_summary <- get_summary(df_pipelines,
                                    "sample_size")
groups_summary <- get_summary(df_pipelines,
                              "groups")
conditions_summary <- get_summary(df_pipelines,
                                  "conditions")
```

* Number of participants: **`r participants_summary$min`** - **`r participants_summary$max`**, median = **`r participants_summary$median`**

* Number of groups: **`r groups_summary$min`** - **`r groups_summary$max`**, median = `r groups_summary$median`

* Number of conditions: **`r conditions_summary$min`** - **`r conditions_summary$max`**, median = `r conditions_summary$median`

```{r hypothesis}
hypothesis_df <- hist_discrete(df_pipelines,
                               "hypothesis",
                               group_col = NULL) %>%
  mutate(percentage = round_custom(percentage))
hypothesis_diff <- get_row(hypothesis_df,
                           "hypothesis",
                           "Group/Condition Differences")
hypothesis_corr <- get_row(hypothesis_df,
                           "hypothesis",
                           "Correlation")
```

* Percentage of pipelines with group or condition analysis: **`r hypothesis_diff$percentage`%** (**`r hypothesis_diff$n`** / **`r hypothesis_diff$total`**)

* Percentage of pipelines with correlation analysis: **`r hypothesis_corr$percentage`%** (**`r hypothesis_corr$n`** / **`r hypothesis_corr$total`**)

```{r trials-summary}
missing_trials_original <- get_row(missing_df, "Column", "trials_original")

trials_summary <- get_summary(df_pipelines,
                              "trials_Mean")
```

* Percentage of missing HEP epoch info: **`r missing_trials_original$percentage`%** (**`r missing_trials_original$count`** / **`r missing_trials_original$total`** studies)

* Number of trials per pipeline: **`r trials_summary$min`**-**`r trials_summary$max`**, median = **`r trials_summary$median`**

```{r stats}
statistics_df <- hist_discrete(df_pipelines, "statistics",
                               allowed = allowed$statistics) %>%
  mutate(percentage = round_custom(percentage)) %>%
  arrange(-percentage)
```

* Most common statistical tests (top 3):

```{r statistics-results, results='asis'}
for (i in 1:3) {
  row <- statistics_df[i, ]
  cat(
    paste0(
      '  * ', row$statistics, ': ',
      '**', row$percentage, '%**', 
      ' (**', row$n, '** / **', row$total, '** ', row$level, ')\n'
    )
  )
}
```

### Power analysis

```{r effect-size}
# Calculate minimum detectable effect sizes (Hedges' g) for each pipeline
hedges_column <- compute_effect_columns(df_pipelines, 
                                        test_type_col = statistics, 
                                        sample_size_col = sample_size, 
                                        groups_col = groups, 
                                        conditions_col = conditions)

# Combine with original data
hedges_df <- bind_cols(df_pipelines, hedges_column) %>%
               filter(clustering == 0,
                      statistics != "Regression") %>%
               distinct(PMID, hedges_g, .keep_all = TRUE) %>%
               drop_na(hedges_g)

hedges_summary <- get_summary(hedges_df, "hedges_g",
                              digits_min = 2, digits_max = 2, digits_median = 2)
```

Power analysis:

* Estimated minimal detectable effect sizes: **`r hedges_summary$min`**-**`r hedges_summary$max`**, median = **`r hedges_summary$median`**

```{r detect-coll}
detect_effect <- function(df, effect_size, name) {
  multiple_rows_per_paper <- any(table(df$PMID) > 1)
  level <- if (multiple_rows_per_paper) "pipelines" else "studies"
  
  df %>%
    summarise(
      name = name,
      effect_size = effect_size,
      total = n(),
      count = sum(hedges_g <= effect_size, na.rm = TRUE),
      percentage = round_custom(count / total * 100),
      level = level
    )
}

detecting_df <- map2_dfr(effect_sizes_Coll2020$value, 
                         effect_sizes_Coll2020$kind,
                         detect_effect, df = hedges_df) %>%
  arrange(percentage)
detecting_df$missing <- detecting_df$total - detecting_df$count
detecting_df$missing_percent <- round_custom(100 - detecting_df$percentage)

# First row has the worst power, last row - the best
underpowered_min <- detecting_df[nrow(detecting_df), ]
underpowered_max <- detecting_df[1, ]
```

* Percent of pipelines detecting effects from Coll et al. (2021):

```{r detect-coll-results, results='asis'}
for (i in 1:nrow(detecting_df)) {
  row <- detecting_df[i, ]
  cat(
    paste0(
      '  * ', row$name, 
      ' (**', row$effect_size, '**): ',
      '**', row$percentage, '%**', 
      ' (**', row$count, '** / **', row$total, '** ', row$level, ')\n'
    )
  )
}
```

* Underpowered and potentially unreliable findings: **`r underpowered_min$missing_percent`%** (**`r underpowered_min$missing`** / **`r underpowered_min$total`**) to **`r underpowered_max$missing_percent`%** (**`r underpowered_max$missing`** / **`r underpowered_max$total`**) of pipelines.

```{r preregistation}
prereg_df <- hist_discrete(df_pipelines, "Preregistration") %>%
  mutate(percentage = round_custom(percentage))
have_prereg <- get_row(prereg_df, "Preregistration", 1)

non_sig_results <- df_pipelines %>%
  group_by(PMID) %>%
  filter(all(significant_test == 0, na.rm = TRUE)) %>%
  distinct(PMID, .keep_all = TRUE) %>%
  ungroup()
non_sig_count <- nrow(non_sig_results)
non_sig_percent <- round_custom(non_sig_count / total_studies * 100)
```

### Preregistrations & publication bias

Preregistrations & publication bias:

* Percentage of pipelines with preregistration: **`r have_prereg$percentage`%** (**`r have_prereg$n`** / **`r have_prereg$total`** **`r have_prereg$level`**) 

* Number and percentage of studies without significant results: **`r non_sig_percent`%** (**`r non_sig_count`** / **`r total_studies`** studies)

## 3.9. Control Analyses

### Categories

```{r control-categories}
category_df <- control_counts(df_pipelines,
                              by = "study",
                              level = "category") %>%
  mutate(percentage = round_custom(100 * percentage)) %>%
  arrange(-percentage)
```

Control categories:

```{r control-categories-results, results='asis'}
for (i in 1:nrow(category_df)) {
  row <- category_df[i, ]
  cat(
    paste0(
      '  * ', row$category, ': ',
      '**', row$percentage, '%**', 
      ' (**', row$count, '** / **', row$total, '** ', row$level, ')\n'
    )
  )
}
```

### Variables

```{r control-variables}
ecg_controls_df <- control_counts(df_pipelines,
                                  by = "study",
                                  level = "variable") %>%
  filter(category == "ECG and Heartbeat-Related Controls") %>%
  mutate(percentage = round_custom(100 * percentage)) %>%
  arrange(-percentage)
```

ECG- and heartbeat-related control variables:

```{r control-variables-results, results='asis'}
for (i in 1:nrow(ecg_controls_df)) {
  row <- ecg_controls_df[i, ]
  cat(
    paste0(
      '  * ', row$variable, ': ',
      '**', row$percentage, '%**', 
      ' (**', row$count, '** / **', row$total, '** ', row$level, ')\n'
    )
  )
}
```

# Supplementary

## A. Estimation of minimal detectable Hedges’ g across reviewed pipelines

```{r hedges-detect-full}
# Combine with original data, this time keep clustering and regression
# See power analysis in Section 3.8 for Hedges' g calculation
hedges_df_full <- bind_cols(df_pipelines, hedges_column) %>%
                    distinct(PMID, hedges_g, .keep_all = TRUE) %>%
                    drop_na(hedges_g)

detecting_df_full <- map2_dfr(effect_sizes_Coll2020$value, 
                              effect_sizes_Coll2020$kind,
                              detect_effect, df = hedges_df_full) %>%  
  arrange(percentage)
```

```{r detect-coll-results-full, results='asis'}
for (i in 1:nrow(detecting_df_full)) {
  row <- detecting_df_full[i, ]
  cat(
    paste0(
      '  * ', row$name, 
      ' (**', row$effect_size, '**): ',
      '**', row$percentage, '%**', 
      ' (**', row$count, '** / **', row$total, '** ', row$level, ')\n'
    )
  )
}
```