---
title: "Manuscript Statistics Summary"
subtitle: "A Systematic Review of Methods Used for Studying Heartbeat Evoked Responses"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    theme: flatly
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

# libraries
library(dplyr)
library(ggplot2)
library(kableExtra)
library(stringr)
library(scales)
library(tidyr)

# Load preprocessed data (created by main.R)
load("data/preprocessed_data.RData")

# Create study-level and pipeline-level datasets for efficiency
df_studies <- df_included %>% distinct(PMID, .keep_all = TRUE)
df_pipelines <- df_included

# EEG-only datasets
eeg_studies <- df_studies %>% filter(modality == "EEG")
eeg_pipelines <- df_pipelines %>% filter(modality == "EEG")
```

# Overview

This document provides all values mentioned in the manuscript "A Systematic Review of Methods Used for Studying Heartbeat Evoked Responses".

## Important Distinction: Studies vs Pipelines

- **Studies**: Unique publications (identified by PMID). Each study represents one research paper.
- **Pipelines**: Individual analysis approaches within studies. Some studies report multiple analysis pipelines (e.g. different time windows, or statistical approaches).

# Literature Search & Screening Results

```{r literature-overview}
# Basic counts
total_retrieved <- nrow(df_screening)
total_pipelines <- nrow(df_pipelines)
total_studies <- nrow(df_studies)

# Year range (based on unique studies)
year_range <- df_studies %>% 
  summarise(min_year = min(Year, na.rm = TRUE), max_year = max(Year, na.rm = TRUE))

# Modality breakdown (pipelines)
modality_counts_pipelines <- df_pipelines %>%
  count(modality) %>%
  mutate(percentage = round(n / sum(n) * 100, 1))

# Modality breakdown (unique studies)
modality_counts_studies <- df_studies %>%
  count(modality) %>%
  mutate(percentage = round(n / sum(n) * 100, 1))

# Task vs resting state - using rsHEP column (pipelines level)
task_counts_pipelines <- df_pipelines %>%
  filter(!is.na(rsHEP)) %>%
  mutate(
    study_type = case_when(
      rsHEP == 1 ~ "Resting state",
      rsHEP == 0 ~ "Task-based",
      TRUE ~ "Unknown"
    )
  ) %>%
  count(study_type) %>%
  mutate(percentage = round(n / sum(n) * 100, 1))

# Task vs resting state - studies that have both vs only one type
study_type_analysis <- df_pipelines %>%
  filter(!is.na(rsHEP)) %>%
  group_by(PMID) %>%
  summarise(
    has_resting = any(rsHEP == 1),
    has_task = any(rsHEP == 0),
    .groups = "drop"
  ) %>%
  mutate(
    study_category = case_when(
      has_resting & has_task ~ "Both resting and task",
      has_resting & !has_task ~ "Resting-state only", 
      !has_resting & has_task ~ "Task-based only",
      TRUE ~ "Other"
    )
  ) %>%
  count(study_category) %>%
  mutate(percentage = round(n / sum(n) * 100, 1))

cat("## Literature Search Results\n")
cat("- **Total retrieved records**: ", total_retrieved, "\n")
cat("- **Total included pipelines**: ", total_pipelines, " from ", total_studies, " unique studies\n")
cat("- **Publication year range**: ", year_range$min_year, "-", year_range$max_year, "\n\n")

cat("## Modality Distribution (Pipelines)\n")
for(i in 1:nrow(modality_counts_pipelines)) {
  cat("- **", modality_counts_pipelines$modality[i], "**: ", modality_counts_pipelines$n[i], " (", modality_counts_pipelines$percentage[i], "%)\n")
}

cat("\n## Modality Distribution (Unique Studies)\n")
for(i in 1:nrow(modality_counts_studies)) {
  cat("- **", modality_counts_studies$modality[i], "**: ", modality_counts_studies$n[i], " (", modality_counts_studies$percentage[i], "%)\n")
}

cat("\n## Study Type Distribution (Pipeline Level)\n")
for(i in 1:nrow(task_counts_pipelines)) {
  cat("- **", task_counts_pipelines$study_type[i], "**: ", task_counts_pipelines$n[i], " (", task_counts_pipelines$percentage[i], "%)\n")
}

cat("\n## Study Type Distribution (Study Level)\n")
for(i in 1:nrow(study_type_analysis)) {
  cat("- **", study_type_analysis$study_category[i], "**: ", study_type_analysis$n[i], " (", study_type_analysis$percentage[i], "%)\n")
}
```

# M/EEG Acquisition & Preprocessing

## Channel Information

```{r channels}
# EEG channel statistics following hist_panel methodology from figures.R

# Get unique (group_col, col) combinations to match hist_panel approach
channel_data <- eeg_studies %>%
  filter(!is.na(meeg_num_electrodes) & meeg_num_electrodes != "unknown") %>%
  distinct(PMID, meeg_num_electrodes) %>%
  mutate(channels_numeric = as.numeric(meeg_num_electrodes)) %>%
  filter(!is.na(channels_numeric))

channel_stats <- channel_data %>%
  summarise(
    min_channels = min(channels_numeric, na.rm = TRUE),
    max_channels = max(channels_numeric, na.rm = TRUE),
    median_channels = median(channels_numeric, na.rm = TRUE),
    n_studies = n()
  )

cat("## EEG Channel Statistics\n")
cat("- **Number of EEG studies with channel data**: ", channel_stats$n_studies, "\n")
cat("- **Channel range**: ", channel_stats$min_channels, "-", channel_stats$max_channels, "\n")
cat("- **Median channels**: ", channel_stats$median_channels, "\n")
```

## Reference Schemes

```{r references}
# Reference processing following eeg_acq_prep() methodology from figures.R

# Define major reference categories (from figures.R)
major_categories <- tolower(c(
  "Cz", "Nose", "Linked earlobes", "Linked mastoids",
  "FCz", "Common average", "Fpz", "CMS", "CMS and DRL",
  "unknown", "Laplacian reference", "REST"
))

# Process reference categories following eeg_acq_prep methodology
eeg_studies_ref <- eeg_studies %>%
  mutate(across(
    .cols = c(reference_online, reference_offline),
    .fns = ~ case_when(
      tolower(.) %in% major_categories ~ tolower(.),
      TRUE ~ "Other"
    )
  ))

# Common reference category mapping (from figures.R)
ref_categories <- c(
  "common average" = "CAR",
  "linked mastoids" = "LM", 
  "linked earlobes" = "LE",
  "cz" = "Cz",
  "fcz" = "FCz",
  "fpz" = "Fpz",
  "cms" = "CMS",
  "cms and drl" = "CMS",
  "nose" = "Nose",
  "laplacian reference" = "LAP",
  "rest" = "REST",
  "other" = "Other",
  "unknown" = "N/M"
)

# Online reference distribution (studies) - following hist_panel methodology
online_ref_counts <- eeg_studies_ref %>%
  filter(!is.na(reference_online)) %>%
  count(reference_online) %>%
  filter(reference_online %in% names(ref_categories)) %>%
  mutate(
    display_name = ref_categories[reference_online],
    percentage = round(n / sum(n) * 100, 1)
  ) %>%
  arrange(desc(n))

# Offline reference distribution (studies) - following hist_panel methodology
offline_ref_counts <- eeg_studies_ref %>%
  filter(!is.na(reference_offline)) %>%
  count(reference_offline) %>%
  filter(reference_offline %in% names(ref_categories)) %>%
  mutate(
    display_name = ref_categories[reference_offline],
    percentage = round(n / sum(n) * 100, 1)
  ) %>%
  arrange(desc(n))

cat("## Online Reference Distribution\n")
for(i in 1:min(5, nrow(online_ref_counts))) {
  cat("- **", online_ref_counts$display_name[i], "**: ", online_ref_counts$percentage[i], "%\n")
}

cat("\n## Offline Reference Distribution\n")
for(i in 1:min(5, nrow(offline_ref_counts))) {
  cat("- **", offline_ref_counts$display_name[i], "**: ", offline_ref_counts$percentage[i], "%\n")
}

# Most common offline reference
most_common_offline <- offline_ref_counts$display_name[1]
cat("\n**Most dominant offline reference choice**: ", most_common_offline, "\n")
```

## Artifact Removal

```{r artifacts}
# Artifact removal statistics (pipelines)
artifact_stats <- df_pipelines %>%
  summarise(
    # Noisy epochs removal (look in other_cleaning_strategy)
    noisy_epochs_pct = round(mean(grepl("noisy epoch|epoch", other_cleaning_strategy, ignore.case = TRUE) %in% TRUE, na.rm = TRUE) * 100, 0),
    
    # Bad channels removal (look in other_cleaning_strategy)  
    bad_channels_pct = round(mean(grepl("bad channels", other_cleaning_strategy, ignore.case = TRUE) %in% TRUE, na.rm = TRUE) * 100, 0),
    
    # Blink/EOG correction (look in other_cleaning_strategy)
    blink_correction_pct = round(mean(grepl("blink|EOG|eye|gratton", other_cleaning_strategy, ignore.case = TRUE) %in% TRUE, na.rm = TRUE) * 100, 0),

    # ICA usage
    ica_pct = round(mean(ICA == 1, na.rm = TRUE) * 100, 1),
    
    # Studies with ICA
    n_ica_pipelines = sum(ICA == 1, na.rm = TRUE),
    total_pipelines = n() 
  )

# Studies using ICA (unique studies)
ica_studies <- df_pipelines %>%
  group_by(PMID) %>%
  summarise(uses_ica = any(ICA == 1, na.rm = TRUE)) %>%
  summarise(
    n_ica_studies = sum(uses_ica),
    total_studies = n(),
    ica_study_pct = round(mean(uses_ica) * 100, 1)
  )

# Component rejection types (studies with ICA, following create_ica_rej.R methodology)
component_types <- df_pipelines %>%
  filter(ICA == 1) %>%
  distinct(PMID, rejected_components) %>%
  filter(rejected_components != "", rejected_components != "unknown") %>%
  mutate(pipeline_id = row_number()) %>%
  # Clean rejected_components: replace newlines with a comma, collapse multiple commas
  mutate(rejected_components = sapply(rejected_components, function(x) {
    x <- gsub("[\r\n]+", ",", x)    
    x <- gsub(",+", ",", x)         
    x <- gsub("^,|,$", "", x)       
    comps <- unlist(strsplit(x, ","))
    comps <- unique(trimws(comps))
    comps <- comps[comps != ""]
    paste(comps, collapse = ",")
  })) %>%
  separate_rows(rejected_components, sep = ",") %>%
  mutate(
    rejected_components = trimws(rejected_components),
    rejected_components = tolower(rejected_components)
  ) %>%
  # Apply component mapping from create_ica_rej.R
  mutate(rejected_components = case_when(
    rejected_components == "eye movements" ~ "Ocular",
    rejected_components == "blinks" ~ "Ocular", 
    rejected_components == "muscle" ~ "Muscle",
    rejected_components == "cfa" ~ "CFA",
    rejected_components == "channel noise" ~ "Channel noise",
    rejected_components == "line noise" ~ "Line noise",
    rejected_components == "other" ~ "Other",
    TRUE ~ rejected_components
  )) %>%
  filter(rejected_components != "") %>%
  group_by(rejected_components) %>%
  summarise(count = n_distinct(pipeline_id), .groups = "drop") %>%
  arrange(desc(count)) %>%
  mutate(
    total_ica_studies = length(unique(df_pipelines$PMID[df_pipelines$ICA == 1 & 
                                                        df_pipelines$rejected_components != "" & 
                                                        df_pipelines$rejected_components != "unknown"])),
    percentage = round(count / total_ica_studies * 100, 1)
  )

cat("## Artifact Removal Statistics\n")
cat("- **Pipelines removing noisy epochs**: ", artifact_stats$noisy_epochs_pct, "%\n")
cat("- **Pipelines removing bad channels**: ", artifact_stats$bad_channels_pct, "%\n")
cat("- **Pipelines using blink correction**: ", artifact_stats$blink_correction_pct, "%\n")
cat("- **Pipelines using eye movement correction**: ", artifact_stats$eye_movement_pct, "%\n")
cat("- **Pipelines using ICA**: ", artifact_stats$ica_pct, "% (", artifact_stats$n_ica_pipelines, "/", artifact_stats$total_pipelines, ")\n")
cat("- **Studies using ICA**: ", ica_studies$ica_study_pct, "% (", ica_studies$n_ica_studies, "/", ica_studies$total_studies, ")\n")

cat("\n## ICA Component Types Removed\n")
for(i in 1:min(nrow(component_types))) {
  cat("- **", component_types$rejected_components[i], "**: ", component_types$percentage[i], "%\n")
}
```

## Filter Settings

```{r filters}
# Filter statistics following create_combined_plot methodology from figures.R

# Following create_filter_plots approach from figures.R - filters studies with valid filter data
filter_data <- df_pipelines %>%
  filter(!is.na(high_pass) & !is.na(low_pass)) %>%
  distinct(PMID, high_pass, low_pass, .keep_all = TRUE) %>%
  # Apply positive value filter (as used in create_combined_plot for log scale)
  filter(high_pass > 0 & low_pass > 0)

filter_stats <- filter_data %>%
  summarise(
    n_valid = n(),
    high_pass_range_min = min(high_pass, na.rm = TRUE),
    high_pass_range_max = max(high_pass, na.rm = TRUE),
    low_pass_range_min = min(low_pass, na.rm = TRUE), 
    low_pass_range_max = max(low_pass, na.rm = TRUE)
  )

# Most common high-pass filter values (studies) - following distinct methodology
common_highpass <- filter_data %>%
  count(high_pass, sort = TRUE) %>%
  head(3)

cat("## Filter Settings\n")
cat("- **Pipelines with complete filter data**: ", filter_stats$n_valid, "\n")
cat("- **High-pass filter range**: ", filter_stats$high_pass_range_min, "-", filter_stats$high_pass_range_max, " Hz\n")
cat("- **Low-pass filter range**: ", filter_stats$low_pass_range_min, "-", filter_stats$low_pass_range_max, " Hz\n")
cat("- **Most common high-pass cutoffs**: ", paste(common_highpass$high_pass, collapse = ", "), " Hz\n")
```

# ECG Acquisition

```{r ecg}
# ECG acquisition statistics following ecg_summary() methodology from figures.R

# Map "unknown" to 9 for consistent processing (following ecg_summary methodology)
ecg_data <- df_pipelines %>%
  mutate(ecg_num_electrodes = replace(ecg_num_electrodes,
                                      ecg_num_electrodes == "unknown", 9))

# ECG electrode statistics (studies)
ecg_electrode_stats <- ecg_data %>%
  distinct(PMID, ecg_num_electrodes) %>%
  filter(!is.na(ecg_num_electrodes)) %>%
  mutate(ecg_num_electrodes_numeric = as.numeric(ecg_num_electrodes)) %>%
  filter(!is.na(ecg_num_electrodes_numeric)) %>%
  summarise(
    n_studies = n(),
    min_electrodes = min(ecg_num_electrodes_numeric, na.rm = TRUE),
    max_electrodes = max(ecg_num_electrodes_numeric, na.rm = TRUE),
    median_electrodes = median(ecg_num_electrodes_numeric, na.rm = TRUE)
  )

# ECG lead distribution (studies) - following hist_panel with distinct methodology
ecg_lead_counts <- df_pipelines %>%
  distinct(PMID, ecg_lead) %>%
  filter(!is.na(ecg_lead) & ecg_lead != "unknown") %>%
  count(ecg_lead, sort = TRUE) %>%
  mutate(percentage = round(n / sum(n) * 100, 1))

# ECG locations analysis (studies) - following plot_ecg_locations methodology
ecg_location_data <- df_pipelines %>%
  distinct(PMID, ecg_lead, ecg_locations) %>%
  filter(
    ecg_lead %in% c("Lead I", "Lead II", "Lead III"), 
    ecg_locations != "unknown",
    !is.na(ecg_locations)
  )

cat("## ECG Electrode Statistics\n")
cat("- **Studies with ECG electrode data**: ", ecg_electrode_stats$n_studies, "\n")
cat("- **ECG electrode range**: ", ecg_electrode_stats$min_electrodes, "-", ecg_electrode_stats$max_electrodes, "\n")
cat("- **Median ECG electrodes**: ", ecg_electrode_stats$median_electrodes, "\n")

cat("\n## ECG Lead Distribution\n")
for(i in 1:min(5, nrow(ecg_lead_counts))) {
  cat("- **", ecg_lead_counts$ecg_lead[i], "**: ", ecg_lead_counts$percentage[i], "%\n")
}

cat("\n## ECG Location Information\n")
cat("- **Studies with standard lead location data**: ", nrow(ecg_location_data), "\n")
```

# CFA Removal Strategies

```{r cfa}
# ICA timing (studies using ICA) - following epoch_continuous_ica.R methodology
ica_timing <- df_studies %>%
  filter(ICA == 1 & !is.na(ica_on_epochs)) %>%
  count(ica_on_epochs) %>%
  mutate(
    timing = case_when(
      ica_on_epochs == 0 ~ "Continuous",
      ica_on_epochs == 1 ~ "Epoched",
      TRUE ~ "Unknown"
    ),
    percentage = round(n / sum(n) * 100, 1)
  )

# CFA identification approaches (studies)
cfa_approach_counts <- df_studies %>%
  filter(!is.na(cfa_rej_approach) & 
         cfa_rej_approach != "" & 
         tolower(str_trim(cfa_rej_approach)) != "unknown") %>%
  mutate(cfa_rej_approach_clean = str_to_title(tolower(str_trim(cfa_rej_approach)))) %>%
  count(cfa_rej_approach_clean, sort = TRUE) %>%
  mutate(percentage = round(n / sum(n) * 100, 1)) %>%
  rename(cfa_rej_approach = cfa_rej_approach_clean)

# CFA identification criteria (studies) - following summarize_cfa_criteria.R methodology
cfa_criteria_counts <- df_studies %>%
  mutate(cfa_rej_criteria = tolower(cfa_rej_criteria)) %>%
  filter(!is.na(cfa_rej_criteria), cfa_rej_criteria != "", cfa_rej_criteria != "unknown") %>%
  distinct(PMID, cfa_rej_criteria) %>%
  mutate(pipeline_id = row_number()) %>%
  # Expand and process the criteria
  separate_rows(cfa_rej_criteria, sep = ",") %>%
  mutate(
    cfa_rej_criteria = str_replace_all(cfa_rej_criteria, "[\r\n]", " "),
    cfa_rej_criteria = str_trim(cfa_rej_criteria, side = "both"),
    # Apply category mapping from summarize_cfa_criteria.R
    cfa_rej_criteria = case_when(
      cfa_rej_criteria == "time course" ~ "Time Course",
      cfa_rej_criteria == "topography" ~ "Topography", 
      cfa_rej_criteria == "power spectrum" ~ "Power Spectrum",
      cfa_rej_criteria == "phase consistency" ~ "Phase Consistency",
      cfa_rej_criteria == "iclabel" ~ "Algorithm",
      cfa_rej_criteria == "corrmap" ~ "Algorithm",
      cfa_rej_criteria == "correlation" ~ "Correlation",
      cfa_rej_criteria == "sasica" ~ "Algorithm",
      TRUE ~ str_to_title(cfa_rej_criteria)
    )
  ) %>%
  filter(cfa_rej_criteria != "", cfa_rej_criteria != "unknown") %>%
  distinct(pipeline_id, cfa_rej_criteria, .keep_all = TRUE) %>%
  group_by(cfa_rej_criteria) %>%
  summarise(count = n_distinct(pipeline_id), .groups = "drop") %>%
  arrange(desc(count)) %>%
  mutate(
    total_pipelines = length(unique(df_studies$PMID[!is.na(df_studies$cfa_rej_criteria) & 
                                                    df_studies$cfa_rej_criteria != "" & 
                                                    tolower(df_studies$cfa_rej_criteria) != "unknown"])),
    percentage = round(count / total_pipelines * 100, 1)
  )

# Number of rejected cardiac ICs (studies)
cardiac_ic_stats <- df_studies %>%
  filter(!is.na(rejected_cardiac_ics)) %>%
  summarise(
    n_studies = n(),
    min_ics = min(rejected_cardiac_ics, na.rm = TRUE),
    max_ics = max(rejected_cardiac_ics, na.rm = TRUE),
    median_ics = median(rejected_cardiac_ics, na.rm = TRUE)
  )

# Other CFA removal strategies (studies) - using same logic as other_strategy_plot.R
other_cfa_strategies <- df_studies %>%
  filter(!is.na(other_cfa_removal_strategy) & 
         other_cfa_removal_strategy != "" & 
         tolower(str_trim(other_cfa_removal_strategy)) != "unknown") %>%
  mutate(
    # Clean and standardize strategy names (based on other_strategy_plot.R)
    strategy_clean = case_when(
      other_cfa_removal_strategy == "limit analysis to time of minimal artifact" ~ 
        "Minimal artifact window",
      str_detect(tolower(other_cfa_removal_strategy), "^rr at least") ~ 
        "RR interval constraints",
      tolower(other_cfa_removal_strategy) %in% c(
        "correct for cfa using the signal from the tip of the nose",
        "regress ecg out",
        "subtracting the cardiac signal artifact (skin-conducted ekg signal to the scalp) from the eeg signal",
        "scaled ecg subtracted from eeg",
        "subtract average ecg",
        "ecg subtraction",
        "weitkunat, r., & schandry, r. (1995)."
      ) ~ "Subtract/regress ECG from EEG",
      tolower(other_cfa_removal_strategy) == "subtract subject average resting state heps from task heps" ~ 
        "Subtract rsHEP from task HEP",
      str_detect(tolower(other_cfa_removal_strategy), "pca|hep") ~ "PCA on HEP",    
      tolower(other_cfa_removal_strategy) == "hjorth" ~ "CSD",
      tolower(other_cfa_removal_strategy) == "csd" ~ "CSD",
      TRUE ~ str_to_title(str_trim(other_cfa_removal_strategy))
    )
  ) %>%
  count(strategy_clean, sort = TRUE) %>%
  mutate(percentage = round(n / sum(n) * 100, 1)) %>%
  rename(strategy = strategy_clean)

cat("## ICA Application Timing\n")
for(i in 1:nrow(ica_timing)) {
  cat("- **", ica_timing$timing[i], "**: ", ica_timing$percentage[i], "%\n")
}

cat("\n## CFA Identification Approaches\n")
cat("- **Not reported**: ", round((1 - sum(cfa_approach_counts$n) / total_studies) * 100, 1), "% of studies\n")
for(i in 1:min(3, nrow(cfa_approach_counts))) {
  cat("- **", cfa_approach_counts$cfa_rej_approach[i], "**: ", cfa_approach_counts$percentage[i], "%\n")
}

cat("\n## CFA Identification Criteria\n")
for(i in 1:min(nrow(cfa_criteria_counts))) {
  cat("- **", cfa_criteria_counts$cfa_rej_criteria[i], "**: ", cfa_criteria_counts$percentage[i], "%\n")
}

cat("\n## Rejected Cardiac ICs\n")
cat("- **Studies reporting number**: ", cardiac_ic_stats$n_studies, "\n")
cat("- **Range**: ", cardiac_ic_stats$min_ics, "-", cardiac_ic_stats$max_ics, "\n")
cat("- **Median**: ", cardiac_ic_stats$median_ics, "\n")

cat("\n## Other CFA Removal Strategies\n")
for(i in 1:min(nrow(other_cfa_strategies))) {
  cat("- **", other_cfa_strategies$strategy[i], "**: ", other_cfa_strategies$n[i], " studies (", other_cfa_strategies$percentage[i], "%)\n")
}
```

# Missing Information Analysis

```{r missing}
# Key variables for missing analysis (following plot_missing.R methodology)
key_variables <- c(
  "rejected_cardiac_ics", "ecg_ground", "ecg_locations", 
  "baseline_start_ms", "baseline_end_ms", "cfa_rej_approach", 
  "cfa_rej_criteria", "trials", "permutations"
)

# ICA-specific columns (only counted as missing if ICA == 1)
ica_columns <- c(
  "ica_on_epochs", "rejected_components", 
  "rejected_cardiac_ics", "cfa_rej_approach", "cfa_rej_criteria"
)

# Function to check if value is missing (following plot_missing.R)
is_missing <- function(x) {
  x_char <- tolower(as.character(x))
  is.na(x) | x == "" | x_char %in% c("unknown", "na")
}

# Calculate missing percentages with proper conditions
missing_stats <- data.frame(
  variable = key_variables,
  missing_pct = sapply(key_variables, function(var) {
    if(var %in% names(df_pipelines)) {
      missing_values <- is_missing(df_pipelines[[var]])
      
      # For ICA columns: only count missing if ICA == 1
      if (var %in% ica_columns) {
        condition <- df_pipelines$ICA == 1
        relevant_rows <- sum(condition, na.rm = TRUE)
        missing_in_relevant <- sum(missing_values & condition, na.rm = TRUE)
        if (relevant_rows == 0) return(NA)
        return(round(missing_in_relevant / relevant_rows * 100, 0))
      }
      
      # For permutations: only count if clustering == 1
      if (grepl("perm", var, ignore.case = TRUE)) {
        condition <- df_pipelines$clustering == 1
        relevant_rows <- sum(condition, na.rm = TRUE)
        missing_in_relevant <- sum(missing_values & condition, na.rm = TRUE)
        if (relevant_rows == 0) return(NA)
        return(round(missing_in_relevant / relevant_rows * 100, 0))
      }
      
      # For trials: also count as missing if starts with "[est"
      if (tolower(var) == "trials") {
        extra_missing <- grepl("^\\[est", df_pipelines[[var]], ignore.case = TRUE)
        missing_values <- missing_values | extra_missing
      }
      
      # Regular missing calculation
      round(mean(missing_values, na.rm = TRUE) * 100, 0)
    } else {
      NA
    }
  })
)

# Sort by missing percentage
missing_stats <- missing_stats[order(-missing_stats$missing_pct, na.last = TRUE),]

cat("## Missing Information (Top Issues)\n")
for(i in 1:min(8, nrow(missing_stats))) {
  if(!is.na(missing_stats$missing_pct[i])) {
    var_display <- gsub("_", " ", missing_stats$variable[i])
    cat("- **", var_display, "**: ", missing_stats$missing_pct[i], "% missing\n")
  }
}
```

# Publication Timeline

```{r timeline}
# Publication timeline (based on unique studies)
pub_timeline <- df_studies %>%
  count(Year) %>%
  arrange(Year)

# Last 10 years analysis (unique studies)
last_10_years <- df_studies %>%
  filter(Year >= (max(Year, na.rm = TRUE) - 9)) %>%
  nrow()

total_unique_studies <- nrow(df_studies)
last_10_pct <- round(last_10_years / total_unique_studies * 100, 0)

cat("## Publication Timeline\n")
cat("- **Studies published in the last 10 years**: ", last_10_pct, "% (", last_10_years, "/", total_unique_studies, ")\n")
cat("- **Year range**: ", min(pub_timeline$Year, na.rm = TRUE), "-", max(pub_timeline$Year, na.rm = TRUE), "\n")
```

# Sample Sizes and Statistical Power

```{r power}
# Sample size statistics (unique studies)
sample_stats <- df_studies %>%
  filter(!is.na(sample_size) & sample_size > 0) %>%
  summarise(
    n_studies = n(),
    min_n = min(sample_size),
    max_n = max(sample_size),
    median_n = median(sample_size),
    mean_n = round(mean(sample_size), 1)
  )

# Trial/epoch statistics (pipelines)
trial_stats <- df_pipelines %>%
  filter(!is.na(trials) & trials > 0) %>%
  summarise(
    n_pipelines = n(),
    min_trials = min(trials),
    max_trials = max(trials),
    median_trials = median(trials),
    mean_trials = round(mean(trials), 1)
  )

cat("## Sample Size Statistics\n")
cat("- **Studies reporting sample size**: ", sample_stats$n_studies, "\n")
cat("- **Sample size range**: ", sample_stats$min_n, "-", sample_stats$max_n, "\n")
cat("- **Median sample size**: ", sample_stats$median_n, "\n")
cat("- **Mean sample size**: ", sample_stats$mean_n, "\n")

cat("\n## Trial/Epoch Statistics\n")
cat("- **Pipelines reporting trial numbers**: ", trial_stats$n_pipelines, "\n")
cat("- **Trial range**: ", trial_stats$min_trials, "-", trial_stats$max_trials, "\n")
cat("- **Median trials**: ", trial_stats$median_trials, "\n")
```

# Time Windows and Analysis

```{r timewindows}
# HEP time window analysis following create_time_windows_plot.R and create_single_ecg_plot.R methodology

# HEP Time of Interest windows (following create_single_ecg_plot.R methodology)
hep_window_data <- df_pipelines %>%
  filter(!hep_start %in% c("none", "unknown"),
         !hep_end %in% c("none", "unknown")) %>%
  mutate(
    start_time = as.numeric(hep_start),
    end_time = as.numeric(hep_end)
  ) %>%
  filter(!is.na(start_time), !is.na(end_time)) %>%
  distinct(PMID, hep_start, hep_end, hep_relative_to, .keep_all = TRUE)

# Overall HEP window statistics
hep_window_stats <- hep_window_data %>%
  summarise(
    n_pipelines = n(),
    start_range_min = min(start_time),
    start_range_max = max(start_time), 
    end_range_min = min(end_time),
    end_range_max = max(end_time),
    duration_min = min(end_time - start_time),
    duration_max = max(end_time - start_time)
  )

# HEP reference scheme distribution (studies with valid HEP windows)
hep_reference_counts <- hep_window_data %>%
  distinct(PMID, hep_relative_to) %>%
  filter(!is.na(hep_relative_to) & hep_relative_to != "unknown") %>%
  count(hep_relative_to, sort = TRUE) %>%
  mutate(percentage = round(n / sum(n) * 100, 1))

# R-peak specific analysis
rpeak_window_data <- hep_window_data %>%
  filter(hep_relative_to == "R-peak")

rpeak_window_stats <- if(nrow(rpeak_window_data) > 0) {
  rpeak_window_data %>%
    summarise(
      n_pipelines = n(),
      start_range_min = min(start_time),
      start_range_max = max(start_time),
      end_range_min = min(end_time),
      end_range_max = max(end_time),
      duration_min = min(end_time - start_time),
      duration_max = max(end_time - start_time)
    )
} else {
  data.frame(n_pipelines = 0, start_range_min = NA, start_range_max = NA,
             end_range_min = NA, end_range_max = NA, duration_min = NA, duration_max = NA)
}

# Most common R-peak time windows analysis (for averaging studies)
rpeak_common_windows <- if(nrow(rpeak_window_data) > 0) {
  rpeak_window_data %>%
    # Create time window strings for grouping
    mutate(time_window = paste(start_time, "to", end_time, "ms")) %>%
    count(time_window, start_time, end_time, sort = TRUE) %>%
    mutate(
      percentage = round(n / sum(n) * 100, 1),
      n_studies = n  # Since we used distinct(PMID, ...) in hep_window_data
    ) %>%
    head(5)  # Top 5 most common windows
} else {
  data.frame(time_window = character(0), start_time = numeric(0), 
             end_time = numeric(0), n = numeric(0), percentage = numeric(0), n_studies = numeric(0))
}

# Find the overlap region that most studies include
rpeak_overlap_analysis <- if(nrow(rpeak_window_data) > 0) {
  # Find the most common overlapping region
  all_start_times <- rpeak_window_data$start_time
  all_end_times <- rpeak_window_data$end_time
  
  # Use a more inclusive approach: find the region that most studies overlap with
  # Use median start time and median end time as core boundaries
  median_start <- median(all_start_times, na.rm = TRUE)
  median_end <- median(all_end_times, na.rm = TRUE)
  
  # Count how many studies include this core region (overlap with median start to median end)
  studies_including_core <- rpeak_window_data %>%
    filter(start_time <= median_start & end_time >= median_end) %>%
    nrow()
  
  core_percentage <- round(studies_including_core / nrow(rpeak_window_data) * 100, 1)
  
  
  list(
    core_start = round(median_start, 0),
    core_end = round(median_end, 0),
    studies_including_core = studies_including_core,
    total_rpeak_studies = nrow(rpeak_window_data),
    core_percentage = core_percentage
  )
} else {
  list(core_start = NA, core_end = NA, studies_including_core = 0, 
       total_rpeak_studies = 0, core_percentage = 0)
}

# T-peak specific analysis  
tpeak_window_data <- hep_window_data %>%
  filter(hep_relative_to == "T-peak")

tpeak_window_stats <- if(nrow(tpeak_window_data) > 0) {
  tpeak_window_data %>%
    summarise(
      n_pipelines = n(),
      start_range_min = min(start_time),
      start_range_max = max(start_time),
      end_range_min = min(end_time),
      end_range_max = max(end_time),
      duration_min = min(end_time - start_time),
      duration_max = max(end_time - start_time)
    )
} else {
  data.frame(n_pipelines = 0, start_range_min = NA, start_range_max = NA,
             end_range_min = NA, end_range_max = NA, duration_min = NA, duration_max = NA)
}

# Baseline window analysis (following create_single_ecg_plot.R methodology) 
baseline_window_data <- df_pipelines %>%
  filter(!is.na(baseline_start_ms), !is.na(baseline_end_ms)) %>%
  mutate(
    baseline_start_numeric = as.numeric(baseline_start_ms),
    baseline_end_numeric = as.numeric(baseline_end_ms)
  ) %>%
  filter(!is.na(baseline_start_numeric), !is.na(baseline_end_numeric))

baseline_stats <- baseline_window_data %>%
  summarise(
    n_pipelines = n(),
    start_range_min = min(baseline_start_numeric),
    start_range_max = max(baseline_start_numeric),
    end_range_min = min(baseline_end_numeric),
    end_range_max = max(baseline_end_numeric),
    duration_min = min(baseline_end_numeric - baseline_start_numeric),
    duration_max = max(baseline_end_numeric - baseline_start_numeric)
  )

baseline_pct <- round(nrow(baseline_window_data) / nrow(df_pipelines) * 100, 1)

# Baseline correction by reference peak (R-peak vs T-peak)
baseline_by_reference <- df_pipelines %>%
  filter(!is.na(baseline_start_ms), !is.na(baseline_end_ms),
         !is.na(hep_relative_to), hep_relative_to != "unknown") %>%
  mutate(
    baseline_start_numeric = as.numeric(baseline_start_ms),
    baseline_end_numeric = as.numeric(baseline_end_ms)
  ) %>%
  filter(!is.na(baseline_start_numeric), !is.na(baseline_end_numeric)) %>%
  group_by(hep_relative_to) %>%
  summarise(
    n_pipelines = n(),
    n_studies = n_distinct(PMID),
    start_range_min = min(baseline_start_numeric),
    start_range_max = max(baseline_start_numeric),
    end_range_min = min(baseline_end_numeric),
    end_range_max = max(baseline_end_numeric),
    .groups = "drop"
  )

# Analysis of baseline windows ending before QRS complex (to avoid CFA contamination)
baseline_before_qrs <- baseline_window_data %>%
  filter(!is.na(hep_relative_to), hep_relative_to != "unknown") %>%
  mutate(
    # For R-peak reference: baseline ends before 0 ms (QRS complex)
    # For T-peak reference: need to account for typical T-peak timing (~300ms after R-peak)
    baseline_ends_before_qrs = case_when(
      hep_relative_to == "R-peak" ~ baseline_end_numeric < 0,
      hep_relative_to == "T-peak" ~ baseline_end_numeric < 0, 
      TRUE ~ FALSE
    )
  )

# Calculate percentage of studies with baseline ending before QRS
baseline_before_qrs_stats <- baseline_before_qrs %>%
  summarise(
    total_studies_with_baseline = n_distinct(PMID),
    studies_ending_before_qrs = n_distinct(PMID[baseline_ends_before_qrs]),
    percentage_before_qrs = round(studies_ending_before_qrs / total_studies_with_baseline * 100, 1)
  )

# Breakdown by reference scheme
baseline_before_qrs_by_ref <- baseline_before_qrs %>%
  group_by(hep_relative_to) %>%
  summarise(
    total_studies = n_distinct(PMID),
    studies_ending_before_qrs = n_distinct(PMID[baseline_ends_before_qrs]),
    percentage_before_qrs = round(studies_ending_before_qrs / total_studies * 100, 1),
    .groups = "drop"
  )

# Significant effects window analysis (following create_time_windows_plot.R merged methodology)
significant_effects_data <- df_pipelines %>%
  filter(significant_test == 1) %>%
  mutate(
    hep_start_numeric = as.numeric(hep_start),
    hep_end_numeric = as.numeric(hep_end),
    significant_start_numeric = as.numeric(significant_start_ms),
    significant_end_numeric = as.numeric(significant_end_ms),
    # Use HEP windows if averaging_time == 1, otherwise use significant windows
    start_time = if_else(averaging_time == "1", hep_start_numeric, significant_start_numeric),
    end_time = if_else(averaging_time == "1", hep_end_numeric, significant_end_numeric),
    reference = if_else(averaging_time == "1", hep_relative_to, significant_relative_to)
  ) %>%
  filter(!is.na(start_time), !is.na(end_time))

significant_window_stats <- if(nrow(significant_effects_data) > 0) {
  significant_effects_data %>%
    summarise(
      n_pipelines = n(),
      start_range_min = min(start_time),
      start_range_max = max(start_time),
      end_range_min = min(end_time), 
      end_range_max = max(end_time),
      duration_min = min(end_time - start_time),
      duration_max = max(end_time - start_time)
    )
} else {
  data.frame(n_pipelines = 0, start_range_min = NA, start_range_max = NA,
             end_range_min = NA, end_range_max = NA, duration_min = NA, duration_max = NA)
}

cat("## HEP Time Windows\n")
cat("- **Pipelines with valid HEP windows**: ", hep_window_stats$n_pipelines, "\n")
cat("- **Overall HEP start time range**: ", hep_window_stats$start_range_min, " to ", hep_window_stats$start_range_max, " ms\n")
cat("- **Overall HEP end time range**: ", hep_window_stats$end_range_min, " to ", hep_window_stats$end_range_max, " ms\n")
cat("- **Overall HEP window duration range**: ", hep_window_stats$duration_min, " to ", hep_window_stats$duration_max, " ms\n")

cat("\n## HEP Reference Peak Distribution\n")
for(i in 1:min(nrow(hep_reference_counts), 5)) {
  cat("- **", as.character(hep_reference_counts$hep_relative_to[i]), "**: ", hep_reference_counts$n[i], " studies (", hep_reference_counts$percentage[i], "%)\n")
}

cat("\n## R-peak Referenced Analysis\n")
if(rpeak_window_stats$n_pipelines > 0) {
  cat("- **Pipelines using R-peak reference**: ", rpeak_window_stats$n_pipelines, "\n")
  cat("- **R-peak start time range**: ", rpeak_window_stats$start_range_min, " to ", rpeak_window_stats$start_range_max, " ms\n")
  cat("- **R-peak end time range**: ", rpeak_window_stats$end_range_min, " to ", rpeak_window_stats$end_range_max, " ms\n")
  cat("- **R-peak window duration range**: ", rpeak_window_stats$duration_min, " to ", rpeak_window_stats$duration_max, " ms\n")
  
  # Most common time windows
  if(nrow(rpeak_common_windows) > 0) {
    cat("\n### Most Common R-peak Time Windows:\n")
    for(i in 1:min(3, nrow(rpeak_common_windows))) {
      cat("- **", rpeak_common_windows$time_window[i], "**: ", rpeak_common_windows$n_studies[i], " studies (", rpeak_common_windows$percentage[i], "%)\n")
    }
  }
  
  # Core overlap analysis
  if(!is.na(rpeak_overlap_analysis$core_start)) {
    cat("\n### Core Time Window (included by most studies):\n")
    cat("- **Core window**: ", rpeak_overlap_analysis$core_start, " to ", rpeak_overlap_analysis$core_end, " ms\n")
    cat("- **Studies including this core**: ", rpeak_overlap_analysis$core_percentage, "% (", rpeak_overlap_analysis$studies_including_core, "/", rpeak_overlap_analysis$total_rpeak_studies, ")\n")
  }
} else {
  cat("- **No R-peak referenced analyses found**\n")
}

cat("\n## T-peak Referenced Analysis\n")
if(tpeak_window_stats$n_pipelines > 0) {
  cat("- **Pipelines using T-peak reference**: ", tpeak_window_stats$n_pipelines, "\n")
  cat("- **T-peak start time range**: ", tpeak_window_stats$start_range_min, " to ", tpeak_window_stats$start_range_max, " ms\n")
  cat("- **T-peak end time range**: ", tpeak_window_stats$end_range_min, " to ", tpeak_window_stats$end_range_max, " ms\n")
  cat("- **T-peak window duration range**: ", tpeak_window_stats$duration_min, " to ", tpeak_window_stats$duration_max, " ms\n")
} else {
  cat("- **No T-peak referenced analyses found**\n")
}

cat("\n## Baseline Correction\n")
cat("- **Pipelines using baseline correction**: ", baseline_pct, "% (", nrow(baseline_window_data), "/", nrow(df_pipelines), ")\n")
if(nrow(baseline_window_data) > 0) {
  cat("- **Overall baseline start time range**: ", baseline_stats$start_range_min, " to ", baseline_stats$start_range_max, " ms\n")
  cat("- **Overall baseline end time range**: ", baseline_stats$end_range_min, " to ", baseline_stats$end_range_max, " ms\n")
  cat("- **Overall baseline duration range**: ", baseline_stats$duration_min, " to ", baseline_stats$duration_max, " ms\n")
}

cat("\n## Baseline Correction by Reference Peak\n")
if(nrow(baseline_by_reference) > 0) {
  for(i in 1:nrow(baseline_by_reference)) {
    ref_peak <- as.character(baseline_by_reference$hep_relative_to[i])
    n_pipes <- baseline_by_reference$n_pipelines[i]
    n_studies <- baseline_by_reference$n_studies[i]
    start_min <- baseline_by_reference$start_range_min[i]
    start_max <- baseline_by_reference$start_range_max[i]
    end_min <- baseline_by_reference$end_range_min[i]
    end_max <- baseline_by_reference$end_range_max[i]
    
    cat("- **", ref_peak, "**: ", n_pipes, " pipelines from ", n_studies, " studies\n")
    cat("  - Start range: ", start_min, " to ", start_max, " ms\n")
    cat("  - End range: ", end_min, " to ", end_max, " ms\n")
  }
} else {
  cat("- **No reference-specific baseline data available**\n")
}

cat("\n## Baseline Windows Ending Before QRS Complex\n")
cat("- **Studies with baseline ending before QRS**: ", baseline_before_qrs_stats$percentage_before_qrs, "% (", baseline_before_qrs_stats$studies_ending_before_qrs, "/", baseline_before_qrs_stats$total_studies_with_baseline, ")\n")

cat("\n### By Reference Scheme:\n")
if(nrow(baseline_before_qrs_by_ref) > 0) {
  for(i in 1:nrow(baseline_before_qrs_by_ref)) {
    ref_peak <- as.character(baseline_before_qrs_by_ref$hep_relative_to[i])
    total <- baseline_before_qrs_by_ref$total_studies[i]
    before_qrs <- baseline_before_qrs_by_ref$studies_ending_before_qrs[i]
    pct <- baseline_before_qrs_by_ref$percentage_before_qrs[i]
    
    cat("- **", ref_peak, "**: ", pct, "% (", before_qrs, "/", total, " studies)\n")
  }
}

cat("\n## Significant Effects Windows\n")
cat("- **Pipelines with significant effects**: ", significant_window_stats$n_pipelines, "\n")
if(significant_window_stats$n_pipelines > 0) {
  cat("- **Effects start time range**: ", significant_window_stats$start_range_min, " to ", significant_window_stats$start_range_max, " ms\n")
  cat("- **Effects end time range**: ", significant_window_stats$end_range_min, " to ", significant_window_stats$end_range_max, " ms\n")
  cat("- **Effects duration range**: ", significant_window_stats$duration_min, " to ", significant_window_stats$duration_max, " ms\n")
}

# Significant effects by reference peak
significant_by_reference <- if(nrow(significant_effects_data) > 0) {
  significant_effects_data %>%
    filter(!is.na(reference), reference != "unknown") %>%
    group_by(reference) %>%
    summarise(
      n_pipelines = n(),
      start_range_min = min(start_time),
      start_range_max = max(start_time),
      end_range_min = min(end_time),
      end_range_max = max(end_time),
      duration_min = min(end_time - start_time),
      duration_max = max(end_time - start_time),
      .groups = "drop"
    )
} else {
  data.frame()
}

if(nrow(significant_by_reference) > 0) {
  cat("\n### Significant Effects by Reference Peak:\n")
  for(i in 1:nrow(significant_by_reference)) {
    ref_peak <- as.character(significant_by_reference$reference[i])
    n_pipes <- significant_by_reference$n_pipelines[i]
    start_min <- significant_by_reference$start_range_min[i]
    start_max <- significant_by_reference$start_range_max[i]
    end_min <- significant_by_reference$end_range_min[i]
    end_max <- significant_by_reference$end_range_max[i]
    dur_min <- significant_by_reference$duration_min[i]
    dur_max <- significant_by_reference$duration_max[i]
    
    cat("- **", ref_peak, "**: ", n_pipes, " pipelines\n")
    cat("  - Start range: ", start_min, " to ", start_max, " ms\n")
    cat("  - End range: ", end_min, " to ", end_max, " ms\n")
    cat("  - Duration range: ", dur_min, " to ", dur_max, " ms\n")
  }
}

# Peak effect timing analysis by method and reference - core regions where most studies found effects
peak_effects_analysis <- if(nrow(significant_effects_data) > 0) {
  significant_effects_data %>%
    filter(!is.na(reference), reference != "unknown") %>%
    mutate(
      # Determine analysis method based on averaging_time
      analysis_method = if_else(averaging_time == "1", "Averaging", "Cluster-based")
    ) %>%
    group_by(analysis_method, reference) %>%
    summarise(
      n_pipelines = n(),
      # Find core regions using median approach (like the HEP core window analysis)
      median_start = median(start_time, na.rm = TRUE),
      median_end = median(end_time, na.rm = TRUE),
      # Count studies that include the core region
      studies_in_core = sum(start_time <= median(start_time, na.rm = TRUE) & 
                           end_time >= median(end_time, na.rm = TRUE), na.rm = TRUE),
      core_percentage = round(studies_in_core / n() * 100, 1),
      .groups = "drop"
    ) %>%
    # For T-peak, add equivalent R-peak timing (assuming ~300ms T-peak delay)
    mutate(
      rpeak_equivalent_start = if_else(reference == "T-peak", median_start + 300, median_start),
      rpeak_equivalent_end = if_else(reference == "T-peak", median_end + 300, median_end)
    )
} else {
  data.frame()
}

cat("\n### Peak Effect Timing by Analysis Method:\n")
if(nrow(peak_effects_analysis) > 0) {
  # Cluster-based analysis
  cluster_data <- peak_effects_analysis %>% filter(analysis_method == "Cluster-based")
  if(nrow(cluster_data) > 0) {
    cat("**Cluster-based analysis core effect regions:**\n")
    for(i in 1:nrow(cluster_data)) {
      ref_peak <- cluster_data$reference[i]
      median_start <- round(cluster_data$median_start[i], 1)
      median_end <- round(cluster_data$median_end[i], 1)
      core_pct <- cluster_data$core_percentage[i]
      n_studies <- cluster_data$studies_in_core[i]
      total_studies <- cluster_data$n_pipelines[i]
      
      if(ref_peak == "R-peak") {
        cat("- **R-peak referenced**: ", median_start, "-", median_end, " ms (", core_pct, "% of studies, ", n_studies, "/", total_studies, ")\n")
      } else if(ref_peak == "T-peak") {
        rpeak_start <- round(cluster_data$rpeak_equivalent_start[i], 1)
        rpeak_end <- round(cluster_data$rpeak_equivalent_end[i], 1)
        cat("- **T-peak referenced**: ", median_start, "-", median_end, " ms (≈", rpeak_start, "-", rpeak_end, " ms after R-peak; ", core_pct, "% of studies, ", n_studies, "/", total_studies, ")\n")
      }
    }
  }
  
  # Averaging analysis
  avg_data <- peak_effects_analysis %>% filter(analysis_method == "Averaging")
  if(nrow(avg_data) > 0) {
    cat("\n**Averaging analysis core effect regions:**\n")
    for(i in 1:nrow(avg_data)) {
      ref_peak <- avg_data$reference[i]
      median_start <- round(avg_data$median_start[i], 1)
      median_end <- round(avg_data$median_end[i], 1)
      core_pct <- avg_data$core_percentage[i]
      n_studies <- avg_data$studies_in_core[i]
      total_studies <- avg_data$n_pipelines[i]
      
      if(ref_peak == "R-peak") {
        cat("- **R-peak referenced**: ", median_start, "-", median_end, " ms (", core_pct, "% of studies, ", n_studies, "/", total_studies, ")\n")
      } else if(ref_peak == "T-peak") {
        rpeak_start <- round(avg_data$rpeak_equivalent_start[i], 1)
        rpeak_end <- round(avg_data$rpeak_equivalent_end[i], 1)
        cat("- **T-peak referenced**: ", median_start, "-", median_end, " ms (≈", rpeak_start, "-", rpeak_end, " ms after R-peak; ", core_pct, "% of studies, ", n_studies, "/", total_studies, ")\n")
      }
    }
  }
} else {
  cat("**No peak effect timing data available**\n")
}
```

# Multiple Pipelines and Methodological Variations

```{r variations}
# Multiple approaches per paper (studies)
multiple_stats_tests <- df_pipelines %>%
  group_by(PMID) %>%
  summarise(n_tests = n_distinct(statistics, na.rm = TRUE)) %>%
  filter(n_tests > 1) %>%
  nrow()

multiple_windows <- df_pipelines %>%
  group_by(PMID) %>%
  summarise(n_windows = n_distinct(paste(hep_start, hep_end), na.rm = TRUE)) %>%
  filter(n_windows > 1) %>%
  nrow()

total_papers <- nrow(df_studies)

cat("## Multiple Approaches per Study\n")
cat("- **Papers using multiple statistical tests**: ", round(multiple_stats_tests / total_papers * 100, 0), "%\n")
cat("- **Papers varying HEP window start/end**: ", round(multiple_windows / total_papers * 100, 0), "%\n")
```

---
*Generated on `r Sys.Date()`*
